### 2018-06-21 paper3_relevance and symbols_01.Rmd
Add files via upload

---
title: "Does high personal relevance mitigate the effect of symbolic elements in government public communications?"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

<br>

Last edited at `r Sys.Date()`.[^footnote_scripts]

[^footnote_scripts]: Original R scripts available at:  https://github.com/saaralonbarkat/symbols_and_relevance

```{r , include=FALSE, echo=FALSE}
#load("SVIVA_R_ENV.RData")
source("SVIVA_exp2_dm_03.R")

SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
SVIVA2_01_center = filter(SVIVA2_01,AREA==0)
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(knitr)
library(tidyverse)
library(stargazer)
library(car)
library(broom)
library(kableExtra)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
N_raw = nrow(SVIVA2_raw_00)
N_0=SVIVA2_00%>%nrow()
N_1=SVIVA2_01%>%nrow()

filter_IP = N_0-(SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE)%>%nrow())
filter_age = N_0-(SVIVA2_00 %>%
  filter(!(AGE%in% 1:17))%>% nrow())
filter_IMC = N_0-(SVIVA2_00 %>%
  filter(IMC==1)%>% nrow())
filter_time = N_0-(SVIVA2_00 %>%
  filter(TIMER_total>=3,TIMER_total<=30)%>%nrow())

N_1_haifa = filter(SVIVA2_01,AREA==1)%>%nrow()
N_1_center = filter(SVIVA2_01,AREA==0)%>%nrow()

```

<br>

---

# Abstract

*Previous public administration studies have examined whether public communications can increase citizens trust in government organizations. Recent experimental studies have demonstrated that these communications can enhance trust not only by conveying substantive information, but also by incorporating strategically desigened symbolic element that evoke positive feelings and associations (e.g. logos, images and celebrities). Still, previous studies did not examine the conditions under which citizens are more/less susceptible to these symbols.

Effective public communications have been proposed as a remedy for citizens' distrust in government. The studies that explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies. Recently, a few studies pointed to the effect of symbolic elements, entangled in these communications (e.g. logos, images and celebrities). Still, we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information. Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements can increase citizens' trust via two mechanisms: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication. Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust. I examine these expectations via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans. The results confirm that symbolic elements in communications increase citizens' trust. The effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to scrutinize their content. I discuss the implications of these findings for democratic responsiveness and accountability.*

---

<br>

# Introduction

Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their undervaluation of public-service performance. One of the main remedies which has been proposed for this problem is greater investment in direct government communications with citizens. Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014]. In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on contracts related to public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].

The public administration research on the effect of government public communications on citizens attitudes has focused mostly on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g. @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017]. Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on organizations' performance and logically persuasive explanations for their policies. At the same time, experiment-based studies that explored the responses of citizens to substantive information revealed cognitive biases that distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].

Recently, a few studies pointed to the additional effect of *symbolic* elements that are entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018]. These studies demonstrated that government organizations may cause citizens to view them more favorably through familiar and well-designed symbolic elements that evoke positive associations and emotions. Still, we lack a theory and robust empirical evidence of the exact mechanisms through which these symbols increase citizens trust. Additionally, these previous studies did not examine the interaction between the symbolic elements and the substantive content of information in public communications.

This research gap has normative significance. Whereas the responsiveness of citizens to substantive information is perceived favorably from a normative view of democratic theory, the potential effect of symbolic elements can be problematic. One can argue that shaping citizens' perceptions of governments by evoking associations and emotions stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking. Mainly, we should be concerned about the possibility that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017]. Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*

To address these research questions, I draw upon the social psychology Elaboration Likelihood Model (ELM). ELM provides a comprehensive theoretical framework for the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences for attitude change  [@petty_1986; @petty_2011]. Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them. *Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.

To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens. The experiment focuses on the empirical case of the Israeli Environment Protection Ministry. I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information of the communications (logically persuasive vs. unpersuasive policy plans) and by symbolic elements in them (real symbols vs. fake symbols and no symbols conditions).

I find that the symbolic elements increased citizens' trust in these policies. In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about its content. I discuss the theoretical and normative implications of these findings.

<br>

# Symbolic elements in government communications and their shaping of citizens' attitudes: what do we know?

Symbols are fundamental for almost any form of human interaction, as acknowledged by early scholars of social science [@blumer_1986]. A symbol can be broadly defined as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp. 28-29]. My focus is on those symbols that are strategically used by government organizations in their public communications, and are designed to distinguish organizations and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations. Prominent examples are unique logos, colors associated with specific meanings, icons, images, and the use of celebrities as endorsers. These elements are widely used by businesses and political candidates to attract targeted consumers and voters. Yet, they can be also found in the communications of government bureaucracies with citizens, including their mass-media advertising campaigns, social media accounts, internet pages, official publications, signboards in public places and personal mail notifications to citizens.

By comparison with the abundant research on citizens’ responses to informative elements in public communications [for reviews see: @cucciniello_2016; @grimmelikhuijsen_2017; @james_2017], public administration literature has devoted relatively little attention to the effect of symbolic elements. Recently, however, a few experimental studies tackled the issue. @marvel_2015 analyzed US citizens' responses to a television advertisement of the public Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and background music. His study shows that participants who watched the advertisement evaluated the organization's performance more positively. @teodoro_2018 suggested that the name of US federal agencies not only represents information about their activities, but may also carry specific symbolic meaning and affect that can shape citizens' support for government policy (depending on citizens' political party identification). These two studies provide examples for the role of symbols in shaping citizens' attitudes. Still, they did not effectively disentangle the effects of the symbolic and informational aspects of the studied public communications.

A study by @karens_2016 did examine the distinct effect of symbols in communications on citizens' trust. The scholars surveyed university students from three European countries and examined their trust in two policy plans of the European Commission, and it's shaping by the appearance of the organization's logo in the communication of the policy plans. They found that including the Commission’s logo significantly increased citizens' trust in these policies. Their results show an impressive effect size equivalent to 0.7 standard deviations. [^footnote_karens]

[^footnote_karens]: The effect size they found was smaller with regard to the "air quality" policy compared with the "digital skills" policy which were presented (Cohen's d = 0.7 vs. 0.6). Also, the effect was smaller among subjects from the Netherlands, compared with those from Belgium and Poland (Cohen's d = 0.5 vs. 0.7).

@alonbarkat_2017 examined Israeli citizens' trust in the Israel Electricity Corporation, a state owned company, and it's shaping by their exposure to comic cartoon figures that were routinely presented in the organization's public campaigns. They compared between citizens who were personally exposed to prolonged power outages, and others who were not. They found that the symbolic element had a positive effect on citizens' trust in the organization, including among those who personally experienced poor performance (a modest effect size equivalent to 0.25 standard deviations). Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them ("evaluative conditioning"). They proposed that the effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the assessed government quality.

The aforementioned studies tend to suggest that public communications increase citizens' trust in government organizations and their policies, not only by conveying valuable substantive information, but also by incorporating symbolic elements that evoke positive associations and emotions. Moreover, the findings of @alonbarkat_2017 suggest that incorporating symbolic elements in public communications can unduly compensate for poor government performance, thus pointing to their potential detrimental implications.

Even though these studies substantiate a link between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this effect. Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective in shaping citizens' trust. Specifically, these studies neither theorized nor empirically tested the interaction between symbolic elements and citizens’ processing of substantive information in communications. We do not know whether well-designed symbols reinforce, or offset, citizens' rational responses to information. Specifically, as explained above, it is essential to assess the possibility that symbols can unduly compensate for unfavorable or logically unpersuasive information that should yield negative responses.

To address this theoretical gap in public administration research, I propose a nuanced theoretical framework for the effects of symbols in communications and their interaction with information, building on social psychology theory on persuasive communication.

<br>

# The Elaboration Likelihood Model and the various mechanisms of persuasion by elements in communications

The social psychology Elaboration Likelihood Model (ELM) provides a comprehensive theoretical framework for investigating peoples' varying responses to "persuasive" communications [@petty_1986; @petty_2011]. In addition to its general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [@petty_1983; @swasy_1985; @dotson_2000; @drge_1989; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002]. Yet, thus far, the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.

According to ELM, the responses of individuals to persuasive communications depends on the amount of thinking that they dedicate to the message content. Persuasion can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation. This range between high and low degrees of thought is referred to as the "elaboration continuum". People's location along this continuum is associated with different psychological processes of persuasion. At the high end of the elaboration continuum, also called the "central route", people are likely to respond by cognitively scrutinizing the arguments central to the merits of the issue. At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as an unconscious transfer of affect[^footnote_dual_process_theories]. In turn, these different persuasion mechanisms are likely to cause divergent types of attitudinal change. Persuasion through the central route is expected to be more enduring, resistant and predictive of behavior, compared with peripheral route persuasion. Of course, much of the time, people are located in between the two ends of the continuum, and thus persuasion is determined by a mixture of these processes.

[^footnote_dual_process_theories]: The conceptual distinction between the "central and peripheral routes for persuasion" largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].

ELM enables to disentangle the distinct effects of different elements in communications. Some elements are processed differently by people at different locations along the elaboration continuum. Consider for instance a text that contains a series of logical arguments supporting a certain position. Those at the high end of the continuum would regard this text as arguments, and systematically scrutinize it based on its logical persuasive quality (central route processing). Conversely, those at the low end of the continuum are likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing). Some elements provide potential cues that lack any logical quality at all. For example, the physical attractiveness of the source normally does not represent any substantive argument, yet it can serve as a simple cue. These latter elements may affect the attitudes of those at the low end, but are less likely to persuade those at the high end [@petty_1986].

ELM further postulates that the placement of people along the elaboration continuum in any given situation is determined by their *motivation* and *ability* to think about the message. Accordingly, the literature proposes a variety of such motivational and ability factors. Among others, studies have demonstrated that the more people are distracted, the more difficult it is for them to scrutinize the message arguments, a mechanism that has been referred to as "elaboration disruption" [@petty_1976; @petty_1986]. Another prominent factor that influences people's inclination to elaborate on the message is their affective state, or mood. Positive mood (compared with neutral or negative moods) reduces people's cognitive ability and attenuates their motivation to think, due to their desire to maintain their positive mood and avoid message processing that would depress it [@worth_1987; @mackie_1989; @bless_1990; @schwarz_1991; @petty_2015; but see: @wegener_1995].[^footnote_elm_factors] Affecting the amount of thinking can cause attitude change in interaction with elements in the communication that can function as arguments or peripheral cues. Decreasing the amount of thinking weakens the effect the substantive arguments and enhances the effect of peripheral cues (and vice versa).

[^footnote_elm_factors]: For a thorough review of motivational and ability factors affecting likelihood to elaborate see @petty_1998.

Elements in communications can also function as factors that affect people's motivation and/or ability to think. For example, Background music in commercials can distract people and prevent them from scrutinizing their content [@park_1986]; The use of humor in television shows stimulates positive mood and reduces people's ability and motivation to scrutinize their substantive arguments [@nabi_2007; @young_2008]. Hence, elements can have more than one function, and can shape attitudes through several mechanisms. They can serve both as variables that affect the amount of thinking and as potential peripheral cues or arguments. Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuades people directly through the peripheral route, yet at the same time they can also as factors that reduce elaboration. Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).[^footnote_multifunction_factors]

[^footnote_multifunction_factors]: @petty_1986 have suggested that we are more likely to find complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum. When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide if the message is worth or needs considering.

<br>

# ELM and the roles of symbolic elements and information in government public communications

How may we apply the theoretical framework of ELM to the study of the effects of symbolic elements in government communications with citizens and their interaction with substantive information?

In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated and capable to do so. Conversely, symbolic elements are potential peripheral cues, which can affect citizens' trust through the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017]. However, in addition to their direct effect as peripheral cues, symbolic elements may also increase citizens' trust indirectly. They can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing negative information (e.g. information on poor performance) and weak arguments (e.g. logically unpersuasive description of their policy plans).

Symbolic elements may decrease citizens' ability and motivation to think about the message in several ways. First, they can cause elaboration disruption, by distracting citizens and absorbing their attention and cognitive efforts [@petty_1976; @petty_1986]. Second, they can decrease citizens' motivation and ability to think about the message content by creating a positive affect and placing citizens in a positive mood. As explained above, the postulation that positive mood decreases elaboration has been explained, in part, by a mood maintenance mechanism [@mackie_1989; @bless_1990; @schwarz_1991]. This mechanism is particularly relevant to the context of government communications, in which thinking about the content of the message - government organizations and policies - is likely to yield negative mood among most people [@marvel_2015; @marvel_2015a; @hvidman_2016]. Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about tedious bureaucratic affairs, which would depress their positive mood. The latter expectation entails an interaction between symbols and the substantive information in the communications. Symbolic elements are likely to increase citizens' trust insofar as they reduce citizens' inclination to scrutinize information that would have decreased their trust.

In sum, I expect that:

>*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*

>*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*

>*H<sub>3</sub> - Symbolic elements are likely to decrease the amount of thinking about the content of the communication.*

>*H<sub>4</sub> - The abovementioned conditioned effect of symbolic elements on citizens' trust is likely to be mediated by the decrease in the amount of thinking (a moderated mediation hypothesis).*

The theoretical hypotheses are graphically displayed in **Figure 1**.

<br>
**Figure 1: Theoretical model**
![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/theoretical_model.png) 
<br>

Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans. Nevertheless, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, since citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2017; @james_2017b]. Congruently, the effect of positive information (versus a medium level) is likely to be relatively small, and hence neutralizing this effect may not make much difference. Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction.

<br>

# Methodology

To empirically test the above mentioned hypotheses, I designed a randomized survey experiment, which simulates citizens' responses to government organizations' communications about their policy plans. Such communications can be found in publicized reports, pamphlets, websites, new media pages and ads. Focusing on communication of future policy plans, as opposed to communications on performance of existing policies, enables me to utilize a real-world empirical case without compromising the reliability  of the manipulation of the content. This is because most citizens do not have prior knowledge of organizations' future policy plans, and thus they will be more willing to trust a fictional communication of an organization with regard to its future policy.

In addition to the above-mentioned hypotheses, the experiment is also designed to test an additional set of hypotheses regarding the interaction between symbols and the perceived personal relevance of communications. The selection of policy plans and the construction of the population sample were designed to account for variation in that variable. In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the interaction between symbols and information.[^footnote_relevance_paper]

[^footnote_relevance_paper]: The methodological aspects which are relevant for examining the additional hypotheses (i.e. the interaction between symbols with personal relevance) are described in a separate paper. An English translation of the full survey is available from the supplementary appendix.

<br>

##*The empirical case*

Empirically, I focused on the case of the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, both at the national and local levels. I analyzed the effects of informative and symbolic elements in EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them. In the survey, the communications about the two policy plans, in which I manipulated the informative and symbolic elements, are presented to the participants as sections from the EPM's official publication of its annual work plan.

Methodologically, EPM makes a good case for this study since has invested greatly over the past years in public communications. In these various communications, the EPM used an array of symbolic elements, which became widely recognized by the public. Here, I focused on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 2**. The first symbolic element is the unique brand logo of the EPM (image a. in figure 1). This logo consists of pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment. The second symbolic element in which I focused is the green color, which is strongly associated with taking care of the environment. The EPM's logo and the green color can be seen in almost all of the visual communications of the EPM, and they represent key elements of its unique "visual identity" [@vandenbosch_2005]. The third element is celebrity endorsements. Specifically, I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, that previously endorsed two salient advertising campaigns of the EPM. The campaign starring the comedian Tal Friedman (image b.) was launched in 2010, and included a series of advertisements in which Friedman was presented with a green grass head, and accordingly the campaign's slogan was: "starting to think green". The campaign starring the comedian Ido Rosenblum (image c.) was launched in 2017, and was focused on reducing the use of disposable bags.[^footnote_campaigns] The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.

In the course of the survey experiment, I confirmed that the EPA logo and the images of the celebrities from the campaigns are familiar to the participants. `r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize EPA logo to some extent and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`% , respectively). In robust analyses I further exclude those who do not recognize these symbols.[^footnote_prior_studies]

[^footnote_campaigns]: Multimedia files of these campaigns are available in EPM's website: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/default.aspx.

[^footnote_prior_studies]: In two prior online survey tests, which I conducted before the experiment, I collected further information about the affect and symbolic associations of these symbols. These results, which are reported in the supplementary appendix, substantiate my empirical assumption that these elements evoke positive emotions Israeli citizens, and that citizens automatically associate them with EPM and its policies. These results also indicate that the images of the celebrity comedians from EPM campaigns are perceived as humoristic, and accordingly, they are expected to position people in a positive mood.

<br>
**Figure 2: symbolic elements of EPM**
![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/EPM_symbols.png) 
<font size="0.5">

Notes:

a. EPM logo.
b. Tal Friedman, comedian,  EPM campaign “starting to think green” (2010): "Isn't money growing on trees? Moving to environmental consumption and saving at least 6,000 NIS per year!", "starting to think green", "The Environmental Protection Ministry".
c. Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "The reusable bag is again left at home? A tip from Ido: Hang it on the door handle and you will not leave without it", "Taking every bag seriously", "The Environmental Protection Ministry".

</font>

<br>

## *Procedure and sample population*

The survey was presented to the participants as a study about citizens' attitudes regarding environmental policy issues. The participants were first asked pre-manipulation questions about their political ideology and their perceptions about the pubic sector.[^footnote_relevance_manipulation] Thereafter, they were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018. The policy plans regarded to reducing air-pollution in the Bay of Haifa (an area in Israel) and reducing domestic waste and increasing recycling. The two policy plans were presented to each subject in a random order. Each policy plan included the title of the policy goal (i.e. "reducing the levels of air pollution in the Haifa bay"), followed by short descriptions of two actions to be taken by EPM in order to fulfill this goal (30-50 words each).

[^footnote_relevance_manipulation]: This section also included a manipulation of participants' perceived personal relevance. Participants in the treatment group were asked a series of questions about environmental government policy, whereas participants in the control group were asked instead equivalent questions about their field of occupation.

Per each policy, the subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e. logically persuasive policy plan) or weak policy (i.e. logically unpersuasive). The policy activities which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM. The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures which are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable. For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were increasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality. The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**. For each subject, one of the two policies was strong and the other was weak. For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.

In addition to information manipulation, the participants are randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment (real symbols), control no symbols and control fake symbols. In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement". Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images. Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people. The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design. Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo. The symbols conditions are displayed in **Appendix B**. Further details about the images in the real and fake symbols conditions are found in the supplementary appendix. That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e. one strong and one weak), enables me later to analyze the interaction between these two manipulations both via between- and within-subjects.

[^footnote_symbols_manipulation_checks]: In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM. The results of these examinations are reported in the supplementary appendix.

Each policy plan was followed by six questions questions about respondents' trust in the policy. Afterwards, the subjects conducted a memory test on the last policy that was presented to them, and were asked about the extent to which they elaborated on it and about the personal relevance of the policy plans. Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence. After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities. Finally, the participants were debriefed about the manipulations, and the possible deception. An English translation of the full survey is available from the supplementary appendix.

Altogether, for each policy plan, the survey experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs. weak policy). The assignment to the different experimental groups is graphically presented in **Figure 3**. The experimental groups are fairly balanced with respect to demographics, and pre-manipulation variables. Throughout the rest of the paper, I will analyze the results at the policy level, in order to simplify the analyses. Accordingly, I transformed the dataset into a multilevel structure of policies nested within subjects.[^footnote_combined_analyses]

[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while adding the interactions between the manipulations and the policy plans. In these models, the interactions between the policy plans and the symbols are far from significance, with no major changes to the results.

<br>
**Figure 3: Experimental design for policy plan communications**
![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow.png)

The survey experiment was conducted online through Qualtrics Survey Software. To subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*. The online survey link was sent by iPanel, between 28.1-1.2.2018 to 5,077 people. A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`). These filters are not significantly associated with the experimental conditions. Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb%>%nrow()` observations nested within these `r N_1` subjects.

[^footnote_responserate]: According to iPanel's reporting, 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample. Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.

[^footnote_sample_areas]: To capture variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country. The final sample consists of `r SVIVA2_01_haifa%>%nrow()` subjects from the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` from the center cities. The two areas received the exact same link to the online survey, and they were equally, randomly assigned to the experimental conditions.

##*Operationalization of variables*

```{r, echo=FALSE, warning=FALSE, message=F}
alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
                               TRUST_air_q2,
                               TRUST_air_q3,
                               TRUST_air_q4,
                               TRUST_air_q5,
                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)

alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
                               TRUST_waste_q2,
                               TRUST_waste_q3,
                               TRUST_waste_q4,
                               TRUST_waste_q5,
                               TRUST_waste_q6))[["total"]][["raw_alpha"]]%>%round(2)

alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2)%>%round(2)

cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate%>%mean()%>%round(2)

cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate%>%mean()%>%round(2)

cor_RT_delta = cor.test(SVIVA2_01$ELABORATION_total_time_log,
                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)

cor_memory_delta = cor.test(SVIVA2_01$MEMORY_total,
                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)

t_air_information = t.test(TRUST_air_INDEX~INFORMATION_air,SVIVA2_01)
t_waste_information = t.test(TRUST_waste_INDEX~INFORMATION_waste,SVIVA2_01)

```

My main independent variables are the above mentioned manipulations for information and symbols, and the interaction between them. My outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy). This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_waste_trust`), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017]. Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan. The mean of this trust index is `r SVIVA2_01_comb%>%summarise(mean(trust))%>%max()%>%round(2)`, the standard variation is `r SVIVA2_01_comb%>%summarise(sd(trust))%>%max()%>%round(2)` and the median is `r SVIVA2_01_comb%>%summarise(median(trust))%>%max()%>%round(2)`. Higher levels of trust are associated with higher trust in government, left-wing ideology and lower levels of education. In addition to measuring participants trust in each policy, per each subject, I also calculated the delta between her trust in the strong and weak policy plans which were presented to her (*Mean* = `r SVIVA2_01%>%summarise(mean(WITHIN_DELTA))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()%>%round(2)`, *Median* = `r SVIVA2_01%>%summarise(median(WITHIN_DELTA))%>%max()%>%round(2)`). I used this Trust in policy delta to analyze the interaction between symbols and information within subjects.

To assess the levels of thinking or elaboration on the policy plans, I used two distinct measures: First, I counted the number of seconds participants spent on scanning each of the policy plans (hereafter – reaction time), log transformed to reduce skewness (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(ELABORATION_time_log))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(ELABORATION_time_log))%>%max()%>%round(2)`). Second, I used a memory test, asking participants whether a list of four items were included in the policy plan, of which two were/were not included (participants could also select "I don't know"). The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero. Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2)%>%round(2)`, which substantiates their validity.

[^footnote_elaboration]: In addition, I included in the survey a battery of five items that measure participants' subjective perception of their level of elaboration. I initially sought to use these items as an additional measure for elaboration. However, I decided to forgo this subjective measure, due to its lack of correlation with the reaction time and memory test score, and its possible bias by people's disinclination to admit that they did not thoroughly read the policy plans.

In addition to the above independent variables, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in government, interest in environmental issues and residence in the Haifa-Bay area. Summary statistics and correlation matrix for all variables are available in the supplementary appendix.

<br>

# Results

I now turn to analyzing the experimental results. I begin by examining my first and second hypotheses, that regard the effect of symbols on trust and its interaction with information. Thereafter, I will examine hypotheses 3 and 4, that regard the mediating role on elaboration. For each section, I conducted both *between-subjects* and *within-subjects* analyses.

##*The interaction bewteen symbols and information*

According to my first hypothesis, I expect that the real symbols condition will have a positive main effect on subjects' trust in the policy plans. According to my second hypothesis, I expect a positive interaction between the real symbols and weak policy plan. Namely, the effect of the real symbols is expected to be greater among those subjects who were assigned to the weak policy. In **Table 1**, I test these two hypotheses via regression analyses. To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level via `lme4` R package (ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`). In Model 1 I regress trust in policy on the symbols manipulation. Thereafter, in Models 2 and 3, I add the information manipulation, and the interaction between them. In these models, I the reference category for the symbols manipulation is the no-symbols condition.

```{r, echo=FALSE,warning=FALSE,message=FALSE}
x_realsymbol = filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(trust))%>%max()
x_fakesymbol = filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(trust))%>%max()
x_nosymbol = filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(trust))%>%max()
sd_trust = SVIVA2_01_comb%>%summarise(sd(trust))%>%max()

x_realsymbol_delta = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA))%>%max()
x_fakesymbol_delta = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA))%>%max()
x_nosymbol_delta = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA))%>%max()
sd_trust_delta = SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()

```

**Table 1: Regression analyses – the effect of symbols on trust in policy**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
library(lme4)

mod_1.1 = lmer(trust~SYMBOL_t+(1|IP),data=SVIVA2_01_comb)
mod_1.2 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
mod_1.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy (combined)"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)

mod_1.1.r_1 = lmer(trust~SYMBOL_t.r+(1|IP),data=SVIVA2_01_comb)
mod_1.2.r_1 = lmer(trust~SYMBOL_t.r+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
mod_1.3.r_1 = lmer(trust~SYMBOL_t.r*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)

mod_1.3.r_2 = lmer(trust~SYMBOL_t*INFORMATION+(1|IP),data=SVIVA2_01_comb)

mod_1.3.r_3 = lmer(trust~SYMBOL_t.r*INFORMATION+(1|IP),data=SVIVA2_01_comb)

mod_1.3.r_4 = lmer(trust~SYMBOL_t.r_2*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)

```

&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).

The real symbols condition has a positive main effect on trust in Model 1.1. The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), and at the 90% level compared with the fake symbols (`r mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`]). These differences are equivalent to `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` and `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` standard variations, respectively. The graphic elements in the fake symbols condition also increased participants' trust, but to a lesser extent, presumably due to their unfamiliarity, and their weaker positive affect.

In Model 1.2, the effect of the symbols remains intact, and the effect of the weak policy condition is negative and significant (*Coef* = `r mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]). In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant. The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively). When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1, one-tailed). Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100)%>%round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]). The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05). To facilitate the interpretation of this interaction, **Figure 4** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.

**Figure 4: The effect of symbolic elements on trust under weak vs. strong information**

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=6,fig.height=4}
ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(INFORMATION_n)))+ 
  theme_classic()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.65),
               width=0.2,size=0.5,position=position_dodge(0.1),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = INFORMATION_n,linetype=INFORMATION_n),position=position_dodge(0.1))+
  scale_shape_manual(guide=F,values=c(19,1))+
  scale_linetype_manual(name="Information",values=c(1,4),labels=c("Weak policy","Strong policy"))+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
```

<font size="0.5">

*Note*: Error bars represent 90% confidence intervals.

</font>

```{r, echo=FALSE,warning=FALSE,message=FALSE}

x_realsymbol_delta=filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA))%>%max()
x_fakesymbol_delta=filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA))%>%max()
x_nosymbol_delta=filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA))%>%max()

t_delta_symbol_nosymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=1))
t_delta_symbol_fakesymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=0))
t_delta_nosymbol_fakesymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=2))

```

The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions. Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition. This comparison is graphically displayed in **Figure 5**. The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively). The differences between the two control groups are insignificant. These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.

**Figure 5: The effect of symbolic elements on within-subject delta between strong and weak policies**

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=4,fig.height=4}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), WITHIN_DELTA))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
                              fun.args = list(mult = 1.65),
                              width=0.1,size=0.5,color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=2)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="Symbolic elements",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Within subject delta", breaks = seq(0,1,by=0.1))

```

<font size="0.5">

*Note*: Error bars represent 90% confidence intervals.

</font>

Altogether, the above between- and within-subject analyses largely support my first two hypothesis. They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications. Symbols attenuate the negative effect of weak or logically unpersuasive information in communications. In other statistical models, shown in the supplementary appendix, I tested additional specifications, including analyzing the unfilterred sample, adding control variables, excluding subjects who did not recognize the real symbols and adding interactions with the policy plans. In all these robust analyses, the main effect of the real symbols remains positive and significant, and the interaction between the real symbols and the weak information remains positive and significant.

How can we explain the finding that the real symbols only had a marginally significant effect on participants' trust in the strong policy, compared with the no logo, and did not increase their trust compared with the fake logo (Model 1.3)? One tentative explanation could be that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels. Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust. If this explanation holds, then result will be a ceiling effect. This explanation can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration. Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceiling_effect]

[^footnote_ceiling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups. The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e. the lower 25% observations). In the weak policy condition, the first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[2])%>%max()%>%round(1)` points compared with the no symbols, whereas the third quartile (i.e. the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[4])%>%max()%>%round(1)` points. In the strong policy condition, we can find similar pattern of decreasing marginal effect. The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile (i.e. the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.

##*The mediating role of elaboration*

In the following section, I test the postulation that the interaction between symbols and information is explained or mediated by a decrease in elaboration. To reiterate, in the survey, I used reaction time (log) and memory score as measures for participants' level of elaboration of the policy plans. Based on my third hypothesis, I expect to find a negative effect of the real symbols on these two measures. Thereafter, my fourth hypothesis entails moderated mediation relations: the decrease in elaboration mediates the effect of symbols of trust under the weak policy, but not under the strong policy (see Figure 1).

```{r, echo=FALSE,warning=FALSE,message=FALSE}
x_realsymbol_RT=filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(ELABORATION_time))%>%max()
x_fakesymbol_RT=filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(ELABORATION_time))%>%max()
x_nosymbol_RT=filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(ELABORATION_time))%>%max()

t_RT_symbol_nosymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=1))
t_RT_symbol_fakesymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=0))
t_RT_nosymbol_fakesymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=2))

x_realsymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(ELABORATION_time_log))%>%max()
x_fakesymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(ELABORATION_time_log))%>%max()
x_nosymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(ELABORATION_time_log))%>%max()

cor_memory_nosymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=1)$SYMBOL),
                               filter(SVIVA2_01_comb,SYMBOL!=1)$MEMORY_score, 
                               method="spearman")$estimate%>%mean()%>%round(2)

cor_memory_fakesymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=0)$SYMBOL),
                               filter(SVIVA2_01_comb,SYMBOL!=0)$MEMORY_score, 
                               method="spearman")$estimate%>%mean()%>%round(2)
```

In **Table 2**, I test the effects of the real symbols on the elaboration measures via regression analyses. I regressed each measure on the symbols manipulation (Models 2.1, 2.3), and than added the information manipulation (Models 2.2, 2.4). The first two models, which refer to reaction time, are random intercept models which are similar to the statistical models in table 1. As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression.

**Table 2: Regression analyses – the effect of symbols on elaboration**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_2.1 = lmer(ELABORATION_time_log~SYMBOL_t+(1|IP),data=SVIVA2_01_comb)
mod_2.2 = lmer(ELABORATION_time_log~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
mod_2.3 = lm(MEMORY_score~SYMBOL_t,data=SVIVA2_01_comb)
mod_2.4 = lm(MEMORY_score~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)

stargazer(mod_2.1,mod_2.2,mod_2.3,mod_2.4,
          type="html",style = "apsr",
          dep.var.labels=c("Reaction time (log)","Memory score"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)"),
          initial.zero = FALSE,
          omit.stat = c("f","ser","aic","bic"),
          notes = "*Notes*: Table entries are non-standardized regression coefficients. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)

mod_2.1.r_1 = lmer(ELABORATION_time~SYMBOL_t.r+(1|IP),data=SVIVA2_01_comb)

mod_2.3.r_1 = lm(MEMORY_score~SYMBOL_t.r,data=SVIVA2_01_comb)

```

&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).

In all four models, the coefficients of the real symbols are negative and significant, and the coefficients of the fake symbols are insignificant. The real symbols decreased the number of second subjects spent on the pages of the policy plans in the online survey, compared with both control groups.[^footnote_RT_symbols] The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), yet it is not sufficiently significant compared with the fake symbols. The averaged memory score of subjects who saw the real symbols was significantly lower, compared with both the no logo and the fake logo groups (*Coef* = `r mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`], and `r mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`], respectively).[^footnote_memory_symbols] There is no significant change to the results when adding the the effects of the information manipulation (in Models 2.2, 2.4). The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them. **Figure 6** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions. The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.

[^footnote_RT_symbols]: The difference in seconds compared with the no symbols group, as extracted from the coefficients in logs is: `r (mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())%>%abs()%>%exp()%>%round(1)`-`r (x_realsymbol_RT_log-x_fakesymbol_RT_log)%>%abs()%>%exp()%>%round(1)`. The difference between the raw averages is `r (x_realsymbol_RT-x_fakesymbol_RT)%>%abs()%>%round(1)` seconds.

[^footnote_memory_symbols]: Descriptively, `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% of those in the real symbols group received the minimum score of 0, compared with `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the no symbols and fake symbols control groups. Congruently, the percentage of those who managed to correctly identify the two items dropped from `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the control groups to only `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`%.  Given that the measure of memory score is ordinal, I also tested it's correlation with the symbols manipulation via Spearman test. Spearman rho = `r cor_memory_nosymbol` and `r cor_memory_fakesymbol`, compared with the no symbols and fake symbols control groups.

**Figure 6: The effect of symbolic elements on elaboration**

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=4,fig.height=4}
ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), ELABORATION_time_log))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
                              fun.args = list(mult = 1.65),
                              width=0.1,size=0.5,color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.5)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Reaction Time (log)")

ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), MEMORY_score))+
  theme_classic()+
  #geom_boxplot(width=0.25,color = "gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
                              fun.args = list(mult = 1.65),
                              width=0.1,size=0.5,color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.5)+
  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Memory score")
```

<font size="0.5">

*Note*: Error bars represent 90% confidence intervals.

</font>

Next, I tested the hypothesis that the decrease in reaction time and memory score mediate the effect of the real symbols on trust in the weak policy plans. To do so, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al. [@imai_2010; @imai_2011], and was also recently also implemented in Public Administration research [@porumbescu_2018]. This method predicts the change in the outcome variable (here: trust in policy) given the causal change in the mediator that would be induced by the treatment (here: decreased elaboration inducted by the real symbols). Accordingly, it enables to decipher the proportion of the causal mediation effect from the total effect. Causal mediation analysis is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling. It is advantaged in terms of its accuracy as well as its ability to identify causality. **Table 3** displays the results of the causal mediation of reaction time (log) and memory test, under the weak policy plans.

```{r, echo=FALSE,warning=FALSE,message=FALSE}
library(mediation)
set.seed(2018)

#RT
med.fit_RT_nosymbol = 
  lm(ELABORATION_time_log~SYMBOL*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=1))

med.out_RT_nosymbol = 
  lm(trust~SYMBOL*INFORMATION+ELABORATION_time_log*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=1))

med.fit_RT_fakesymbol = 
  lm(ELABORATION_time_log~SYMBOL*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=0))

med.out_RT_fakesymbol = 
  lm(trust~SYMBOL*INFORMATION+ELABORATION_time_log*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=0))

med_RT__nosymbol_INFORMTION_0 = mediate(med.fit_RT_nosymbol,
                                med.out_RT_nosymbol,
                                treat = "SYMBOL",
                                mediator = "ELABORATION_time_log", 
                                covariates = list(INFORMATION = 0), sims = 100)

med_RT__fakesymbol_INFORMTION_0 = mediate(med.fit_RT_fakesymbol,
                                  med.out_RT_fakesymbol,
                                  treat = "SYMBOL",
                                  mediator = "ELABORATION_time_log", 
                                  covariates = list(INFORMATION = 0), sims = 100)

med_RT__nosymbol_INFORMTION_1 = mediate(med.fit_RT_nosymbol,
                                med.out_RT_nosymbol,
                                treat = "SYMBOL",
                                mediator = "ELABORATION_time_log", 
                                covariates = list(INFORMATION = 1), sims = 100)

med_RT__fakesymbol_INFORMTION_1 = mediate(med.fit_RT_fakesymbol,
                                  med.out_RT_fakesymbol,
                                  treat = "SYMBOL",
                                  mediator = "ELABORATION_time_log", 
                                  covariates = list(INFORMATION = 1), sims = 100)

#memory
med.fit_memory_nosymbol = 
  lm(MEMORY_score~SYMBOL*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=1))

med.out_memory_nosymbol = 
  lm(trust~SYMBOL*INFORMATION+MEMORY_score*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=1))

med.fit_memory_fakesymbol = 
  lm(MEMORY_score~SYMBOL*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=0))

med.out_memory_fakesymbol = 
  lm(trust~SYMBOL*INFORMATION+MEMORY_score*INFORMATION,
     data=filter(SVIVA2_01_comb,SYMBOL!=0))

med_memory__nosymbol_INFORMTION_0 = mediate(med.fit_memory_nosymbol,
                                med.out_memory_nosymbol,
                                treat = "SYMBOL",
                                mediator = "MEMORY_score", 
                                covariates = list(INFORMATION = 0), sims = 100)

med_memory__fakesymbol_INFORMTION_0 = mediate(med.fit_memory_fakesymbol,
                                  med.out_memory_fakesymbol,
                                  treat = "SYMBOL",
                                  mediator = "MEMORY_score", 
                                  covariates = list(INFORMATION = 0), sims = 100)

med_memory__nosymbol_INFORMTION_1 = mediate(med.fit_memory_nosymbol,
                                med.out_memory_nosymbol,
                                treat = "SYMBOL",
                                mediator = "MEMORY_score", 
                                covariates = list(INFORMATION = 1), sims = 100)

med_memory__fakesymbol_INFORMTION_1 = mediate(med.fit_memory_fakesymbol,
                                  med.out_memory_fakesymbol,
                                  treat = "SYMBOL",
                                  mediator = "MEMORY_score", 
                                  covariates = list(INFORMATION = 1), sims = 100)

extract_mediation_summary <- function (x) {

  clp <- 100 * x$conf.level
  isLinear.y <- ((class(x$model.y)[1] %in% c("lm", "rq")) || 
                   (inherits(x$model.y, "glm") && x$model.y$family$family == 
                      "gaussian" && x$model.y$family$link == "identity") || 
                   (inherits(x$model.y, "survreg") && x$model.y$dist == 
                      "gaussian"))

  printone <- !x$INT && isLinear.y

  if (printone) {

    smat <- c(x$d1, x$d1.ci, x$d1.p)
    smat <- rbind(smat, c(x$z0, x$z0.ci, x$z0.p))
    smat <- rbind(smat, c(x$tau.coef, x$tau.ci, x$tau.p))
    smat <- rbind(smat, c(x$n0, x$n0.ci, x$n0.p))

    rownames(smat) <- c("ACME", "ADE", "Total Effect", "Prop. Mediated")

  } else {
    smat <- c(x$d0, x$d0.ci, x$d0.p)
    smat <- rbind(smat, c(x$d1, x$d1.ci, x$d1.p))
    smat <- rbind(smat, c(x$z0, x$z0.ci, x$z0.p))
    smat <- rbind(smat, c(x$z1, x$z1.ci, x$z1.p))
    smat <- rbind(smat, c(x$tau.coef, x$tau.ci, x$tau.p))
    smat <- rbind(smat, c(x$n0, x$n0.ci, x$n0.p))
    smat <- rbind(smat, c(x$n1, x$n1.ci, x$n1.p))
    smat <- rbind(smat, c(x$d.avg, x$d.avg.ci, x$d.avg.p))
    smat <- rbind(smat, c(x$z.avg, x$z.avg.ci, x$z.avg.p))
    smat <- rbind(smat, c(x$n.avg, x$n.avg.ci, x$n.avg.p))

    rownames(smat) <- c("ACME (control)", "ACME (treated)", 
                        "ADE (control)", "ADE (treated)", "Total Effect", 
                        "Prop. Mediated (control)", "Prop. Mediated (treated)", 
                        "ACME (average)", "ADE (average)", "Prop. Mediated (average)")

  }

  colnames(smat) <- c("Estimate", paste(clp, "% CI Lower", sep = ""), 
                      paste(clp, "% CI Upper", sep = ""), "p-value")
  smat

}

```

```{r, echo=FALSE,warning=FALSE,message=FALSE}
#RT
table_med_RT__nosymbol_INFORMTION_0 = 
summary(med_RT__nosymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_RT__fakesymbol_INFORMTION_0 = 
summary(med_RT__fakesymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_RT__nosymbol_INFORMTION_1 = 
summary(med_RT__nosymbol_INFORMTION_1)%>%
extract_mediation_summary()

table_med_RT__fakesymbol_INFORMTION_1 = 
summary(med_RT__fakesymbol_INFORMTION_1)%>%
extract_mediation_summary()

#memory
table_med_memory__nosymbol_INFORMTION_0 = 
summary(med_memory__nosymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_memory__fakesymbol_INFORMTION_0 = 
summary(med_memory__fakesymbol_INFORMTION_0)%>%
extract_mediation_summary()

table_med_memory__nosymbol_INFORMTION_1 = 
summary(med_memory__nosymbol_INFORMTION_1)%>%
extract_mediation_summary()

table_med_memory__fakesymbol_INFORMTION_1 = 
summary(med_memory__fakesymbol_INFORMTION_1)%>%
extract_mediation_summary()
```

**Table 3: Causal mediation analysis**

*Mediator: Reaction time*
```{r, echo=FALSE,warning=FALSE,message=FALSE}
table_med_RT_INFORMTION_0 = 
  cbind.data.frame(table_med_RT__nosymbol_INFORMTION_0,
                   table_med_RT__fakesymbol_INFORMTION_0)
library(kableExtra)

kable(table_med_RT_INFORMTION_0, "html",digits = 3) %>%
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
```

*Mediator: Memory score*
```{r, echo=FALSE,warning=FALSE,message=FALSE}
table_med_memory_INFORMTION_0 = 
  cbind.data.frame(table_med_memory__nosymbol_INFORMTION_0,
                   table_med_memory__fakesymbol_INFORMTION_0)

kable(table_med_memory_INFORMTION_0, "html",digits = 3) %>%
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
```

*Notes*: "ACME": Averaged causal mediated effect; "ADE": Averaged direct effect. Mediate function uses bootstrap to estimate the confidence intervals. In all these analyses I used `set.seed=2018`.

The results suggest that the decreased reaction time significantly mediates the effect of the real symbols on trust in the weak policies. The estimated proportion of the mediation is `r (table_med_RT__nosymbol_INFORMTION_0["Prop. Mediated","Estimate"]*100)%>%round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_INFORMTION_0["Prop. Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols. The decreased memory score also mediates the effect (*p*<.1), but only compared with the no symbols group.[^footnote_mediation_memory]

[^footnote_mediation_memory]: The differences between the analyses of the two measures can be also explained by the fact that memory score is calculated with regard to half of the observations.

Finally, I also tested this moderated mediation hypothesis via within-subjects analysis. Given that each subject represents one observation, the memory score remains the same, and for the reaction time, I summed the number of seconds subjects spent on both policies (log transformed). The results of this causal mediation analysis are summarized in **Table 4**.

```{r, echo=FALSE,warning=FALSE,message=FALSE}
med.fit_RT_nosymbol_delta = 
  lm(ELABORATION_total_time_log~SYMBOL,
     data=filter(SVIVA2_01,SYMBOL!=1))

med.out_RT_nosymbol_delta = 
  lm(WITHIN_DELTA~SYMBOL+ELABORATION_total_time_log,
     data=filter(SVIVA2_01,SYMBOL!=1))

med.fit_RT_fakesymbol_delta = 
  lm(ELABORATION_total_time_log~SYMBOL,
     data=filter(SVIVA2_01,SYMBOL!=0))

med.out_RT_fakesymbol_delta = 
  lm(WITHIN_DELTA~SYMBOL+ELABORATION_total_time_log,
     data=filter(SVIVA2_01,SYMBOL!=0))

med_RT__nosymbol_delta = mediate(med.fit_RT_nosymbol_delta,
                                med.out_RT_nosymbol_delta,
                                treat = "SYMBOL",
                                mediator = "ELABORATION_total_time_log", 
                                sims = 100)

med_RT__fakesymbol_delta = mediate(med.fit_RT_fakesymbol_delta,
                                med.out_RT_fakesymbol_delta,
                                treat = "SYMBOL",
                                mediator = "ELABORATION_total_time_log", 
                                sims = 100)

med.fit_memory_nosymbol_delta = 
  lm(MEMORY_total~SYMBOL,
     data=filter(SVIVA2_01,SYMBOL!=1))

med.out_memory_nosymbol_delta = 
  lm(WITHIN_DELTA~SYMBOL+MEMORY_total,
     data=filter(SVIVA2_01,SYMBOL!=1))

med.fit_memory_fakesymbol_delta = 
  lm(MEMORY_total~SYMBOL,
     data=filter(SVIVA2_01,SYMBOL!=1))

med.out_memory_fakesymbol_delta = 
  lm(WITHIN_DELTA~SYMBOL+MEMORY_total,
     data=filter(SVIVA2_01,SYMBOL!=1))

med_memory__nosymbol_delta = mediate(med.fit_memory_nosymbol_delta,
                                med.out_memory_nosymbol_delta,
                                treat = "SYMBOL",
                                mediator = "MEMORY_total", 
                                sims = 100)

med_memory__fakesymbol_delta = mediate(med.fit_memory_fakesymbol_delta,
                                med.out_memory_fakesymbol_delta,
                                treat = "SYMBOL",
                                mediator = "MEMORY_total", 
                                sims = 100)
```

```{r, echo=FALSE,warning=FALSE,message=FALSE}
#RT
table_med_RT__nosymbol_delta = 
summary(med_RT__nosymbol_delta)%>%
extract_mediation_summary()

table_med_RT__fakesymbol_delta = 
summary(med_RT__fakesymbol_delta)%>%
extract_mediation_summary()

#memory
table_med_memory__nosymbol_delta = 
summary(med_memory__nosymbol_delta)%>%
extract_mediation_summary()

table_med_memory__fakesymbol_delta = 
summary(med_memory__fakesymbol_delta)%>%
extract_mediation_summary()
```

**Table 4: Causal mediation analysis (within subjects)**

*Mediator: Reaction time*

```{r, echo=FALSE,warning=FALSE,message=FALSE}
table_med_RT_delta = 
  cbind.data.frame(table_med_RT__nosymbol_delta,
                   table_med_RT__fakesymbol_delta)

kable(table_med_RT_delta, "html",digits = 3) %>%
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
```

*Mediator: Memory score*

```{r, echo=FALSE,warning=FALSE,message=FALSE}
table_med_memory_delta = 
  cbind.data.frame(table_med_memory__nosymbol_delta,
                   table_med_memory__fakesymbol_delta)

kable(table_med_memory_delta, "html",digits = 3) %>%
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
```
<br>

```{r, echo=FALSE,warning=FALSE,message=FALSE}
t1<- medsens(med_RT__nosymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect", 
             sims = 100)
t2<- medsens(med_RT__fakesymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect", 
             sims = 100)

t3<- medsens(med_memory__nosymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect",              sims = 100)

t4<- medsens(med_RT__nosymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)

t5<- medsens(med_RT__fakesymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)

t6<- medsens(med_memory__nosymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)

t7<- medsens(med_memory__fakesymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)

#summary(t1)
```

The results of the within subjects mediation analysis similarly supports the moderated mediation hypothesis. The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction the time and the memory score. With respect to the reaction time, the estimated proportional mediation is `r (table_med_RT__nosymbol_delta["Prop. Mediated","Estimate"]*100)%>%round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_delta["Prop. Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols. Regarding the memory score,the estimated proportional mediation is `r (table_med_memory__nosymbol_delta["Prop. Mediated","Estimate"]*100)%>%round(1)`% and `r (table_med_memory__fakesymbol_delta["Prop. Mediated","Estimate"]*100)%>%round(1)`%, respectively.[^footnote_mediation_sensitivity]

[^footnote_mediation_sensitivity]: I also conducted a robustness test of "formal sensitivity" for the significant causal mediation models, as proposed by Imai et al. [-@imai_2010]. The sensitivity test examines the extent to which the causal mediation would change as a result of a correlation between the error terms of the mediator and the outcome variable (the "sequential ignorability" assumption). With regard to mediation by reaction time, the sensitivity factors range between 0.2-0.3, which suggest that a correlation greater than these values would violate the sequential ignorability assumption. Imai et al. did not offer any rule of thumb with regard to these factors. Yet, these results are consistent with sensitivity factors reported in previous studies, and therefore the mediation can be considered fairly reliable. The sensitivity factors for the mediation by the memory score are 0.1, which entails that it is less reliable.

Altogether, the between- and within-subjects analyses are consistent with my third and fourth hypotheses. They demonstrate that subjects who saw the policy plans with the familiar symbols of EPM, were less likely to elaborate on the content of the EPM policies, which in turn attenuated the negative effect of the weak information, and increased their trust in the weak policies. The partial mediation by reaction time is strongly significant, whereas the mediation by the memory test is not sufficiently significant in all models. In some of these models, the familiar symbols also had a significant direct positive effect, which can be theoretically explained by the peripheral effect of symbols via transfer of affect, in accordance with my first hypothesis.

#Discussion and conclusion

A growing body of Public-Administration research seeks to assess whether and how government organizations can increase citizens' trust through direct communications with citizens. This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect. Using a rigorous experimental design, embedded in a realistic setting focused on the case of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications. To the best of my knowledge, this is the first study to explore this interactions in the context of government communications.

I found that participants' exposure to the familiar symbols of EPM increased their trust in its policy plans, and that the effect was greater when they were presented with a weak policy plan. The latter interaction is partly explained by the negative effect of the symbols on the elaboration of the policy plans. These findings are based the analyses of the responses of more than `r (SVIVA2_01%>%nrow()%>%round(-2))-100` participants to two different policies, and are robust for various model specifications. Moreover, they are evidenced in both between- and within-subjects analysis. These results, if generalizable, suggest that incorporating familiar symbolic elements in public communications increase citizens' trust in government organizations and their actions, via two mechanisms: First, they evoke general positive feelings that are transferred to the specific organizations and policies. Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thereby, they cause them to disregard its weaknesses. These two supplementary mechanisms are theorized using the framework of the social psychology elaboration likelihood model [@petty_1986; @petty_2011].

Certainly, we must be cautious when drawing general conclusions from our findings. This study focuses, empirically, on one public organization, characterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians. Future studies may further examine the proposed theory by focusing on additional cases of public organizations and policy areas. In addition, this study focuses on policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.   Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information on good/bad outcomes. Another limitation of the study regards the fact that it examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol. Future studies may compare the effectiveness of different types of symbolic elements.

Keeping these limitations in mind, this study has several important implications for public administration research. Most importantly, my findings highlight the significant role of branding and symbolic communication in shaping citizens' attitudes about government. Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abounded research on their responses to information. Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018]. Furthermore, my findings suggest that symbols decrease citizens' "rational", systematic processing of substantive information. This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information.[^footnote_biases_ELM]. On the other hand, the emotive effect of government symbols on public opinion is highly problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010]. Moreover, it becomes especially problematic when symbols are used by poorly performing organizations, or organizations that lack professional expertise. It those cases, symbolic elements can mitigate justified public criticism of government failures. Ultimately, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which provides them political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018]. Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, organizations can also use it as a means to undermine them.

[^footnote_biases_ELM]: This possibility is supported, theoretically, by ELM. According to ELM, biased processing occurs in the central route, whereby people give proportional weight for strong or weak arguments. Accordingly, decreasing the amount of thinking may also decrease biased processing [@petty_1986]. Future research might put this expectation to test.

This study also contributes to existing behavioral Public Administration research by introducing ELM and applying it as a comprehensive theoretical framework for studying citizens' attitudes formation, and citizens' responses to government communications. ELM has various postulations and implications, but most importantly, it stresses that people respond differently to different communications, depending on people's motivation and ability to think about the subject, and on the quality of arguments and the peripheral cues in the communication. In this study, I applied ELM to theorize the direct and indirect effects of symbolic elements on trust. Future Public-Administration studies may apply ELM and further explore the effects of other peripheral, heuristic cues in government communications, and the moderating role of motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective. Future studies may also examine the postulations of ELM that persuasion via arguments is more likely to be enduring,  and to increase citizens' cooperation with government policies, compared with persuasion via symbolic elements and heuristic cues.

Finally, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications. The participants of these studies, including this particular one, have relatively high motivation to elaborate on the information that scholars presented them, because they may assume that they will be asked about it afterwards. In case they receive payment or other compensation for their participation, this further increases their motivation. By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they probably also have lower ability to do so, given the high competition on their time and attention. Accordingly, their responses to performance information will less affected by asymmetrical processing of information, because most of them are not likely to process this information in the first place. Instead, most of them will rely on simple cues and heuristic shortcuts. I expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2017; @olsen_2017]. Future studies may empirically explore these interactions. Regardless, scholars should also take to account this methodological issue when designing survey experiments, and attempt to simulate real world conditions, as much as possible. For instance, they can add filler sections in the survey before the real manipulation to attenuate participants' motivation and ability to elaborate. In addition, because the graphic design of communications also affects motivation and ability to elaborate, as shown here, scholars should simulate the design of real communications.

<br>

##Appendix A: Information manipulation

**Air-pollution policy** (Reducing the air-pollution in the Haifa-Bay)

EPM is working to reduce the air-pollution in the Haifa-Bay through:

*Strong*

* **Increasing the supervision of the factories in Haifa-Bay**.
In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways. The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the amount of fines for pollutants.

* **Reduction of smoke emissions from vehicles in Haifa Bay**.
The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area. The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and promotes the operation of a "clean-air area" that restricts the entry of polluting vehicles.

*Weak*

* **Decreasing the supervision of the factories in Haifa-Bay**.
The Ministry is preparing for a change in the method of supervision of the factories. The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the amount of fines. The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.

* **Raising citizens' awareness of the efforts to improve air quality**.
In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful. The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents. To this end, the ministry has increased its investment in public relations and publicity in this subject.

<br>

**Recycling policy** (Reducing waste and increasing recycling)

EPM is working to reduce the amount of waste and increase its recycling through:

*Strong*

* **Packaging recycling - Increased supervision of manufacturers**.
In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, which imposes on manufacturers and importers the responsibility for recycling the packaging. The Ministry will work to increase enforcement by virtue of this act, and will enforce it with regard to additional manufacturers and importers.

* **Reducing the usage of disposable bags**.
In order to reduce the use of disposable plastic bags, the Ministry enforces the Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the chains. The Ministry works to implement the act, and encourages the transition to reusable grocery bags.

*Weak*

* **Packaging recycling - Decreased supervision of manufacturers**.
The Ministry is preparing to a change in the method of supervision of the manufacturers, who are responsible for the recycling of product packaging by virtue of the act The ministry will reduce the number of inspections, rely on manufacturers' self-reports regarding their compliance with the requirements of the act, and reduce the amount of fines. The change is coordinated with members of the industry, which are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.

* **Reducing the usage of disposable bags**.
In recent years, the Ministry has taken steps to encourage the reduction of waste, which have been partially successful. The Ministry works to raise awareness of the actions taken and to highlight their success in order to improve its image among the public. To this end, the ministry has increased its investment in public relations and publicity in this subject.

<br>

##Appendix B: Symbols manipulation
![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/symbols_manipulation.png)

<font size="0.5">

*Note: The policy plans communications presented here are the strong policies, in the version adjusted for mobile interface.*

</font>

<br>

<br>

#References

### 2018-06-21 SVIVA_exp2_dm_03.R

@@ -1,0 +1,563 @@
+### SVIVA experiment 2 data management ###
+
+# Hi there!
+
+#loading packages
+
+library(tidyverse)
+#library(psych)
+library(car)
+library(stringr)
+library(lubridate)
+
+
+#loading raw data CSV file
+SVIVA2_raw_00 <- read.csv("SVIVA_exp2.csv")
+CITY_00 <- read.csv("CITY.csv")
+
+SVIVA2_raw <- SVIVA2_raw_00 %>% filter(V10==1)
+CITY <- CITY_00 %>% filter(V10==1)
+
+
+SVIVA2_raw[is.na(SVIVA2_raw)] <- 0
+
+SVIVA2_00 = SVIVA2_raw %>%
+  dplyr::select(V4,V5) %>%
+  mutate(IP = SVIVA2_raw$V6,
+         USER_ID = SVIVA2_raw$i.user3,
+         START_DATE = dmy_hm(SVIVA2_raw$V8),
+         END_DATE = dmy_hm(SVIVA2_raw$V9)) %>%  
+         mutate(TIMER_total = as.integer(END_DATE-START_DATE),
+         FINISHED = SVIVA2_raw$V10) %>%
+  dplyr::select(-c(1:2)) %>%
+  
+  ##Define variables####
+
+
+##interface
+mutate(MOBILE = if_else(SVIVA2_raw$Q23.1+SVIVA2_raw$Q22.1==1,1,0)) %>%
+  
+  #controls####
+mutate(ENVIRONMENT_INTEREST = Recode(SVIVA2_raw$Q3.2,"0=NA"),
+       ENVIRONMENT_FOLLOW = Recode(SVIVA2_raw$Q3.3,"0=NA"),
+       ENVIRONMENT_PREFERENCE = Recode(SVIVA2_raw$Q3.4,"0=NA"),
+       GOV_EVALUATION = SVIVA2_raw$Q2.3,
+       GOV_TRUST = SVIVA2_raw$Q2.4,
+       IDEOLOGY = SVIVA2_raw$Q2.5,
+       CHILDREN = if_else(SVIVA2_raw$Q313==5,0,1),
+       CHILDREN_young = if_else(SVIVA2_raw$Q313 %in% c(1,2),1,0),
+       FACTORIES_relatives = Recode(SVIVA2_raw$Q314,"0=NA;1=0;2=1"))%>%
+  
+  
+  ##demographics
[…]

### 2018-06-21 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 
-*Previous public administration studies have examined whether public communications can increase citizens trust in government organizations.
+*Previous public administration studies have examined whether public communications can affect citizens trust in government organizations and their policies.
 Recent experimental studies have demonstrated that these communications can enhance trust not only by conveying substantive information, but also by incorporating strategically desigened symbolic element that evoke positive feelings and associations (e.g.
 logos, images and celebrities).
-Still, previous studies did not examine the conditions under which citizens are more/less susceptible to these symbols.
-
-Effective public communications have been proposed as a remedy for citizens' distrust in government.
-The studies that explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies.
-Recently, a few studies pointed to the effect of symbolic elements, entangled in these communications (e.g.
-logos, images and celebrities).
-Still, we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information.
-Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements can increase citizens' trust via two mechanisms: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
-Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
-I examine these expectations via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans.
-The results confirm that symbolic elements in communications increase citizens' trust.
-The effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to scrutinize their content.
-I discuss the implications of these findings for democratic responsiveness and accountability.*
+Still, under which conditions are citizens more/less likely to be emotionally persuaded by these symbols?
+Building on the social psychology Elaboration Likelihood Model (ELM), I theorize that citizens are less susceptible to symbols when they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to invest in elaborate processing.
+I put this theory to test through a survey experiment, where I examine circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens' trust in the Environment Protection Ministry's policies for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
+I operationalize personal relevance both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+The experimental results do not support the hypothesis that higher personal relevance attenuates the effect of symbols.
+They tentatively suggest that symbols are more likely to persuade citizens who have predominant negative attitudes.*
 
@@
 
-Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their undervaluation of public-service performance.
-One of the main remedies which has been proposed for this problem is greater investment in direct government communications with citizens.
-Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
-In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on contracts related to public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].
+Public administration scholars have explored whether government organizations can enhance citizens' trust in them by employing public communications.
+Whereas most of the studies on the effect of government public communications on citizens attitudes has focused on the *informative* aspects of these communications [e.g.
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @grimmelikhuijsen_2015; @ho_2017], recent experimental studies further pointed to the emotive effect of *symbolic* elements that are entangled in government communications, such as  agencies' names [@teodoro_2018], brand logos [@karens_2016], and figures in public campaigns [@alonbarkat_2017].
+These studies demonstrated that these familiar and well-designed symbolic elements can enhance citizens' trust irratioanlly through a mechanism of "evaluative conditioning" - unconscious transfer of affect from the symbols to the public organizations and policies associated with them [@dehouwer_2012].
 
-The public administration research on the effect of government public communications on citizens attitudes has focused mostly on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
-Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on organizations' performance and logically persuasive explanations for their policies.
-At the same time, experiment-based studies that explored the responses of citizens to substantive information revealed cognitive biases that distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].
+While the abovementioned studies have substantiated the distinct effect of symbols, they did not theorize, nor empirically examine the conditions under which are these symbols are likely to be more/less effective in persuading citizens.
+The research gap has great significance.
+From the organizations' practical point of view, ...
 
-Recently, a few studies pointed to the additional effect of *symbolic* elements that are entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-These studies demonstrated that government organizations may cause citizens to view them more favorably through familiar and well-designed symbolic elements that evoke positive associations and emotions.
-Still, we lack a theory and robust empirical evidence of the exact mechanisms through which these symbols increase citizens trust.
-Additionally, these previous studies did not examine the interaction between the symbolic elements and the substantive content of information in public communications.
+Employing a broader, democratic normative stance, we should be also concerned from the effect of symbols.
+Symbolic elements can elicit undue trust in poorly performing organizations and in ill-conceived policies.
+Accordingly, it may enable public organizations to escape justified public criticism [@alonbarkat_2017].
+Hence, by understanding when citizens are more likely to be affected by symbols, we  may enable us to identify the
 
-This research gap has normative significance.
-Whereas the responsiveness of citizens to substantive information is perceived favorably from a normative view of democratic theory, the potential effect of symbolic elements can be problematic.
-One can argue that shaping citizens' perceptions of governments by evoking associations and emotions stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking.
-Mainly, we should be concerned about the possibility that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
-Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
+Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *under what conditions do symbolic elements  increase citizens' trust in governemnt policy?* And specifically, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
 
@@
 Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
+I expect that this effect is attenuated the more citizens perceive the communications as personally relevant, because they are more motivated to think about their messages.
 *Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
 
-To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens.
+To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow() %>% round(-1)` Israeli citizens.
 The experiment focuses on the empirical case of the Israeli Environment Protection Ministry.
@@
 fake symbols and no symbols conditions).
+In addition, I examine the moderating role of the perceived personal relevance of these policies.
 
@@
 In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about its content.
+I did not find support for the hypothesis that the effect of the symbolic elements is attenuated by the perceived personal relevance of the policy issue.
 I discuss the theoretical and normative implications of these findings.
@@
 
-# Symbolic elements in government communications and their shaping of citizens' attitudes: what do we know?
+# The Elaboration Likelihood Model (ELM) and the effect of symbols and information in communicaions.
 
-Symbols are fundamental for almost any form of human interaction, as acknowledged by early scholars of social science [@blumer_1986].
-A symbol can be broadly defined as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp.
-28-29].
-My focus is on those symbols that are strategically used by government organizations in their public communications, and are designed to distinguish organizations and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations.
-Prominent examples are unique logos, colors associated with specific meanings, icons, images, and the use of celebrities as endorsers.
-These elements are widely used by businesses and political candidates to attract targeted consumers and voters.
-Yet, they can be also found in the communications of government bureaucracies with citizens, including their mass-media advertising campaigns, social media accounts, internet pages, official publications, signboards in public places and personal mail notifications to citizens.
-
-By comparison with the abundant research on citizens’ responses to informative elements in public communications [for reviews see: @cucciniello_2016; @grimmelikhuijsen_2017; @james_2017], public administration literature has devoted relatively little attention to the effect of symbolic elements.
-Recently, however, a few experimental studies tackled the issue.
-@marvel_2015 analyzed US citizens' responses to a television advertisement of the public Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and background music.
-His study shows that participants who watched the advertisement evaluated the organization's performance more positively.
-@teodoro_2018 suggested that the name of US federal agencies not only represents information about their activities, but may also carry specific symbolic meaning and affect that can shape citizens' support for government policy (depending on citizens' political party identification).
-These two studies provide examples for the role of symbols in shaping citizens' attitudes.
-Still, they did not effectively disentangle the effects of the symbolic and informational aspects of the studied public communications.
-
-A study by @karens_2016 did examine the distinct effect of symbols in communications on citizens' trust.
-The scholars surveyed university students from three European countries and examined their trust in two policy plans of the European Commission, and it's shaping by the appearance of the organization's logo in the communication of the policy plans.
-They found that including the Commission’s logo significantly increased citizens' trust in these policies.
-Their results show an impressive effect size equivalent to 0.7 standard deviations.
-[^footnote_karens]
-
-[^footnote_karens]: The effect size they found was smaller with regard to the "air quality" policy compared with the "digital skills" policy which were presented (Cohen's d = 0.7 vs.
-0.6).
-Also, the effect was smaller among subjects from the Netherlands, compared with those from Belgium and Poland (Cohen's d = 0.5 vs.
-0.7).
-
-@alonbarkat_2017 examined Israeli citizens' trust in the Israel Electricity Corporation, a state owned company, and it's shaping by their exposure to comic cartoon figures that were routinely presented in the organization's public campaigns.
-They compared between citizens who were personally exposed to prolonged power outages, and others who were not.
-They found that the symbolic element had a positive effect on citizens' trust in the organization, including among those who personally experienced poor performance (a modest effect size equivalent to 0.25 standard deviations).
-Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them ("evaluative conditioning").
-They proposed that the effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the assessed government quality.
-
-The aforementioned studies tend to suggest that public communications increase citizens' trust in government organizations and their policies, not only by conveying valuable substantive information, but also by incorporating symbolic elements that evoke positive associations and emotions.
-Moreover, the findings of @alonbarkat_2017 suggest that incorporating symbolic elements in public communications can unduly compensate for poor government performance, thus pointing to their potential detrimental implications.
-
-Even though these studies substantiate a link between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this effect.
-Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective in shaping citizens' trust.
-Specifically, these studies neither theorized nor empirically tested the interaction between symbolic elements and citizens’ processing of substantive information in communications.
-We do not know whether well-designed symbols reinforce, or offset, citizens' rational responses to information.
-Specifically, as explained above, it is essential to assess the possibility that symbols can unduly compensate for unfavorable or logically unpersuasive information that should yield negative responses.
-
-To address this theoretical gap in public administration research, I propose a nuanced theoretical framework for the effects of symbols in communications and their interaction with information, building on social psychology theory on persuasive communication.
-
+The social psychology Elaboration Likelihood Model (ELM) provides a comprehensive theoretical framework for investigating peoples' varying responses to "persuasive" 
 <br>
 
-# The Elaboration Likelihood Model and the various mechanisms of persuasion by elements in communications
-
-The social psychology Elaboration Likelihood Model (ELM) provides a comprehensive theoretical framework for investigating peoples' varying responses to "persuasive" communications [@petty_1986; @petty_2011].
-In addition to its general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [@petty_1983; @swasy_1985; @dotson_2000; @drge_1989; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
-Yet, thus far, the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.
-
-According to ELM, the responses of individuals to persuasive communications depends on the amount of thinking that they dedicate to the message content.
-Persuasion can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation.
-This range between high and low degrees of thought is referred to as the "elaboration continuum".
-People's location along this continuum is associated with different psychological processes of persuasion.
-At the high end of the elaboration continuum, also called the "central route", people are likely to respond by cognitively scrutinizing the arguments central to the merits of the issue.
-At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as an unconscious transfer of affect[^footnote_dual_process_theories].
-In turn, these different persuasion mechanisms are likely to cause divergent types of attitudinal change.
-Persuasion through the central route is expected to be more enduring, resistant and predictive of behavior, compared with peripheral route persuasion.
-Of course, much of the time, people are located in between the two ends of the continuum, and thus persuasion is determined by a mixture of these processes.
-
-[^footnote_dual_process_theories]: The conceptual distinction between the "central and peripheral routes for persuasion" largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].
-
-ELM enables to disentangle the distinct effects of different elements in communications.
-Some elements are processed differently by people at different locations along the elaboration continuum.
-Consider for instance a text that contains a series of logical arguments supporting a certain position.
-Those at the high end of the continuum would regard this text as arguments, and systematically scrutinize it based on its logical persuasive quality (central route processing).
-Conversely, those at the low end of the continuum are likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing).
-Some elements provide potential cues that lack any logical quality at all.
-For example, the physical attractiveness of the source normally does not represent any substantive argument, yet it can serve as a simple cue.
-These latter elements may affect the attitudes of those at the low end, but are less likely to persuade those at the high end [@petty_1986].
-
-ELM further postulates that the placement of people along the elaboration continuum in any given situation is determined by their *motivation* and *ability* to think about the message.
-Accordingly, the literature proposes a variety of such motivational and ability factors.
-Among others, studies have demonstrated that the more people are distracted, the more difficult it is for them to scrutinize the message arguments, a mechanism that has been referred to as "elaboration disruption" [@petty_1976; @petty_1986].
-Another prominent factor that influences people's inclination to elaborate on the message is their affective state, or mood.
-Positive mood (compared with neutral or negative moods) reduces people's cognitive ability and attenuates their motivation to think, due to their desire to maintain their positive mood and avoid message processing that would depress it [@worth_1987; @mackie_1989; @bless_1990; @schwarz_1991; @petty_2015; but see: @wegener_1995].[^footnote_elm_factors] Affecting the amount of thinking can cause attitude change in interaction with elements in the communication that can function as arguments or peripheral cues.
-Decreasing the amount of thinking weakens the effect the substantive arguments and enhances the effect of peripheral cues (and vice versa).
-
-[^footnote_elm_factors]: For a thorough review of motivational and ability factors affecting likelihood to elaborate see @petty_1998.
-
-Elements in communications can also function as factors that affect people's motivation and/or ability to think.
-For example, Background music in commercials can distract people and prevent them from scrutinizing their content [@park_1986]; The use of humor in television shows stimulates positive mood and reduces people's ability and motivation to scrutinize their substantive arguments [@nabi_2007; @young_2008].
-Hence, elements can have more than one function, and can shape attitudes through several mechanisms.
-They can serve both as variables that affect the amount of thinking and as potential peripheral cues or arguments.
-Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuades people directly through the peripheral route, yet at the same time they can also as factors that reduce elaboration.
-Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).[^footnote_multifunction_factors]
-
-[^footnote_multifunction_factors]: @petty_1986 have suggested that we are more likely to find complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
-When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide if the message is worth or needs considering.
-
-<br>
-
-# ELM and the roles of symbolic elements and information in government public communications
+# The moderating role of perceived personal relevance on citizens' responses to symbols and information in communications
 
 How may we apply the theoretical framework of ELM to the study of the effects of symbolic elements in government communications with citizens and their interaction with substantive information?
-
-In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated and capable to do so.
-Conversely, symbolic elements are potential peripheral cues, which can affect citizens' trust through the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
-However, in addition to their direct effect as peripheral cues, symbolic elements may also increase citizens' trust indirectly.
-They can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing negative information (e.g.
-information on poor performance) and weak arguments (e.g.
-logically unpersuasive description of their policy plans).
-
-Symbolic elements may decrease citizens' ability and motivation to think about the message in several ways.
-First, they can cause elaboration disruption, by distracting citizens and absorbing their attention and cognitive efforts [@petty_1976; @petty_1986].
-Second, they can decrease citizens' motivation and ability to think about the message content by creating a positive affect and placing citizens in a positive mood.
-As explained above, the postulation that positive mood decreases elaboration has been explained, in part, by a mood maintenance mechanism [@mackie_1989; @bless_1990; @schwarz_1991].
-This mechanism is particularly relevant to the context of government communications, in which thinking about the content of the message - government organizations and policies - is likely to yield negative mood among most people [@marvel_2015; @marvel_2015a; @hvidman_2016].
-Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about tedious bureaucratic affairs, which would depress their positive mood.
-The latter expectation entails an interaction between symbols and the substantive information in the communications.
-Symbolic elements are likely to increase citizens' trust insofar as they reduce citizens' inclination to scrutinize information that would have decreased their trust.
 
@@
 **Figure 1: Theoretical model**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/theoretical_model.png) 
+
 <br>
-
-Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
-Nevertheless, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, since citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2017; @james_2017b].
-Congruently, the effect of positive information (versus a medium level) is likely to be relatively small, and hence neutralizing this effect may not make much difference.
-Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction.
 
@@
 
-To empirically test the above mentioned hypotheses, I designed a randomized survey experiment, which simulates citizens' responses to government organizations' communications about their policy plans.
-Such communications can be found in publicized reports, pamphlets, websites, new media pages and ads.
-Focusing on communication of future policy plans, as opposed to communications on performance of existing policies, enables me to utilize a real-world empirical case without compromising the reliability  of the manipulation of the content.
-This is because most citizens do not have prior knowledge of organizations' future policy plans, and thus they will be more willing to trust a fictional communication of an organization with regard to its future policy.
-
-In addition to the above-mentioned hypotheses, the experiment is also designed to test an additional set of hypotheses regarding the interaction between symbols and the perceived personal relevance of communications.
-The selection of policy plans and the construction of the population sample were designed to account for variation in that variable.
-In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the interaction between symbols and information.[^footnote_relevance_paper]
-
-[^footnote_relevance_paper]: The methodological aspects which are relevant for examining the additional hypotheses (i.e.
-the interaction between symbols with personal relevance) are described in a separate paper.
-An English translation of the full survey is available from the supplementary appendix.
-
 <br>
@@
 
-Empirically, I focused on the case of the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, both at the national and local levels.
-I analyzed the effects of informative and symbolic elements in EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them.
-In the survey, the communications about the two policy plans, in which I manipulated the informative and symbolic elements, are presented to the participants as sections from the EPM's official publication of its annual work plan.
+<br>
 
-Methodologically, EPM makes a good case for this study since has invested greatly over the past years in public communications.
-In these various communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
-Here, I focused on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 2**.
-The first symbolic element is the unique brand logo of the EPM (image a.
-in figure 1).
-This logo consists of pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
-The second symbolic element in which I focused is the green color, which is strongly associated with taking care of the environment.
-The EPM's logo and the green color can be seen in almost all of the visual communications of the EPM, and they represent key elements of its unique "visual identity" [@vandenbosch_2005].
-The third element is celebrity endorsements.
-Specifically, I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, that previously endorsed two salient advertising campaigns of the EPM.
-The campaign starring the comedian Tal Friedman (image b.) was launched in 2010, and included a series of advertisements in which Friedman was presented with a green grass head, and accordingly the campaign's slogan was: "starting to think green".
-The campaign starring the comedian Ido Rosenblum (image c.) was launched in 2017, and was focused on reducing the use of disposable bags.[^footnote_campaigns] The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.
-
-In the course of the survey experiment, I confirmed that the EPA logo and the images of the celebrities from the campaigns are familiar to the participants.
-`r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize EPA logo to some extent and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`% , respectively).
-In robust analyses I further exclude those who do not recognize these symbols.[^footnote_prior_studies]
-
-[^footnote_campaigns]: Multimedia files of these campaigns are available in EPM's website: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/default.aspx.
-
-[^footnote_prior_studies]: In two prior online survey tests, which I conducted before the experiment, I collected further information about the affect and symbolic associations of these symbols.
-These results, which are reported in the supplementary appendix, substantiate my empirical assumption that these elements evoke positive emotions Israeli citizens, and that citizens automatically associate them with EPM and its policies.
-These results also indicate that the images of the celebrity comedians from EPM campaigns are perceived as humoristic, and accordingly, they are expected to position people in a positive mood.
-
-<br>
-**Figure 2: symbolic elements of EPM**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/EPM_symbols.png) 
-<font size="0.5">
-
-Notes:
-
-a. EPM logo.
-b.
-Tal Friedman, comedian,  EPM campaign “starting to think green” (2010): "Isn't money growing on trees?
-Moving to environmental consumption and saving at least 6,000 NIS per year!", "starting to think green", "The Environmental Protection Ministry".
-c.
-Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "The reusable bag is again left at home?
-A tip from Ido: Hang it on the door handle and you will not leave without it", "Taking every bag seriously", "The Environmental Protection Ministry".
-
-</font>
+##*Data collection*
 
@@
 
-## *Procedure and sample population*
-
-The survey was presented to the participants as a study about citizens' attitudes regarding environmental policy issues.
-The participants were first asked pre-manipulation questions about their political ideology and their perceptions about the pubic sector.[^footnote_relevance_manipulation] Thereafter, they were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
-The policy plans regarded to reducing air-pollution in the Bay of Haifa (an area in Israel) and reducing domestic waste and increasing recycling.
-The two policy plans were presented to each subject in a random order.
-Each policy plan included the title of the policy goal (i.e.
-"reducing the levels of air pollution in the Haifa bay"), followed by short descriptions of two actions to be taken by EPM in order to fulfill this goal (30-50 words each).
-
-[^footnote_relevance_manipulation]: This section also included a manipulation of participants' perceived personal relevance.
-Participants in the treatment group were asked a series of questions about environmental government policy, whereas participants in the control group were asked instead equivalent questions about their field of occupation.
-
-Per each policy, the subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
-logically persuasive policy plan) or weak policy (i.e.
-logically unpersuasive).
-The policy activities which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
-The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures which are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
-For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were increasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality.
-The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
-For each subject, one of the two policies was strong and the other was weak.
-For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
-
-In addition to information manipulation, the participants are randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment (real symbols), control no symbols and control fake symbols.
-In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement".
-Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy.
-In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
-Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
-The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
-Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo.
-The symbols conditions are displayed in **Appendix B**.
-Further details about the images in the real and fake symbols conditions are found in the supplementary appendix.
-That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e.
-one strong and one weak), enables me later to analyze the interaction between these two manipulations both via between- and within-subjects.
-
-[^footnote_symbols_manipulation_checks]: In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
-The results of these examinations are reported in the supplementary appendix.
-
-Each policy plan was followed by six questions questions about respondents' trust in the policy.
-Afterwards, the subjects conducted a memory test on the last policy that was presented to them, and were asked about the extent to which they elaborated on it and about the personal relevance of the policy plans.
-Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence.
-After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities.
-Finally, the participants were debriefed about the manipulations, and the possible deception.
-An English translation of the full survey is available from the supplementary appendix.
-
-Altogether, for each policy plan, the survey experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs.
-weak policy).
-The assignment to the different experimental groups is graphically presented in **Figure 3**.
-The experimental groups are fairly balanced with respect to demographics, and pre-manipulation variables.
-Throughout the rest of the paper, I will analyze the results at the policy level, in order to simplify the analyses.
-Accordingly, I transformed the dataset into a multilevel structure of policies nested within subjects.[^footnote_combined_analyses]
-
-[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while adding the interactions between the manipulations and the policy plans.
-In these models, the interactions between the policy plans and the symbols are far from significance, with no major changes to the results.
+## *Procedure*
 
@@
 **Figure 3: Experimental design for policy plan communications**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow.png)
+<br>
 
-The survey experiment was conducted online through Qualtrics Survey Software.
-To subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*.
-The online survey link was sent by iPanel, between 28.1-1.2.2018 to 5,077 people.
-A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
-These filters are not significantly associated with the experimental conditions.
-Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb%>%nrow()` observations nested within these `r N_1` subjects.
-
-[^footnote_responserate]: According to iPanel's reporting, 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample.
-Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
-
-[^footnote_sample_areas]: To capture variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country.
-The final sample consists of `r SVIVA2_01_haifa%>%nrow()` subjects from the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` from the center cities.
-The two areas received the exact same link to the online survey, and they were equally, randomly assigned to the experimental conditions.
-
-##*Operationalization of variables*
-
-```{r, echo=FALSE, warning=FALSE, message=F}
-alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
-                               TRUST_air_q2,
-                               TRUST_air_q3,
-                               TRUST_air_q4,
-                               TRUST_air_q5,
-                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)
-
-alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
-                               TRUST_waste_q2,
-                               TRUST_waste_q3,
-                               TRUST_waste_q4,
-                               TRUST_waste_q5,
-                               TRUST_waste_q6))[["total"]][["raw_alpha"]]%>%round(2)
-
-alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2)%>%round(2)
-
-cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate%>%mean()%>%round(2)
-
-cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate%>%mean()%>%round(2)
-
-cor_RT_delta = cor.test(SVIVA2_01$ELABORATION_total_time_log,
-                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
-
-cor_memory_delta = cor.test(SVIVA2_01$MEMORY_total,
-                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
-
-t_air_information = t.test(TRUST_air_INDEX~INFORMATION_air,SVIVA2_01)
-t_waste_information = t.test(TRUST_waste_INDEX~INFORMATION_waste,SVIVA2_01)
-
-```
-
-My main independent variables are the above mentioned manipulations for information and symbols, and the interaction between them.
-My outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy).
-This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_waste_trust`), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
-Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-The mean of this trust index is `r SVIVA2_01_comb%>%summarise(mean(trust))%>%max()%>%round(2)`, the standard variation is `r SVIVA2_01_comb%>%summarise(sd(trust))%>%max()%>%round(2)` and the median is `r SVIVA2_01_comb%>%summarise(median(trust))%>%max()%>%round(2)`.
-Higher levels of trust are associated with higher trust in government, left-wing ideology and lower levels of education.
-In addition to measuring participants trust in each policy, per each subject, I also calculated the delta between her trust in the strong and weak policy plans which were presented to her (*Mean* = `r SVIVA2_01%>%summarise(mean(WITHIN_DELTA))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()%>%round(2)`, *Median* = `r SVIVA2_01%>%summarise(median(WITHIN_DELTA))%>%max()%>%round(2)`).
-I used this Trust in policy delta to analyze the interaction between symbols and information within subjects.
-
-To assess the levels of thinking or elaboration on the policy plans, I used two distinct measures: First, I counted the number of seconds participants spent on scanning each of the policy plans (hereafter – reaction time), log transformed to reduce skewness (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(ELABORATION_time_log))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(ELABORATION_time_log))%>%max()%>%round(2)`).
-Second, I used a memory test, asking participants whether a list of four items were included in the policy plan, of which two were/were not included (participants could also select "I don't know").
-The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero.
-Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2)%>%round(2)`, which substantiates their validity.
-
-[^footnote_elaboration]: In addition, I included in the survey a battery of five items that measure participants' subjective perception of their level of elaboration.
-I initially sought to use these items as an additional measure for elaboration.
-However, I decided to forgo this subjective measure, due to its lack of correlation with the reaction time and memory test score, and its possible bias by people's disinclination to admit that they did not thoroughly read the policy plans.
-
-In addition to the above independent variables, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in government, interest in environmental issues and residence in the Haifa-Bay area.
-Summary statistics and correlation matrix for all variables are available in the supplementary appendix.
+##*Variables*
 
@@
 
-I now turn to analyzing the experimental results.
-I begin by examining my first and second hypotheses, that regard the effect of symbols on trust and its interaction with information.
-Thereafter, I will examine hypotheses 3 and 4, that regard the mediating role on elaboration.
-For each section, I conducted both *between-subjects* and *within-subjects* analyses.
-
-##*The interaction bewteen symbols and information*
-
-According to my first hypothesis, I expect that the real symbols condition will have a positive main effect on subjects' trust in the policy plans.
-According to my second hypothesis, I expect a positive interaction between the real symbols and weak policy plan.
-Namely, the effect of the real symbols is expected to be greater among those subjects who were assigned to the weak policy.
-In **Table 1**, I test these two hypotheses via regression analyses.
-To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level via `lme4` R package (ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`).
-In Model 1 I regress trust in policy on the symbols manipulation.
-Thereafter, in Models 2 and 3, I add the information manipulation, and the interaction between them.
-In these models, I the reference category for the symbols manipulation is the no-symbols condition.
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-x_realsymbol = filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(trust))%>%max()
-x_fakesymbol = filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(trust))%>%max()
-x_nosymbol = filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(trust))%>%max()
-sd_trust = SVIVA2_01_comb%>%summarise(sd(trust))%>%max()
-
-x_realsymbol_delta = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA))%>%max()
-x_fakesymbol_delta = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA))%>%max()
-x_nosymbol_delta = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA))%>%max()
-sd_trust_delta = SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()
-
-```
-
-**Table 1: Regression analyses – the effect of symbols on trust in policy**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-library(lme4)
-
-mod_1.1 = lmer(trust~SYMBOL_t+(1|IP),data=SVIVA2_01_comb)
-mod_1.2 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-mod_1.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-
-stargazer(mod_1.1,mod_1.2,mod_1.3,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in policy (combined)"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak policy (0=strong policy)",
-                             "Weak policy x Real symbols",
-                             "Weak policy x Fake symbols"),
-          initial.zero = FALSE,
-          omit.stat = c("aic","bic"),
-          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
-Standard errors are in parentheses.
-The reference category for the symbols manipulation conditions is the control no-symbols.",
-          notes.append = FALSE)
-
-mod_1.1.r_1 = lmer(trust~SYMBOL_t.r+(1|IP),data=SVIVA2_01_comb)
-mod_1.2.r_1 = lmer(trust~SYMBOL_t.r+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-mod_1.3.r_1 = lmer(trust~SYMBOL_t.r*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-
-mod_1.3.r_2 = lmer(trust~SYMBOL_t*INFORMATION+(1|IP),data=SVIVA2_01_comb)
-
-mod_1.3.r_3 = lmer(trust~SYMBOL_t.r*INFORMATION+(1|IP),data=SVIVA2_01_comb)
-
-mod_1.3.r_4 = lmer(trust~SYMBOL_t.r_2*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-
-```
-
-&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
-
-The real symbols condition has a positive main effect on trust in Model 1.1.
-The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), and at the 90% level compared with the fake symbols (`r mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`]).
-These differences are equivalent to `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` and `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` standard variations, respectively.
-The graphic elements in the fake symbols condition also increased participants' trust, but to a lesser extent, presumably due to their unfamiliarity, and their weaker positive affect.
-
-In Model 1.2, the effect of the symbols remains intact, and the effect of the weak policy condition is negative and significant (*Coef* = `r mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]).
-In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant.
-The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively).
-When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1, one-tailed).
-Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100)%>%round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]).
-The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05).
-To facilitate the interpretation of this interaction, **Figure 4** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.
-
-**Figure 4: The effect of symbolic elements on trust under weak vs. strong information**
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=6,fig.height=4}
-ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(INFORMATION_n)))+ 
-  theme_classic()+
-  #geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.65),
-               width=0.2,size=0.5,position=position_dodge(0.1),color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = INFORMATION_n,linetype=INFORMATION_n),position=position_dodge(0.1))+
-  scale_shape_manual(guide=F,values=c(19,1))+
-  scale_linetype_manual(name="Information",values=c(1,4),labels=c("Weak policy","Strong policy"))+
-  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
-```
-
-<font size="0.5">
-
-*Note*: Error bars represent 90% confidence intervals.
-
-</font>
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-
-x_realsymbol_delta=filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA))%>%max()
-x_fakesymbol_delta=filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA))%>%max()
-x_nosymbol_delta=filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA))%>%max()
-
-t_delta_symbol_nosymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=1))
-t_delta_symbol_fakesymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=0))
-t_delta_nosymbol_fakesymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=2))
-
-```
-
-The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions.
-Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition.
-This comparison is graphically displayed in **Figure 5**.
-The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively).
-The differences between the two control groups are insignificant.
-These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.
-
-**Figure 5: The effect of symbolic elements on within-subject delta between strong and weak policies**
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=4,fig.height=4}
-ggplot(SVIVA2_01, aes(factor(SYMBOL_n), WITHIN_DELTA))+
-  theme_classic()+
-  #geom_boxplot(width=0.25,color = "gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-                              fun.args = list(mult = 1.65),
-                              width=0.1,size=0.5,color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=2)+
-  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
-  scale_x_discrete(name="Symbolic elements",labels=c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Within subject delta", breaks = seq(0,1,by=0.1))
-
-```
-
-<font size="0.5">
-
-*Note*: Error bars represent 90% confidence intervals.
-
-</font>
-
-Altogether, the above between- and within-subject analyses largely support my first two hypothesis.
-They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications.
-Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.
-In other statistical models, shown in the supplementary appendix, I tested additional specifications, including analyzing the unfilterred sample, adding control variables, excluding subjects who did not recognize the real symbols and adding interactions with the policy plans.
-In all these robust analyses, the main effect of the real symbols remains positive and significant, and the interaction between the real symbols and the weak information remains positive and significant.
-
-How can we explain the finding that the real symbols only had a marginally significant effect on participants' trust in the strong policy, compared with the no logo, and did not increase their trust compared with the fake logo (Model 1.3)?
-One tentative explanation could be that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels.
-Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
-If this explanation holds, then result will be a ceiling effect.
-This explanation can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
-Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceiling_effect]
-
-[^footnote_ceiling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups.
-The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
-the lower 25% observations).
-In the weak policy condition, the first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[2])%>%max()%>%round(1)` points compared with the no symbols, whereas the third quartile (i.e.
-the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[4])%>%max()%>%round(1)` points.
-In the strong policy condition, we can find similar pattern of decreasing marginal effect.
-The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile (i.e.
-the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.
-
-##*The mediating role of elaboration*
-
-In the following section, I test the postulation that the interaction between symbols and information is explained or mediated by a decrease in elaboration.
-To reiterate, in the survey, I used reaction time (log) and memory score as measures for participants' level of elaboration of the policy plans.
-Based on my third hypothesis, I expect to find a negative effect of the real symbols on these two measures.
-Thereafter, my fourth hypothesis entails moderated mediation relations: the decrease in elaboration mediates the effect of symbols of trust under the weak policy, but not under the strong policy (see Figure 1).
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-x_realsymbol_RT=filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(ELABORATION_time))%>%max()
-x_fakesymbol_RT=filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(ELABORATION_time))%>%max()
-x_nosymbol_RT=filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(ELABORATION_time))%>%max()
-
-t_RT_symbol_nosymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=1))
-t_RT_symbol_fakesymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=0))
-t_RT_nosymbol_fakesymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=2))
-
-x_realsymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(ELABORATION_time_log))%>%max()
-x_fakesymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(ELABORATION_time_log))%>%max()
-x_nosymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(ELABORATION_time_log))%>%max()
-
-cor_memory_nosymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=1)$SYMBOL),
-                               filter(SVIVA2_01_comb,SYMBOL!=1)$MEMORY_score, 
-                               method="spearman")$estimate%>%mean()%>%round(2)
-
-cor_memory_fakesymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=0)$SYMBOL),
-                               filter(SVIVA2_01_comb,SYMBOL!=0)$MEMORY_score, 
-                               method="spearman")$estimate%>%mean()%>%round(2)
-```
-
-In **Table 2**, I test the effects of the real symbols on the elaboration measures via regression analyses.
-I regressed each measure on the symbols manipulation (Models 2.1, 2.3), and than added the information manipulation (Models 2.2, 2.4).
-The first two models, which refer to reaction time, are random intercept models which are similar to the statistical models in table 1.
-As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression.
-
-**Table 2: Regression analyses – the effect of symbols on elaboration**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_2.1 = lmer(ELABORATION_time_log~SYMBOL_t+(1|IP),data=SVIVA2_01_comb)
-mod_2.2 = lmer(ELABORATION_time_log~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-mod_2.3 = lm(MEMORY_score~SYMBOL_t,data=SVIVA2_01_comb)
-mod_2.4 = lm(MEMORY_score~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
-
-stargazer(mod_2.1,mod_2.2,mod_2.3,mod_2.4,
-          type="html",style = "apsr",
-          dep.var.labels=c("Reaction time (log)","Memory score"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak policy (0=strong policy)"),
-          initial.zero = FALSE,
-          omit.stat = c("f","ser","aic","bic"),
-          notes = "*Notes*: Table entries are non-standardized regression coefficients.
-Standard errors are in parentheses.
-The reference category for the symbols manipulation conditions is the control no-symbols.",
-          notes.append = FALSE)
-
-mod_2.1.r_1 = lmer(ELABORATION_time~SYMBOL_t.r+(1|IP),data=SVIVA2_01_comb)
-
-mod_2.3.r_1 = lm(MEMORY_score~SYMBOL_t.r,data=SVIVA2_01_comb)
-
-```
-
-&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
-
-In all four models, the coefficients of the real symbols are negative and significant, and the coefficients of the fake symbols are insignificant.
-The real symbols decreased the number of second subjects spent on the pages of the policy plans in the online survey, compared with both control groups.[^footnote_RT_symbols] The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), yet it is not sufficiently significant compared with the fake symbols.
-The averaged memory score of subjects who saw the real symbols was significantly lower, compared with both the no logo and the fake logo groups (*Coef* = `r mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`], and `r mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`], respectively).[^footnote_memory_symbols] There is no significant change to the results when adding the the effects of the information manipulation (in Models 2.2, 2.4).
-The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them.
-**Figure 6** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions.
-The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.
-
-[^footnote_RT_symbols]: The difference in seconds compared with the no symbols group, as extracted from the coefficients in logs is: `r (mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())%>%abs()%>%exp()%>%round(1)`-`r (x_realsymbol_RT_log-x_fakesymbol_RT_log)%>%abs()%>%exp()%>%round(1)`.
-The difference between the raw averages is `r (x_realsymbol_RT-x_fakesymbol_RT)%>%abs()%>%round(1)` seconds.
-
-[^footnote_memory_symbols]: Descriptively, `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% of those in the real symbols group received the minimum score of 0, compared with `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the no symbols and fake symbols control groups.
-Congruently, the percentage of those who managed to correctly identify the two items dropped from `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the control groups to only `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`%.
-Given that the measure of memory score is ordinal, I also tested it's correlation with the symbols manipulation via Spearman test.
-Spearman rho = `r cor_memory_nosymbol` and `r cor_memory_fakesymbol`, compared with the no symbols and fake symbols control groups.
-
-**Figure 6: The effect of symbolic elements on elaboration**
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=4,fig.height=4}
-ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), ELABORATION_time_log))+
-  theme_classic()+
-  #geom_boxplot(width=0.25,color = "gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-                              fun.args = list(mult = 1.65),
-                              width=0.1,size=0.5,color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.5)+
-  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
-  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
-  scale_y_continuous(name = "Reaction Time (log)")
-
-ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), MEMORY_score))+
-  theme_classic()+
-  #geom_boxplot(width=0.25,color = "gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-                              fun.args = list(mult = 1.65),
-                              width=0.1,size=0.5,color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.5)+
-  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
-  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
-  scale_y_continuous(name = "Memory score")
-```
-
-<font size="0.5">
-
-*Note*: Error bars represent 90% confidence intervals.
-
-</font>
-
-Next, I tested the hypothesis that the decrease in reaction time and memory score mediate the effect of the real symbols on trust in the weak policy plans.
-To do so, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al.
-[@imai_2010; @imai_2011], and was also recently also implemented in Public Administration research [@porumbescu_2018].
-This method predicts the change in the outcome variable (here: trust in policy) given the causal change in the mediator that would be induced by the treatment (here: decreased elaboration inducted by the real symbols).
-Accordingly, it enables to decipher the proportion of the causal mediation effect from the total effect.
-Causal mediation analysis is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling.
-It is advantaged in terms of its accuracy as well as its ability to identify causality.
-**Table 3** displays the results of the causal mediation of reaction time (log) and memory test, under the weak policy plans.
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-library(mediation)
-set.seed(2018)
-
-#RT
-med.fit_RT_nosymbol = 
-  lm(ELABORATION_time_log~SYMBOL*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=1))
-
-med.out_RT_nosymbol = 
-  lm(trust~SYMBOL*INFORMATION+ELABORATION_time_log*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=1))
-
-med.fit_RT_fakesymbol = 
-  lm(ELABORATION_time_log~SYMBOL*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=0))
-
-med.out_RT_fakesymbol = 
-  lm(trust~SYMBOL*INFORMATION+ELABORATION_time_log*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=0))
-
-med_RT__nosymbol_INFORMTION_0 = mediate(med.fit_RT_nosymbol,
-                                med.out_RT_nosymbol,
-                                treat = "SYMBOL",
-                                mediator = "ELABORATION_time_log", 
-                                covariates = list(INFORMATION = 0), sims = 100)
-
-med_RT__fakesymbol_INFORMTION_0 = mediate(med.fit_RT_fakesymbol,
-                                  med.out_RT_fakesymbol,
-                                  treat = "SYMBOL",
-                                  mediator = "ELABORATION_time_log", 
-                                  covariates = list(INFORMATION = 0), sims = 100)
-
-med_RT__nosymbol_INFORMTION_1 = mediate(med.fit_RT_nosymbol,
-                                med.out_RT_nosymbol,
-                                treat = "SYMBOL",
-                                mediator = "ELABORATION_time_log", 
-                                covariates = list(INFORMATION = 1), sims = 100)
-
-med_RT__fakesymbol_INFORMTION_1 = mediate(med.fit_RT_fakesymbol,
-                                  med.out_RT_fakesymbol,
-                                  treat = "SYMBOL",
-                                  mediator = "ELABORATION_time_log", 
-                                  covariates = list(INFORMATION = 1), sims = 100)
-
-#memory
-med.fit_memory_nosymbol = 
-  lm(MEMORY_score~SYMBOL*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=1))
-
-med.out_memory_nosymbol = 
-  lm(trust~SYMBOL*INFORMATION+MEMORY_score*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=1))
-
-med.fit_memory_fakesymbol = 
-  lm(MEMORY_score~SYMBOL*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=0))
-
-med.out_memory_fakesymbol = 
-  lm(trust~SYMBOL*INFORMATION+MEMORY_score*INFORMATION,
-     data=filter(SVIVA2_01_comb,SYMBOL!=0))
-
-med_memory__nosymbol_INFORMTION_0 = mediate(med.fit_memory_nosymbol,
-                                med.out_memory_nosymbol,
-                                treat = "SYMBOL",
-                                mediator = "MEMORY_score", 
-                                covariates = list(INFORMATION = 0), sims = 100)
-
-med_memory__fakesymbol_INFORMTION_0 = mediate(med.fit_memory_fakesymbol,
-                                  med.out_memory_fakesymbol,
-                                  treat = "SYMBOL",
-                                  mediator = "MEMORY_score", 
-                                  covariates = list(INFORMATION = 0), sims = 100)
-
-med_memory__nosymbol_INFORMTION_1 = mediate(med.fit_memory_nosymbol,
-                                med.out_memory_nosymbol,
-                                treat = "SYMBOL",
-                                mediator = "MEMORY_score", 
-                                covariates = list(INFORMATION = 1), sims = 100)
-
-med_memory__fakesymbol_INFORMTION_1 = mediate(med.fit_memory_fakesymbol,
-                                  med.out_memory_fakesymbol,
-                                  treat = "SYMBOL",
-                                  mediator = "MEMORY_score", 
-                                  covariates = list(INFORMATION = 1), sims = 100)
-
-extract_mediation_summary <- function (x) {
-
-  clp <- 100 * x$conf.level
-  isLinear.y <- ((class(x$model.y)[1] %in% c("lm", "rq")) || 
-                   (inherits(x$model.y, "glm") && x$model.y$family$family == 
-                      "gaussian" && x$model.y$family$link == "identity") || 
-                   (inherits(x$model.y, "survreg") && x$model.y$dist == 
-                      "gaussian"))
-
-  printone <- !x$INT && isLinear.y
-
-  if (printone) {
-
-    smat <- c(x$d1, x$d1.ci, x$d1.p)
-    smat <- rbind(smat, c(x$z0, x$z0.ci, x$z0.p))
-    smat <- rbind(smat, c(x$tau.coef, x$tau.ci, x$tau.p))
-    smat <- rbind(smat, c(x$n0, x$n0.ci, x$n0.p))
-
-    rownames(smat) <- c("ACME", "ADE", "Total Effect", "Prop. Mediated")
-
-  } else {
-    smat <- c(x$d0, x$d0.ci, x$d0.p)
-    smat <- rbind(smat, c(x$d1, x$d1.ci, x$d1.p))
-    smat <- rbind(smat, c(x$z0, x$z0.ci, x$z0.p))
-    smat <- rbind(smat, c(x$z1, x$z1.ci, x$z1.p))
-    smat <- rbind(smat, c(x$tau.coef, x$tau.ci, x$tau.p))
-    smat <- rbind(smat, c(x$n0, x$n0.ci, x$n0.p))
-    smat <- rbind(smat, c(x$n1, x$n1.ci, x$n1.p))
-    smat <- rbind(smat, c(x$d.avg, x$d.avg.ci, x$d.avg.p))
-    smat <- rbind(smat, c(x$z.avg, x$z.avg.ci, x$z.avg.p))
-    smat <- rbind(smat, c(x$n.avg, x$n.avg.ci, x$n.avg.p))
-
-    rownames(smat) <- c("ACME (control)", "ACME (treated)", 
-                        "ADE (control)", "ADE (treated)", "Total Effect", 
-                        "Prop. Mediated (control)", "Prop. Mediated (treated)", 
-                        "ACME (average)", "ADE (average)", "Prop. Mediated (average)")
-
-  }
-
-  colnames(smat) <- c("Estimate", paste(clp, "% CI Lower", sep = ""), 
-                      paste(clp, "% CI Upper", sep = ""), "p-value")
-  smat
-
-}
-
-```
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-#RT
-table_med_RT__nosymbol_INFORMTION_0 = 
-summary(med_RT__nosymbol_INFORMTION_0)%>%
-extract_mediation_summary()
-
-table_med_RT__fakesymbol_INFORMTION_0 = 
-summary(med_RT__fakesymbol_INFORMTION_0)%>%
-extract_mediation_summary()
-
-table_med_RT__nosymbol_INFORMTION_1 = 
-summary(med_RT__nosymbol_INFORMTION_1)%>%
-extract_mediation_summary()
-
-table_med_RT__fakesymbol_INFORMTION_1 = 
-summary(med_RT__fakesymbol_INFORMTION_1)%>%
-extract_mediation_summary()
-
-#memory
-table_med_memory__nosymbol_INFORMTION_0 = 
-summary(med_memory__nosymbol_INFORMTION_0)%>%
-extract_mediation_summary()
-
-table_med_memory__fakesymbol_INFORMTION_0 = 
-summary(med_memory__fakesymbol_INFORMTION_0)%>%
-extract_mediation_summary()
-
-table_med_memory__nosymbol_INFORMTION_1 = 
-summary(med_memory__nosymbol_INFORMTION_1)%>%
-extract_mediation_summary()
-
-table_med_memory__fakesymbol_INFORMTION_1 = 
-summary(med_memory__fakesymbol_INFORMTION_1)%>%
-extract_mediation_summary()
-```
-
-**Table 3: Causal mediation analysis**
-
-*Mediator: Reaction time*
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-table_med_RT_INFORMTION_0 = 
-  cbind.data.frame(table_med_RT__nosymbol_INFORMTION_0,
-                   table_med_RT__fakesymbol_INFORMTION_0)
-library(kableExtra)
-
-kable(table_med_RT_INFORMTION_0, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
-  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
-```
-
-*Mediator: Memory score*
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-table_med_memory_INFORMTION_0 = 
-  cbind.data.frame(table_med_memory__nosymbol_INFORMTION_0,
-                   table_med_memory__fakesymbol_INFORMTION_0)
-
-kable(table_med_memory_INFORMTION_0, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
-  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
-```
-
-*Notes*: "ACME": Averaged causal mediated effect; "ADE": Averaged direct effect. Mediate function uses bootstrap to estimate the confidence intervals. In all these analyses I used `set.seed=2018`.
-
-The results suggest that the decreased reaction time significantly mediates the effect of the real symbols on trust in the weak policies.
-The estimated proportion of the mediation is `r (table_med_RT__nosymbol_INFORMTION_0["Prop.
-Mediated","Estimate"]*100)%>%round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_INFORMTION_0["Prop.
-Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols.
-The decreased memory score also mediates the effect (*p*<.1), but only compared with the no symbols group.[^footnote_mediation_memory]
-
-[^footnote_mediation_memory]: The differences between the analyses of the two measures can be also explained by the fact that memory score is calculated with regard to half of the observations.
-
-Finally, I also tested this moderated mediation hypothesis via within-subjects analysis.
-Given that each subject represents one observation, the memory score remains the same, and for the reaction time, I summed the number of seconds subjects spent on both policies (log transformed).
-The results of this causal mediation analysis are summarized in **Table 4**.
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-med.fit_RT_nosymbol_delta = 
-  lm(ELABORATION_total_time_log~SYMBOL,
-     data=filter(SVIVA2_01,SYMBOL!=1))
-
-med.out_RT_nosymbol_delta = 
-  lm(WITHIN_DELTA~SYMBOL+ELABORATION_total_time_log,
-     data=filter(SVIVA2_01,SYMBOL!=1))
-
-med.fit_RT_fakesymbol_delta = 
-  lm(ELABORATION_total_time_log~SYMBOL,
-     data=filter(SVIVA2_01,SYMBOL!=0))
-
-med.out_RT_fakesymbol_delta = 
-  lm(WITHIN_DELTA~SYMBOL+ELABORATION_total_time_log,
-     data=filter(SVIVA2_01,SYMBOL!=0))
-
-med_RT__nosymbol_delta = mediate(med.fit_RT_nosymbol_delta,
-                                med.out_RT_nosymbol_delta,
-                                treat = "SYMBOL",
-                                mediator = "ELABORATION_total_time_log", 
-                                sims = 100)
-
-med_RT__fakesymbol_delta = mediate(med.fit_RT_fakesymbol_delta,
-                                med.out_RT_fakesymbol_delta,
-                                treat = "SYMBOL",
-                                mediator = "ELABORATION_total_time_log", 
-                                sims = 100)
-
-med.fit_memory_nosymbol_delta = 
-  lm(MEMORY_total~SYMBOL,
-     data=filter(SVIVA2_01,SYMBOL!=1))
-
-med.out_memory_nosymbol_delta = 
-  lm(WITHIN_DELTA~SYMBOL+MEMORY_total,
-     data=filter(SVIVA2_01,SYMBOL!=1))
-
-med.fit_memory_fakesymbol_delta = 
-  lm(MEMORY_total~SYMBOL,
-     data=filter(SVIVA2_01,SYMBOL!=1))
-
-med.out_memory_fakesymbol_delta = 
-  lm(WITHIN_DELTA~SYMBOL+MEMORY_total,
-     data=filter(SVIVA2_01,SYMBOL!=1))
-
-med_memory__nosymbol_delta = mediate(med.fit_memory_nosymbol_delta,
-                                med.out_memory_nosymbol_delta,
-                                treat = "SYMBOL",
-                                mediator = "MEMORY_total", 
-                                sims = 100)
-
-med_memory__fakesymbol_delta = mediate(med.fit_memory_fakesymbol_delta,
-                                med.out_memory_fakesymbol_delta,
-                                treat = "SYMBOL",
-                                mediator = "MEMORY_total", 
-                                sims = 100)
-```
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-#RT
-table_med_RT__nosymbol_delta = 
-summary(med_RT__nosymbol_delta)%>%
-extract_mediation_summary()
-
-table_med_RT__fakesymbol_delta = 
-summary(med_RT__fakesymbol_delta)%>%
-extract_mediation_summary()
-
-#memory
-table_med_memory__nosymbol_delta = 
-summary(med_memory__nosymbol_delta)%>%
-extract_mediation_summary()
-
-table_med_memory__fakesymbol_delta = 
-summary(med_memory__fakesymbol_delta)%>%
-extract_mediation_summary()
-```
-
-**Table 4: Causal mediation analysis (within subjects)**
-
-*Mediator: Reaction time*
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-table_med_RT_delta = 
-  cbind.data.frame(table_med_RT__nosymbol_delta,
-                   table_med_RT__fakesymbol_delta)
-
-kable(table_med_RT_delta, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
-  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
-```
-
-*Mediator: Memory score*
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-table_med_memory_delta = 
-  cbind.data.frame(table_med_memory__nosymbol_delta,
-                   table_med_memory__fakesymbol_delta)
-
-kable(table_med_memory_delta, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
-  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
-```
-<br>
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-t1<- medsens(med_RT__nosymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect", 
-             sims = 100)
-t2<- medsens(med_RT__fakesymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect", 
-             sims = 100)
-
-t3<- medsens(med_memory__nosymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect",              sims = 100)
-
-t4<- medsens(med_RT__nosymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
-
-t5<- medsens(med_RT__fakesymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
-
-t6<- medsens(med_memory__nosymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
-
-t7<- medsens(med_memory__fakesymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
-
-#summary(t1)
-```
-
-The results of the within subjects mediation analysis similarly supports the moderated mediation hypothesis.
-The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction the time and the memory score.
-With respect to the reaction time, the estimated proportional mediation is `r (table_med_RT__nosymbol_delta["Prop.
-Mediated","Estimate"]*100)%>%round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_delta["Prop.
-Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols.
-Regarding the memory score,the estimated proportional mediation is `r (table_med_memory__nosymbol_delta["Prop.
-Mediated","Estimate"]*100)%>%round(1)`% and `r (table_med_memory__fakesymbol_delta["Prop.
-Mediated","Estimate"]*100)%>%round(1)`%, respectively.[^footnote_mediation_sensitivity]
-
-[^footnote_mediation_sensitivity]: I also conducted a robustness test of "formal sensitivity" for the significant causal mediation models, as proposed by Imai et al.
-[-@imai_2010].
-The sensitivity test examines the extent to which the causal mediation would change as a result of a correlation between the error terms of the mediator and the outcome variable (the "sequential ignorability" assumption).
-With regard to mediation by reaction time, the sensitivity factors range between 0.2-0.3, which suggest that a correlation greater than these values would violate the sequential ignorability assumption.
-Imai et al.
-did not offer any rule of thumb with regard to these factors.
-Yet, these results are consistent with sensitivity factors reported in previous studies, and therefore the mediation can be considered fairly reliable.
-The sensitivity factors for the mediation by the memory score are 0.1, which entails that it is less reliable.
-
-Altogether, the between- and within-subjects analyses are consistent with my third and fourth hypotheses.
-They demonstrate that subjects who saw the policy plans with the familiar symbols of EPM, were less likely to elaborate on the content of the EPM policies, which in turn attenuated the negative effect of the weak information, and increased their trust in the weak policies.
-The partial mediation by reaction time is strongly significant, whereas the mediation by the memory test is not sufficiently significant in all models.
-In some of these models, the familiar symbols also had a significant direct positive effect, which can be theoretically explained by the peripheral effect of symbols via transfer of affect, in accordance with my first hypothesis.
-
 #Discussion and conclusion
-
-A growing body of Public-Administration research seeks to assess whether and how government organizations can increase citizens' trust through direct communications with citizens.
-This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect.
-Using a rigorous experimental design, embedded in a realistic setting focused on the case of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications.
-To the best of my knowledge, this is the first study to explore this interactions in the context of government communications.
-
-I found that participants' exposure to the familiar symbols of EPM increased their trust in its policy plans, and that the effect was greater when they were presented with a weak policy plan.
-The latter interaction is partly explained by the negative effect of the symbols on the elaboration of the policy plans.
-These findings are based the analyses of the responses of more than `r (SVIVA2_01%>%nrow()%>%round(-2))-100` participants to two different policies, and are robust for various model specifications.
-Moreover, they are evidenced in both between- and within-subjects analysis.
-These results, if generalizable, suggest that incorporating familiar symbolic elements in public communications increase citizens' trust in government organizations and their actions, via two mechanisms: First, they evoke general positive feelings that are transferred to the specific organizations and policies.
-Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thereby, they cause them to disregard its weaknesses.
-These two supplementary mechanisms are theorized using the framework of the social psychology elaboration likelihood model [@petty_1986; @petty_2011].
-
-Certainly, we must be cautious when drawing general conclusions from our findings.
-This study focuses, empirically, on one public organization, characterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians.
-Future studies may further examine the proposed theory by focusing on additional cases of public organizations and policy areas.
-In addition, this study focuses on policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.
-Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information on good/bad outcomes.
-Another limitation of the study regards the fact that it examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol.
-Future studies may compare the effectiveness of different types of symbolic elements.
-
-Keeping these limitations in mind, this study has several important implications for public administration research.
-Most importantly, my findings highlight the significant role of branding and symbolic communication in shaping citizens' attitudes about government.
-Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abounded research on their responses to information.
-Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-Furthermore, my findings suggest that symbols decrease citizens' "rational", systematic processing of substantive information.
-This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information.[^footnote_biases_ELM].
-On the other hand, the emotive effect of government symbols on public opinion is highly problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
-Moreover, it becomes especially problematic when symbols are used by poorly performing organizations, or organizations that lack professional expertise.
-It those cases, symbolic elements can mitigate justified public criticism of government failures.
-Ultimately, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which provides them political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
-Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, organizations can also use it as a means to undermine them.
-
-[^footnote_biases_ELM]: This possibility is supported, theoretically, by ELM.
-According to ELM, biased processing occurs in the central route, whereby people give proportional weight for strong or weak arguments.
-Accordingly, decreasing the amount of thinking may also decrease biased processing [@petty_1986].
-Future research might put this expectation to test.
-
-This study also contributes to existing behavioral Public Administration research by introducing ELM and applying it as a comprehensive theoretical framework for studying citizens' attitudes formation, and citizens' responses to government communications.
-ELM has various postulations and implications, but most importantly, it stresses that people respond differently to different communications, depending on people's motivation and ability to think about the subject, and on the quality of arguments and the peripheral cues in the communication.
-In this study, I applied ELM to theorize the direct and indirect effects of symbolic elements on trust.
-Future Public-Administration studies may apply ELM and further explore the effects of other peripheral, heuristic cues in government communications, and the moderating role of motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
-Future studies may also examine the postulations of ELM that persuasion via arguments is more likely to be enduring,  and to increase citizens' cooperation with government policies, compared with persuasion via symbolic elements and heuristic cues.
-
-Finally, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications.
-The participants of these studies, including this particular one, have relatively high motivation to elaborate on the information that scholars presented them, because they may assume that they will be asked about it afterwards.
-In case they receive payment or other compensation for their participation, this further increases their motivation.
-By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they probably also have lower ability to do so, given the high competition on their time and attention.
-Accordingly, their responses to performance information will less affected by asymmetrical processing of information, because most of them are not likely to process this information in the first place.
-Instead, most of them will rely on simple cues and heuristic shortcuts.
-I expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2017; @olsen_2017].
-Future studies may empirically explore these interactions.
-Regardless, scholars should also take to account this methodological issue when designing survey experiments, and attempt to simulate real world conditions, as much as possible.
-For instance, they can add filler sections in the survey before the real manipulation to attenuate participants' motivation and ability to elaborate.
-In addition, because the graphic design of communications also affects motivation and ability to elaborate, as shown here, scholars should simulate the design of real communications.
 

### 2018-06-21 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 ---
-title: "Does high personal relevance mitigate the effect of symbolic elements in government public communications?"
+title: "Does high personal relevance mitigate the persuasion of symbolic elements in government public communications?"
 author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
@@
 Building on the social psychology Elaboration Likelihood Model (ELM), I theorize that citizens are less susceptible to symbols when they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to invest in elaborate processing.
-I put this theory to test through a survey experiment, where I examine circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens' trust in the Environment Protection Ministry's policies for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
+I put this theory to test through a survey experiment, where I examine circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
 I operationalize personal relevance both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
@@
 
-While the abovementioned studies have substantiated the distinct effect of symbols, they did not theorize, nor empirically examine the conditions under which are these symbols are likely to be more/less effective in persuading citizens.
-The research gap has great significance.
-From the organizations' practical point of view, ...
+While the abovementioned studies have substantiated the distinct effect of symbols, they did not theorize, nor they empirically examined the conditions under which are these symbols are likely to be more/less effective in persuading citizens.
+This research gap has great significance.
+From the practical point of view of public organizations, this may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
+Employing a broader perspective of normative democratic theory, the emotive effect of symbols can be perceived as problematic.
+It stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking.
+Morover, as argued by @alonbarkat_2017, symbolic communication may elicit undue trust in poorly performing organizations, and enable public organizations to escape justified public criticism.
+Hence, by understanding when citizens are more/less likely to be affected by symbols, we may be able to better assess the potential risk for governments' manipulative use of symbolic communications.
 
-Employing a broader, democratic normative stance, we should be also concerned from the effect of symbols.
-Symbolic elements can elicit undue trust in poorly performing organizations and in ill-conceived policies.
-Accordingly, it may enable public organizations to escape justified public criticism [@alonbarkat_2017].
-Hence, by understanding when citizens are more likely to be affected by symbols, we  may enable us to identify the
-
-Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *under what conditions do symbolic elements  increase citizens' trust in governemnt policy?* And specifically, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
-
-To address these research questions, I draw upon the social psychology Elaboration Likelihood Model (ELM).
-ELM provides a comprehensive theoretical framework for the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences for attitude change  [@petty_1986; @petty_2011].
-Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
-I expect that this effect is attenuated the more citizens perceive the communications as personally relevant, because they are more motivated to think about their messages.
-*Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
-
-To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow() %>% round(-1)` Israeli citizens.
-The experiment focuses on the empirical case of the Israeli Environment Protection Ministry.
-I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information of the communications (logically persuasive vs.
-unpersuasive policy plans) and by symbolic elements in them (real symbols vs.
-fake symbols and no symbols conditions).
-In addition, I examine the moderating role of the perceived personal relevance of these policies.
-
-I find that the symbolic elements increased citizens' trust in these policies.
-In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about its content.
-I did not find support for the hypothesis that the effect of the symbolic elements is attenuated by the perceived personal relevance of the policy issue.
-I discuss the theoretical and normative implications of these findings.
+To address this literature gap, I draw upon the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
+I hypothesize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to invest in elaborate processing.
+Similarly, higher perceived personal relevance are expected to enhance citizens' inclincation to scrutinize the substantive content of communication.
+Employing a survey experiment, I test this hypothesis in the context of the Israeli Environment Protection Ministry, and its policy plans for reducing the air pollution in a specific area (the Haifa-Bay) and for reducing domestic waste.
+I operationalize personal relevance both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
 
@@
 
->*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*
+*H<sub>1</sub> - Symbolic elements in communications are less (more) likely to increase citizens' trust in governemnt organizations and policicies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
 
->*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
-
->*H<sub>3</sub> - Symbolic elements are likely to decrease the amount of thinking about the content of the communication.*
-
->*H<sub>4</sub> - The abovementioned conditioned effect of symbolic elements on citizens' trust is likely to be mediated by the decrease in the amount of thinking (a moderated mediation hypothesis).*
+*H<sub>2</sub> - The logical quality of the communication is more (less) likely to affect citizens' trust in governemnt organizations and policicies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
 

### 2018-07-01 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 ---
-title: "Does high personal relevance mitigate the persuasion of symbolic elements in government public communications?"
+title: "The persuasion of symbolic elements in government public communications, and their moderation by personal relevance"
 author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
@@
 
-*Previous public administration studies have examined whether public communications can affect citizens trust in government organizations and their policies.
-Recent experimental studies have demonstrated that these communications can enhance trust not only by conveying substantive information, but also by incorporating strategically desigened symbolic element that evoke positive feelings and associations (e.g.
-logos, images and celebrities).
-Still, under which conditions are citizens more/less likely to be emotionally persuaded by these symbols?
+*Recent experimental studies have demonstrated that government public communications can enhance citizens' trust in government organizations and their policies not only by conveying substantive information, but also by incorporating strategically desigened symbolic element that evoke positive feelings and associations.
+Yet, under which conditions are citizens more/less likely to be emotionally persuaded by these symbols?
 Building on the social psychology Elaboration Likelihood Model (ELM), I theorize that citizens are less susceptible to symbols when they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to invest in elaborate processing.
-I put this theory to test through a survey experiment, where I examine circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
-I operationalize personal relevance both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
-The experimental results do not support the hypothesis that higher personal relevance attenuates the effect of symbols.
+I put this theory to test through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing the air pollution in a specific area (the Haifa-Bay) and for reducing domestic waste.
+I operationalize the perceived personal relevance of these policies both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+The results of both methods do not support the hypothesis that higher personal relevance attenuates the effect of symbols.
 They tentatively suggest that symbols are more likely to persuade citizens who have predominant negative attitudes.*
@@
 
-Public administration scholars have explored whether government organizations can enhance citizens' trust in them by employing public communications.
-Whereas most of the studies on the effect of government public communications on citizens attitudes has focused on the *informative* aspects of these communications [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @grimmelikhuijsen_2015; @ho_2017], recent experimental studies further pointed to the emotive effect of *symbolic* elements that are entangled in government communications, such as  agencies' names [@teodoro_2018], brand logos [@karens_2016], and figures in public campaigns [@alonbarkat_2017].
-These studies demonstrated that these familiar and well-designed symbolic elements can enhance citizens' trust irratioanlly through a mechanism of "evaluative conditioning" - unconscious transfer of affect from the symbols to the public organizations and policies associated with them [@dehouwer_2012].
+A growing public administration literature explores whether government public communications can enhance citizens' trust in public organizations and policies.
+Whereas most of the studies have focused on the *informative* aspects of government communications [e.g.
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @grimmelikhuijsen_2015; @ho_2017], recent experimental studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as  brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
+The latter studies suggested that that familiar and well-designed symbols can enhance citizens' trust irrationally through a mechanism of "evaluative conditioning" - unconscious transfer of affect from the symbols to the public organizations and policies associated with them [@dehouwer_2012].
+Understanding the effect of symbolic elements is important, insofar as they exist in almost any communications between public organizations and citizens, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
 
-While the abovementioned studies have substantiated the distinct effect of symbols, they did not theorize, nor they empirically examined the conditions under which are these symbols are likely to be more/less effective in persuading citizens.
+While previous studies have substantiated the distinct effect of symbols on citizens' trust, they did not theorize, nor they empirically examined the conditions under which are these symbols are likely to be more/less effective.
 This research gap has great significance.
-From the practical point of view of public organizations, this may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
-Employing a broader perspective of normative democratic theory, the emotive effect of symbols can be perceived as problematic.
-It stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking.
-Morover, as argued by @alonbarkat_2017, symbolic communication may elicit undue trust in poorly performing organizations, and enable public organizations to escape justified public criticism.
-Hence, by understanding when citizens are more/less likely to be affected by symbols, we may be able to better assess the potential risk for governments' manipulative use of symbolic communications.
+First, from the practical point of view of government organizations, this may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
+Second, employing a broader perspective of democratic theory, one can argue that the emotive effect of symbols challenges the fundamental normative expectation that citizens' judgments should be based on their critical thinking.
+Furthermore, the positive symbolic message can compensate for poor performance and create a misalignment between citizens' perceptions and the "real world" [@alonbarkat_2017].
+Hence, by identifying the circumstances under which citizens are more/less likely to be affected by symbols, we would better assess the potential risk for governments' manipulative use of public communications.
 
@@
 I hypothesize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to invest in elaborate processing.
-Similarly, higher perceived personal relevance are expected to enhance citizens' inclincation to scrutinize the substantive content of communication.
-Employing a survey experiment, I test this hypothesis in the context of the Israeli Environment Protection Ministry, and its policy plans for reducing the air pollution in a specific area (the Haifa-Bay) and for reducing domestic waste.
-I operationalize personal relevance both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+Similarly, higher perceived personal relevance are expected to enhance citizens' inclination to scrutinize the substantive content of communication.
+Employing a survey experiment, I test this hypothesis in the context of the Israeli Environment Protection Ministry, and two of its policy plans: reducing the air pollution in a specific area (the Haifa-Bay); and reducing domestic waste.
+I operationalize the perceived personal relevance of these policies both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
 
@@
 
-The social psychology Elaboration Likelihood Model (ELM) provides a comprehensive theoretical framework for investigating peoples' varying responses to "persuasive" 
-<br>
+The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a theoretical framework for investigating the effects of "persuasive" communications on people's attitudes [@petty_1986; @petty_2011].
+Whilst this model has been applied in various contexts, thus far, the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.
 
-# The moderating role of perceived personal relevance on citizens' responses to symbols and information in communications
+ELM postulates that people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
+When people have high motivation and ability to elaborate on the message, they are likely to focus on the arguments in the communication which are central to the merits of the issue, and scrutinize them ("central route").
+Conversely, when they are unmotivated or unable to elaborate, they may rely on available heuristic cues that require relatively little amount of cognitive effort ("peripheral route").[^footnote_dual_process_theories] These two routes for persuasion are regarded as two ends of an "elaboration continuum".
+When people are located between these two edges, as they are much of the time, persuasion will be determined by a mixture of these processes.
 
-How may we apply the theoretical framework of ELM to the study of the effects of symbolic elements in government communications with citizens and their interaction with substantive information?
+In light of the latter conceptualization of ELM, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
+Conversely, symbolic elements can be regarded as potential peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
+Accordingly, the more citizens are motivated to think about the content of the communication, and the more they are capable of doing so, the more they are likely to form their attitudes based on its substantive information.
+Conversely, the less motivated and capable they are to elaborate, the more susceptible they are to symbolic elements in the communication.
 
-In sum, I expect that:
+[^footnote_dual_process_theories]: The conceptual distinction between the "central and peripheral routes for persuasion" largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].
+
+This literature has pointed to a variety of factors that shape people's motivation and ability to think about the message, and accordingly - their placement along the elaboration continuum and inclination to be persuaded either by the arguments or by peripheral cues.
+Among others, scholars have theorized that the more people perceive the issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater.
+That postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
+These studies have demonstrated that manipulating the perceived personal relevance of the communication affects subjects' inclination to elaborate, and accordingly, it increases the effect of arguments in the communication and decreases the effect of peripheral cues.
+Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors]
+
+[^footnote_elm_factors]: For a thorough review of motivational and ability factors affecting likelihood to elaborate see @petty_1998.
+
+Connecting the public administration literature on citizens' responses to government public communications with the above insights from social psychology literature, I theorize that the extent to which citizens perceive the communication as personally relevant moderates the effects of symbolic elements on the one hand and of substantive information on the other hand.
+I hypothesize that:
 
@@
 
-The theoretical hypotheses are graphically displayed in **Figure 1**.
+These theoretical hypotheses are graphically displayed in **Figure 1**.
 
@@
 **Figure 1: Theoretical model**
-
-<br>
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/theoretical_model_relevance.png)
 
@@
 
+I tested the above mentioned hypotheses via a randomized survey experiment, which simulates citizens' responses to government organizations' communications about their policy plans.
+
 <br>
@@
 ##*The empirical case*
+
+Empirically, I focused on the case of the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, both at the national and local levels.
+I examined citizens' responses to communications of EPM regarding two of its current policy plans.
+The first policy regards reducing the air pollution in the Haifa-Bay area.
+This policy issue was selected insofar as it offers a fortunate case for examining the moderating role of perceived personal relevance in a natural and realistic setting.
+The comparison between those who reside in the polluted area and those who don't represents natural variation in the perceived personal relevance of this policy issue.
+At the same time, because this policy issue is intangible, invisible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as it is the case in many other policy issues [@petty_1983].
+Accordingly, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize a communication about the air-pollution in their area of residence, yet are not more capable to do so than those who reside elsewhere.
+As explained below, the sample population of the experiment consists of residents of Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
+The second policy plan regards reducing domestic waste and increasing recycling.
+This policy issue is assumed to be equally relevant for Haifa-bay residents and others.
+Therefore, comparing between these two policies enables me to confirm that differences between the two groups, if found, are explained by differences in the perceived personal relevance of the policy issue.
+For the sake of simplicity, I henceforth refer to these two policy plans as "air-pollution" and "recycling" policies.
+
+EPM also makes a good case for this study due to its significant investment in public communications, and its deployment of various symbolic elements.
+Here, I focused on three symbolic elements which have been used in the EPM's public communications, and became widely recognized by the public.
+The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
+The second symbolic element is the green color, which is strongly associated with taking care of the environment.
+The third element is the images of two high-profile celebrity comedians which were taken from advertising campaigns of the EPM.
+Further details about these symbolic elements are found in the supplementary appendix.
+
+<br>
+
+##*Sample selection and recruitment*
+
+The survey was conducted in late January 2018.
+To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
+I will henceforth refer to these two groups of cities as Haifa-bay and center.
+
+I conducted the survey experiment through Qualtrics Survey Software.
+To select and recruit residents of these specific cities, I was assisted by an Israeli internet research panel company *iPanel*.
+The online survey link was sent by iPanel, between 28.1-1.2.2018.
+A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+These filters are not significantly associated with the areas or the experimental conditions.
+Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
+
+[^footnote_responserate]: According to iPanel's reporting, 5,077 people were invited to fill the survey.
+Of these people, approximately 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample.
+Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
+
+<br>
+
+## *Procedure*
+
+To disguise the purpose of the experiment, the survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general, as opposed to attitudes about EPM or the specific two policies.
+The participants were first asked pre-manipulation questions about their political ideology and their trust in government ministries in general and evaluation of their performance.
+Thereafter, they were asked about their interest in environmental policy issues, the extent to which they follow these issues in the media, their preference for more/less government investment in this field.
+They were also asked to describe the most salient environmental issue in their particular area of residence.[^footnote_relevance_manipulation]
+
+[^footnote_relevance_manipulation]: The latter questions about environmental policy was initially designed as a manipulation of for perceived personal relevance (specifically for Haifa-Bay subjects with regard to the air-pollution policy).
+The questions which are mentioned above were included in the treatment group, whereas subjects in the control group were asked instead equivalent questions about their field of occupation.
+However, manipulation checks suggested that these priming questions did not enhance the perceived personal relevance of these policies for the participants (either from Haifa-Bay or center cities).
+Therefore, I will not regard to this treatment in the paper.
+
+Thereafter, participants were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
+Each policy plan included the title of the policy goal (i.e.
+"reducing the levels of air pollution in the Haifa bay"), followed by short descriptions of two actions to be taken by EPM in order to fulfill this goal (30-50 words each).
+
+The air-pollution and recycling policy plans were presented to each subject in a random order.
+Per each policy, the subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
+logically persuasive policy plan) and weak policy (i.e.
+logically unpersuasive).
+The policy activities which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
+The proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles in the Haifa-Bay area.
+The strong recycling policy regarded increasing the supervision of manufacturers and reducing the use of disposable bags.
+The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures which are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
+Accordingly, the weak policy plans regarded reducing of regulatory burden on the factories/ manufacturers, and raising citizens' awareness of the efforts to improve air quality/reduce waste.
+The full texts of the weak and strong conditions for the two policy plans is displayed in Appendix A.
+For each subject, one of the two policies was strong and the other was weak, which enables me to compare both between- and within-subjects.
+For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
+
+The participants are also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment, control no-symbols and control fake-symbols.
+In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement".
+Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy, given the relevance of the campaign to the policy plan; Friedman's image from the campaign of "starting to think green", which was more general and regarded to a variety of environmental issues, was attached to the air-pollution policy.
+In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
+Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
+The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
+Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.
+In that sense, it can be regarded as a placebo.
+In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM (supplementary appendix ##TBA##).
+The symbols conditions are displayed in the Appendix B.
+
+Each policy plan was followed by questions about respondents' trust in the policy.
+Afterwards, the subjects were asked about their perceived level of elaboration on the last policy that was presented to them, conducted a memory test.
+They were also asked about the extent to which they perceive the two policies as personally relevant to themselves.
+Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence.
+After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities.
+Finally, the participants are debriefed about the manipulations, and the possible deception.
+An English translation of the full survey
+is available from the supplementary appendix.
+
+Altogether, for each policy plan, the survey experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs.
+weak policy).
+The experimental groups are fairly balanced with respect to demographics, pre-manipulation variables and the two areas.
+The assignment to the different experimental groups is graphically presented in Figure 3.
 

### 2018-07-02 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 output:
+  word_document: default
+  pdf_document:
+    toc: yes
   html_document:
@@
       toc_depth: 3
-  pdf_document:
-    toc: yes
-  word_document: default
 link-citations: yes
@@
 
-I tested the above mentioned hypotheses via a randomized survey experiment, which simulates citizens' responses to government organizations' communications about their policy plans.
-
-<br>
-
-##*The empirical case*
-
-Empirically, I focused on the case of the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, both at the national and local levels.
+I tested the above mentioned hypotheses via a randomized survey experiment, focusing on the case of the Israeli Environment Protection Ministry (hereafter: EPM).
 I examined citizens' responses to communications of EPM regarding two of its current policy plans.
-The first policy regards reducing the air pollution in the Haifa-Bay area.
-This policy issue was selected insofar as it offers a fortunate case for examining the moderating role of perceived personal relevance in a natural and realistic setting.
-The comparison between those who reside in the polluted area and those who don't represents natural variation in the perceived personal relevance of this policy issue.
-At the same time, because this policy issue is intangible, invisible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as it is the case in many other policy issues [@petty_1983].
-Accordingly, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize a communication about the air-pollution in their area of residence, yet are not more capable to do so than those who reside elsewhere.
-As explained below, the sample population of the experiment consists of residents of Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
-The second policy plan regards reducing domestic waste and increasing recycling.
-This policy issue is assumed to be equally relevant for Haifa-bay residents and others.
-Therefore, comparing between these two policies enables me to confirm that differences between the two groups, if found, are explained by differences in the perceived personal relevance of the policy issue.
+The first policy regards *reducing the air pollution in the Haifa-Bay area*, located in the north of Israel.
+This policy issue offers a fortunate case for examining the moderating role of perceived personal relevance.
+The differences between those who reside in the polluted area and those who do not represent natural variation in this factor.
+Moreover, because this policy issue is intangible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as it is the case in many other policy issues [@petty_1983].
+Congruently, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize a communication about the air-pollution in their area of residence, yet are not more capable to do so than those who reside elsewhere.
+As explained below, the sample population of the study consists of residents of Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
+The second policy plan regards *reducing domestic waste and increasing recycling*.
+This topic is assumed to be equally relevant for Haifa-bay residents and others.
+Therefore, adding this policy plan enables to further confirm that their different responses to the air-pollution policy, if found, are explained by differences in perceived personal relevance.
 For the sake of simplicity, I henceforth refer to these two policy plans as "air-pollution" and "recycling" policies.
@@
 The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
-The second symbolic element is the green color, which is strongly associated with taking care of the environment.
+The second element is the green color, which is strongly associated with taking care of the environment.
 The third element is the images of two high-profile celebrity comedians which were taken from advertising campaigns of the EPM.
@@
 
-<br>
-
-##*Sample selection and recruitment*
-
-The survey was conducted in late January 2018.
+The survey was conducted online through Qualtrics Survey Software.
 To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
 I will henceforth refer to these two groups of cities as Haifa-bay and center.
-
-I conducted the survey experiment through Qualtrics Survey Software.
 To select and recruit residents of these specific cities, I was assisted by an Israeli internet research panel company *iPanel*.
@@
 The participants were first asked pre-manipulation questions about their political ideology and their trust in government ministries in general and evaluation of their performance.
-Thereafter, they were asked about their interest in environmental policy issues, the extent to which they follow these issues in the media, their preference for more/less government investment in this field.
-They were also asked to describe the most salient environmental issue in their particular area of residence.[^footnote_relevance_manipulation]
-
-[^footnote_relevance_manipulation]: The latter questions about environmental policy was initially designed as a manipulation of for perceived personal relevance (specifically for Haifa-Bay subjects with regard to the air-pollution policy).
-The questions which are mentioned above were included in the treatment group, whereas subjects in the control group were asked instead equivalent questions about their field of occupation.
-However, manipulation checks suggested that these priming questions did not enhance the perceived personal relevance of these policies for the participants (either from Haifa-Bay or center cities).
-Therefore, I will not regard to this treatment in the paper.
+Thereafter, they are assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance).
+Subjects in the relevance treatment group are asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
+In addition to these three likert-scale questions, they are also asked to describe the most salient environmental issue in their particular area of residence.
+These treatment items were designed to prime subjects to think about environmental issue and their relevance to their own lives.
+In addition, the latter open-ended question was designed specifically to prime Haifa-bay residents to think about the issue of the air pollution and its personal relevance.
+Subjects in the relevance control group are asked equivalent questions about their field of occupation.
 
@@
 "reducing the levels of air pollution in the Haifa bay"), followed by short descriptions of two actions to be taken by EPM in order to fulfill this goal (30-50 words each).
+Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
+logically persuasive policy plan) or weak policy (i.e.
+logically unpersuasive).
+Each subject, moreover, was exposed to one strong and one weak policy communication.
+For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
+The actions which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
+The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures that are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
+For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were decreasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality.
+The full texts of the weak and strong conditions for the two policy plans is displayed in the supplementary appendix.
 
-The air-pollution and recycling policy plans were presented to each subject in a random order.
-Per each policy, the subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
-logically persuasive policy plan) and weak policy (i.e.
-logically unpersuasive).
-The policy activities which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
-The proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles in the Haifa-Bay area.
-The strong recycling policy regarded increasing the supervision of manufacturers and reducing the use of disposable bags.
-The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures which are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
-Accordingly, the weak policy plans regarded reducing of regulatory burden on the factories/ manufacturers, and raising citizens' awareness of the efforts to improve air quality/reduce waste.
-The full texts of the weak and strong conditions for the two policy plans is displayed in Appendix A.
-For each subject, one of the two policies was strong and the other was weak, which enables me to compare both between- and within-subjects.
-For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
+In addition to information manipulation, the participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
+In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements.
+In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
+In the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
+The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.[^footnote_symbols_manipulation_checks] The symbols conditions are displayed in **Appendix B**.
+Further details about the images in the real and fake symbols conditions are found in the supplementary appendix.
+That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e.
+one strong and one weak), enables me later to analyze the interaction between the areas and the information conditions both via between- and within-subjects.
 
-The participants are also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment, control no-symbols and control fake-symbols.
-In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement".
-Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy, given the relevance of the campaign to the policy plan; Friedman's image from the campaign of "starting to think green", which was more general and regarded to a variety of environmental issues, was attached to the air-pollution policy.
-In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
-Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
-The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
-Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.
-In that sense, it can be regarded as a placebo.
-In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM (supplementary appendix ##TBA##).
-The symbols conditions are displayed in the Appendix B.
+[^footnote_symbols_manipulation_checks]: In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
+The results of these examinations are reported in the supplementary appendix.
 
-Each policy plan was followed by questions about respondents' trust in the policy.
-Afterwards, the subjects were asked about their perceived level of elaboration on the last policy that was presented to them, conducted a memory test.
-They were also asked about the extent to which they perceive the two policies as personally relevant to themselves.
+Each policy plan was followed by six questions questions about respondents' trust in the policy.
+Afterwards, the subjects conducted a memory test on the last policy that was presented to them, and were asked about the extent to which they elaborated on it and about the personal relevance of the policy plans.
 Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence.
 After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities.
-Finally, the participants are debriefed about the manipulations, and the possible deception.
-An English translation of the full survey
-is available from the supplementary appendix.
+Finally, the participants were debriefed about the manipulations, and the possible deception.
+An English translation of the full survey is available from the supplementary appendix.
 
 Altogether, for each policy plan, the survey experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs.
-weak policy).
-The experimental groups are fairly balanced with respect to demographics, pre-manipulation variables and the two areas.
-The assignment to the different experimental groups is graphically presented in Figure 3.
+weak policy) x 2 (relevance: treatment vs.
+control).[^footnote_information_symbols_paper]  The assignment to the different experimental groups, across the two areas, is graphically presented in **Figure 2**.
+The experimental groups are fairly balanced with respect to the two areas, as well as to demographics, and pre-manipulation variables.
+
+[^footnote_information_symbols_paper]: In addition to the above-mentioned hypotheses, the experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and information, and its moderation by the effect of symbols on elaboration.
+In this paper, however, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
+The methodological aspects which are relevant for examining the additional hypotheses are described in a separate paper.
+
+<br>
+**Figure 2: Experimental design for policy plan communications**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow_relevance.png)
 
@@
 
-##*Data collection*
+##*Variables*
 
-<br>
+```{r, echo=FALSE, warning=FALSE, message=F}
+alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
+                               TRUST_air_q2,
+                               TRUST_air_q3,
+                               TRUST_air_q4,
+                               TRUST_air_q5,
+                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)
 
-## *Procedure*
+alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
+                               TRUST_waste_q2,
+                               TRUST_waste_q3,
+                               TRUST_waste_q4,
+                               TRUST_waste_q5,
+                               TRUST_waste_q6))[["total"]][["raw_alpha"]]%>%round(2)
 
-<br>
-**Figure 3: Experimental design for policy plan communications**
-<br>
+alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2)%>%round(2)
 
-##*Variables*
+cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate%>%mean()%>%round(2)
+
+cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate%>%mean()%>%round(2)
+
+cor_RT_delta = cor.test(SVIVA2_01$ELABORATION_total_time_log,
+                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
+
+cor_memory_delta = cor.test(SVIVA2_01$MEMORY_total,
+                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
+
+t_air_information = t.test(TRUST_air_INDEX~INFORMATION_air,SVIVA2_01)
+t_waste_information = t.test(TRUST_waste_INDEX~INFORMATION_waste,SVIVA2_01)
+
+```
+
+My outcome variable is citizens' trust in policy.
+This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
+Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
+
+My key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.
+I  operationalize the latter variable both experimentally (through the abovementioned priming questions) and observationally (through the distinction between the Haifa-Bay and center).
+I coded living in Haifa-bay area according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
 
@@
 
-##Appendix A: Information manipulation
-
-**Air-pollution policy** (Reducing the air-pollution in the Haifa-Bay)
-
-EPM is working to reduce the air-pollution in the Haifa-Bay through:
-
-*Strong*
-
-* **Increasing the supervision of the factories in Haifa-Bay**.
-In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways.
-The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the amount of fines for pollutants.
-
-* **Reduction of smoke emissions from vehicles in Haifa Bay**.
-The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area.
-The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and promotes the operation of a "clean-air area" that restricts the entry of polluting vehicles.
-
-*Weak*
-
-* **Decreasing the supervision of the factories in Haifa-Bay**.
-The Ministry is preparing for a change in the method of supervision of the factories.
-The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the amount of fines.
-The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.
-
-* **Raising citizens' awareness of the efforts to improve air quality**.
-In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful.
-The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents.
-To this end, the ministry has increased its investment in public relations and publicity in this subject.
-
-<br>
-
-**Recycling policy** (Reducing waste and increasing recycling)
-
-EPM is working to reduce the amount of waste and increase its recycling through:
-
-*Strong*
-
-* **Packaging recycling - Increased supervision of manufacturers**.
-In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, which imposes on manufacturers and importers the responsibility for recycling the packaging.
-The Ministry will work to increase enforcement by virtue of this act, and will enforce it with regard to additional manufacturers and importers.
-
-* **Reducing the usage of disposable bags**.
-In order to reduce the use of disposable plastic bags, the Ministry enforces the Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the chains.
-The Ministry works to implement the act, and encourages the transition to reusable grocery bags.
-
-*Weak*
-
-* **Packaging recycling - Decreased supervision of manufacturers**.
-The Ministry is preparing to a change in the method of supervision of the manufacturers, who are responsible for the recycling of product packaging by virtue of the act The ministry will reduce the number of inspections, rely on manufacturers' self-reports regarding their compliance with the requirements of the act, and reduce the amount of fines.
-The change is coordinated with members of the industry, which are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.
-
-* **Reducing the usage of disposable bags**.
-In recent years, the Ministry has taken steps to encourage the reduction of waste, which have been partially successful.
-The Ministry works to raise awareness of the actions taken and to highlight their success in order to improve its image among the public.
-To this end, the ministry has increased its investment in public relations and publicity in this subject.
-
-<br>
-
-##Appendix B: Symbols manipulation
+##Appendix A: Symbols manipulation
 ![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/symbols_manipulation.png)

### 2018-07-02 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 output:
-  word_document: default
-  pdf_document:
-    toc: yes
   html_document:
@@
       toc_depth: 3
+  pdf_document:
+    toc: yes
+  word_document: default
 link-citations: yes
@@
 When people have high motivation and ability to elaborate on the message, they are likely to focus on the arguments in the communication which are central to the merits of the issue, and scrutinize them ("central route").
-Conversely, when they are unmotivated or unable to elaborate, they may rely on available heuristic cues that require relatively little amount of cognitive effort ("peripheral route").[^footnote_dual_process_theories] These two routes for persuasion are regarded as two ends of an "elaboration continuum".
+Conversely, when they are unmotivated or unable to elaborate, they may rely on available heuristic cues that require relatively little amount of cognitive effort ("peripheral route").
+These two routes for persuasion are regarded as two ends of an "elaboration continuum".
 When people are located between these two edges, as they are much of the time, persuasion will be determined by a mixture of these processes.
@@
 Conversely, the less motivated and capable they are to elaborate, the more susceptible they are to symbolic elements in the communication.
-
-[^footnote_dual_process_theories]: The conceptual distinction between the "central and peripheral routes for persuasion" largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].
 
@@
 
+<br>
+
+## *Data collection*
+
 The survey was conducted online through Qualtrics Survey Software.
@@
 The online survey link was sent by iPanel, between 28.1-1.2.2018.
-A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
+Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
 These filters are not significantly associated with the areas or the experimental conditions.
 Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
-
-[^footnote_responserate]: According to iPanel's reporting, 5,077 people were invited to fill the survey.
-Of these people, approximately 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample.
-Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
 
@@
 
-To disguise the purpose of the experiment, the survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general, as opposed to attitudes about EPM or the specific two policies.
-The participants were first asked pre-manipulation questions about their political ideology and their trust in government ministries in general and evaluation of their performance.
-Thereafter, they are assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance).
-Subjects in the relevance treatment group are asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
-In addition to these three likert-scale questions, they are also asked to describe the most salient environmental issue in their particular area of residence.
-These treatment items were designed to prime subjects to think about environmental issue and their relevance to their own lives.
-In addition, the latter open-ended question was designed specifically to prime Haifa-bay residents to think about the issue of the air pollution and its personal relevance.
-Subjects in the relevance control group are asked equivalent questions about their field of occupation.
+The survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general.
+After a set of pre-manipulation questions, they subjects were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance).
+Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
+In addition to these three likert-scale questions, they were also asked to describe the most salient environmental issue in their particular area of residence.
+These questions were designed to prime subjects to think about the impact of environmental issues to their own lives.
+They were also designed to prime Haifa-bay residents to think about the personal relevance of the air pollution in their area.
+Subjects in the relevance control group were asked equivalent questions about their field of occupation.
 
-Thereafter, participants were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
-Each policy plan included the title of the policy goal (i.e.
-"reducing the levels of air pollution in the Haifa bay"), followed by short descriptions of two actions to be taken by EPM in order to fulfill this goal (30-50 words each).
+After the relevance manipulation, participants were presented with the two policy plans of EPM, which they were told that were obtained from EPM's annual work plan.
+Each policy plan was followed by questions about respondents' trust in them.
 Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
@@
 logically unpersuasive).
-Each subject, moreover, was exposed to one strong and one weak policy communication.
-For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
-The actions which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
-The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures that are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
-For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were decreasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality.
+The information in the strong policy plans condition was taken from the real work plan and from other official sources, whereas the information in the weak policy plans was fictional, and was deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.
 The full texts of the weak and strong conditions for the two policy plans is displayed in the supplementary appendix.
+Each subject, moreover, was exposed to one strong and one weak policy communication, diaplayed in a random order.
 
-In addition to information manipulation, the participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
-In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements.
+The participants were also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
+In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the EPM logo, green color and celebrity images from campaigns.
 In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
-In the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
-The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.[^footnote_symbols_manipulation_checks] The symbols conditions are displayed in **Appendix B**.
-Further details about the images in the real and fake symbols conditions are found in the supplementary appendix.
-That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e.
-one strong and one weak), enables me later to analyze the interaction between the areas and the information conditions both via between- and within-subjects.
+In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with images of unfamiliar people.
+The symbols conditions are displayed in **Appendix A**.
+Further details about the real and fake symbols are found in the supplementary appendix.
 
-[^footnote_symbols_manipulation_checks]: In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
-The results of these examinations are reported in the supplementary appendix.
-
-Each policy plan was followed by six questions questions about respondents' trust in the policy.
-Afterwards, the subjects conducted a memory test on the last policy that was presented to them, and were asked about the extent to which they elaborated on it and about the personal relevance of the policy plans.
-Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence.
-After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities.
-Finally, the participants were debriefed about the manipulations, and the possible deception.
-An English translation of the full survey is available from the supplementary appendix.
-
-Altogether, for each policy plan, the survey experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs.
+Altogether, per each policy plan, the experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs.
 weak policy) x 2 (relevance: treatment vs.
@@
 
-cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate%>%mean()%>%round(2)
-
-cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate%>%mean()%>%round(2)
-
-cor_RT_delta = cor.test(SVIVA2_01$ELABORATION_total_time_log,
-                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
-
-cor_memory_delta = cor.test(SVIVA2_01$MEMORY_total,
-                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
-
-t_air_information = t.test(TRUST_air_INDEX~INFORMATION_air,SVIVA2_01)
-t_waste_information = t.test(TRUST_waste_INDEX~INFORMATION_waste,SVIVA2_01)
-
 ```
@@
 My outcome variable is citizens' trust in policy.
-This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
-Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
+This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
+Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
 
 My key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.
-I  operationalize the latter variable both experimentally (through the abovementioned priming questions) and observationally (through the distinction between the Haifa-Bay and center).
+Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
+Manipulation checks for the information confirm that the weak policy plans were perceived as less effective in achieving the policy goal compared with the strong plans.
+As for the communication's perceived personal relevance, I operationalize this variable both observationally (through the distinction between the Haifa-Bay and center samples) and experimentally (through the abovementioned priming questions).
 I coded living in Haifa-bay area according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
+The survey data supports the assumption that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
+Indeed, when asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects regarded to the air-pollution.
+As for the relevance priming questions, however, manipulation checks suggest that those in the relevance treatment group did not perceive either of the two policies as more personally relevant.
+The limitation of this manipulation should be kept in mind in the following sections.
+The results of the manipulation checks and validation analyses reported here are avilable from the supplementary appendix.
 

### 2018-07-03 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 
-My outcome variable is citizens' trust in policy.
-This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
+My outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively).
+This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
@@
 Manipulation checks for the information confirm that the weak policy plans were perceived as less effective in achieving the policy goal compared with the strong plans.
-As for the communication's perceived personal relevance, I operationalize this variable both observationally (through the distinction between the Haifa-Bay and center samples) and experimentally (through the abovementioned priming questions).
+The perceived personal relevance of the communication is operationalized observationally (through the distinction between the Haifa-Bay and center samples) as well as experimentally (through the abovementioned priming questions).
 I coded living in Haifa-bay area according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
-The survey data supports the assumption that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
-Indeed, when asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects regarded to the air-pollution.
+Validity checks confirm that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
+Moreover, when directly asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects regarded to the air-pollution.
 As for the relevance priming questions, however, manipulation checks suggest that those in the relevance treatment group did not perceive either of the two policies as more personally relevant.
-The limitation of this manipulation should be kept in mind in the following sections.
-The results of the manipulation checks and validation analyses reported here are avilable from the supplementary appendix.
+This limitation should be kept in mind in the following analyses of the effect of this manipulation.
+The results of the all manipulation and validation checks  reported here are avilable from the supplementary appendix.
+
+In addition to the above independent variables, the survey also included control items. Summary statistics and correlation matrix for all variables are available in the supplementary appendix.
 
@@
 # Results
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
+mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+
+mod_waste_1.1 = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
+mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+
+mod_air_1.1_r1 = lm(TRUST_air_INDEX~SYMBOL_t.r+INFORMATION_weak,data=SVIVA2_01_comb)
+
+```
+
+**Table 1** presents the results of OLS regression analyses for the effects of the symbols and information manipulations on trust in the two policies, and their interaction with the areas.
+Models 1.1-1.3 regards the Air-pollution policy, and Models 1.4 - 1.6 regards the recycling policy.
+For each of these policy plans, I first regress trust on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).
+The real symbols had a positive main effect on both policies compared with the no symbols condition.
+Compared with the fake symbols, the increase is significant at the 90% (one-tailed) regarding the air-pollution policy, yet it is insignificant compared with the recycling policy.
+The information manipulation has a significant main effect in both policy plans.
+As shown by the coefficients of the Area in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in the air-pollution policy, and also, to a lower degree, in the recycling policy.
+This may suggest that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, but less so towards EPM or environmental policy in general.
+
+I now turn to analyze the interactions between the manipulations and the areas.
+With regard to the air-pollution policy, my first hypotheses entails a positive interaction between residence in the center (i.e.
+low personal relevance) and the real symbols.
+My second hypothesis entails a positive interaction between center residents and weak information.
+Yet, counter to these expectations, in Model 1.3, the interaction between residence in the center and the real symbols is negative, and the interaction with the weak information is insignificant.
+These findings suggest that the real symbols were more effective on those reside in the polluted area and that the latter were not more likely to scrutinize the content of the policy plan.
+Similar patterns were also found with regard to the recycling policy.
+In Model 1.6, the interaction between the areas and the information is insignificant, and the effect of the real symbols is similarly greater among the Haifa-Bay subjects.
+**Figure 3** provides a descriptive demonstration of the effects of the the interaction between the areas and the symbols manipualation, to facilitate their interpretations.
+
+**Table 1: Regression analyses – observational measure for perceived personal relevance.**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+stargazer(mod_air_1.1,mod_air_1.2,mod_air_1.3,
+          mod_waste_1.1,mod_waste_1.2,mod_waste_1.3,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information"),
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
+
+**Figure 3: The effect of symbolic elements on trust across areas**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
+SVIVA2_01_comb = SVIVA2_01_comb %>% 
+  mutate(POLICY_n = Recode(policy,"'TRUST_air_INDEX'='Air-pollution'; 'TRUST_waste_INDEX'='Recycling'"))
+
+ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
+  theme_classic()+
+  #geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.65),
+               width=0.2,size=0.5,position=position_dodge(0.2),color="gray70") + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.2))+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.2),alpha=0.8)+
+  scale_shape_manual(guide=F,values=c(19,1))+
+  scale_linetype_manual(name="Area",values=c(1,4))+
+  facet_grid(~POLICY_n)+
+  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
+  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
+
+```
+
+<font size="0.5">
+
+*Note*: Error bars represent 90% confidence intervals.
+
+</font>
+
+Thereafter, I will add the interaction with the relevance manipulation. In all these analyses I use linear OLS regressions.
+
+**Table 2: Regression analyses – experimental manipulation of perceived personal relevance.**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_air_2.1 = lm(TRUST_air_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_air_2.2 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
+mod_air_2.3 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
+mod_air_2.4 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
+
+mod_waste_2.1 = lm(TRUST_waste_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_waste_2.2 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
+mod_waste_2.3 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
+mod_waste_2.4 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
+
+stargazer(mod_air_2.1,mod_air_2.2,mod_air_2.4,
+          mod_waste_2.1,mod_waste_2.2,mod_waste_2.4,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Relevance treatment",
+                             "Relevance treatment x Real symbols",
+                             "Relevance treatment x Fake symbols",
+                             "Relevance treatment x Weak Information",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information",
+                             "Relevance treatment x Area",
+                             "Relevance treatment x Area x Real symbols",
+                             "Relevance treatment x Area x Fake symbols",
+                             "Relevance treatment x Area x Weak Information"),
+          omit.stat = c("rsq","ser", "f"),
+          order = c(1,2,4,3,6:8,5,9,10,12,11,13:15),
+          initial.zero = FALSE,
+          notes = "",
+          notes.append = FALSE)
+
+```
 

### 2018-07-04 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 
-# Methodology
+# Research design
 
@@
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
+Participants were more likely to report low levels of trust in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
 
@@
 Manipulation checks for the information confirm that the weak policy plans were perceived as less effective in achieving the policy goal compared with the strong plans.
-The perceived personal relevance of the communication is operationalized observationally (through the distinction between the Haifa-Bay and center samples) as well as experimentally (through the abovementioned priming questions).
+The perceived personal relevance of the communication is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
 I coded living in Haifa-bay area according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
@@
 As for the relevance priming questions, however, manipulation checks suggest that those in the relevance treatment group did not perceive either of the two policies as more personally relevant.
-This limitation should be kept in mind in the following analyses of the effect of this manipulation.
-The results of the all manipulation and validation checks  reported here are avilable from the supplementary appendix.
-
-In addition to the above independent variables, the survey also included control items. Summary statistics and correlation matrix for all variables are available in the supplementary appendix.
+This limitation should be kept in mind when interpreting the results regarding this manipulation.
+The results of the all manipulation and validation checks are avilable from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
 
@@
 mod_air_1.1_r1 = lm(TRUST_air_INDEX~SYMBOL_t.r+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_waste_1.1_r1 = lm(TRUST_waste_INDEX~SYMBOL_t.r+INFORMATION_weak,data=SVIVA2_01_comb)
 
@@
 
-**Table 1** presents the results of OLS regression analyses for the effects of the symbols and information manipulations on trust in the two policies, and their interaction with the areas.
-Models 1.1-1.3 regards the Air-pollution policy, and Models 1.4 - 1.6 regards the recycling policy.
-For each of these policy plans, I first regress trust on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).
-The real symbols had a positive main effect on both policies compared with the no symbols condition.
-Compared with the fake symbols, the increase is significant at the 90% (one-tailed) regarding the air-pollution policy, yet it is insignificant compared with the recycling policy.
-The information manipulation has a significant main effect in both policy plans.
-As shown by the coefficients of the Area in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in the air-pollution policy, and also, to a lower degree, in the recycling policy.
-This may suggest that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, but less so towards EPM or environmental policy in general.
+**Table 1** presents the results of OLS regression analyses for the effects of the symbols and information manipulations on trust in the two policy plans, and their interaction with the two areas.
+Models 1.1-1.3 regard the Air-pollution policy, and Models 1.4 - 1.6 regard the recycling policy.
+I regress trust in policy on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).
+The real symbols had positive main effects on both policies compared with the no symbols condition.
+Compared with the fake symbols, the increase is significant at the 90% (one-tailed) regarding the air-pollution policy, and only marginally significant compared with the recycling policy (*p* = `r (summary(mod_waste_1.1_r1)$coefficients["SYMBOL_t.r1",4]/2)%>%round(2)`, one-tailed).
+The information manipulation also has a significant main effect in both policy plans, as expected.
+Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in the air-pollution policy, and also, to a lower degree, in the recycling policy.
+The latter suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, and to some extent towards EPM or environmental policy in general.
 
-I now turn to analyze the interactions between the manipulations and the areas.
+Keeping in mind these main effects, I now turn to analyze the interactions between the manipulations and the areas.
 With regard to the air-pollution policy, my first hypotheses entails a positive interaction between residence in the center (i.e.
 low personal relevance) and the real symbols.
-My second hypothesis entails a positive interaction between center residents and weak information.
-Yet, counter to these expectations, in Model 1.3, the interaction between residence in the center and the real symbols is negative, and the interaction with the weak information is insignificant.
-These findings suggest that the real symbols were more effective on those reside in the polluted area and that the latter were not more likely to scrutinize the content of the policy plan.
-Similar patterns were also found with regard to the recycling policy.
-In Model 1.6, the interaction between the areas and the information is insignificant, and the effect of the real symbols is similarly greater among the Haifa-Bay subjects.
-**Figure 3** provides a descriptive demonstration of the effects of the the interaction between the areas and the symbols manipualation, to facilitate their interpretations.
+Based on my second hypothesis, I expect to find a positive interaction between center residents and weak information.
+Counter to these expectations, in Model 1.3, the interaction between residence in the center and the real symbols is negative (*p*<.1), and the interaction with the weak information is insignificant.
+These findings suggest that the real symbols were more effective in increasing the trust of those reside in the polluted area and that the latter were not more likely to scrutinize the content of the communication.
+I also found similar patterns regarding the recycling policy.
+In Model 1.6, the interaction between the areas and the information is insignificant, and the interaction with the real symbols is negative.
+**Figure 3** provides a descriptive demonstration of the interaction between the areas and the symbols manipualation for the two policies.
 
@@
 
-Thereafter, I will add the interaction with the relevance manipulation. In all these analyses I use linear OLS regressions.
+Next, I examine whether those subjects who were primed to think about the personal relevance of these policy plans were more likely to scrutinize them, and less likely to be affected by the familiar symbols.
+The interaction between the relevance manipulation and the symbols and information manipulations is presented in **Table 2**.
+Again, the first three models regard the Air-pollution policy, and the remaining models regard the recycling policy.
+Models 2.1, 2.4 replicate models 1.1, 1.4 while adding the relevance manipulation.
+Thereafter, I add the interactions between the relevance manipulation and the symbols and information manipulations (Models 2.2, 2.5).
+Finally, to test the moderation of the relevance manipulation within each area, I add three-way interactions with the areas (Models 2.3, 2.6).
+In all these models, the relevance treatment did not yield significant effects, and there are no significant interactions with the symbols and information manipulations.
+The triple interactions with the areas are also insignificant (in Models 2.3, 2.6), which indicates that in neither of these areas did the relevance treatment moderate the effects of the symbols and information manipulations.
 
@@
 
+I further explored the robustness of these findings additional analyses, reported in the supplementary appendix.
+First, in addition to the above operationalizations of personal relevance, I also relied on subjects' subjective reporting.
+Second, I further explored the effect of personal relevance on subjects inclincation to scrutinize the policy plans, using additional measures for message elaboration available in the survey: the time participants spent on scanning the policy plans and their score in a memory test.
+I also tested wheather personal relevance decreased the delta (within-subjects) between trust in strong and weak policy plans presented to each subject.
+Third, I added a set of individual-level controls, and factors related to personal relevance of air-pollution, and to personal interest in environmental issues.
+Finally, I replicated my analyses on the unfilterred sample.
+None of these multiple robust analyses supports my theoretical hypotheses.
+
+<br>
+
 #Discussion and conclusion
 
-<br>
+Public administration studies have demonstrated the positive effect of symbolic elements in governemnt public communications on citizens trust in government organizations and their actions.
 

### 2018-07-05 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 
-I tested the above mentioned hypotheses via a randomized survey experiment, focusing on the case of the Israeli Environment Protection Ministry (hereafter: EPM).
-I examined citizens' responses to communications of EPM regarding two of its current policy plans.
+I tested the above mentioned hypotheses via a randomized survey experiment, building on the methodology of @petty_1983.
+The study focuses on the case of the Israeli Environment Protection Ministry (hereafter: EPM), and examines citizens' responses to communications of EPM regarding two of its current policy plans.
 The first policy regards *reducing the air pollution in the Haifa-Bay area*, located in the north of Israel.
@@
 The full texts of the weak and strong conditions for the two policy plans is displayed in the supplementary appendix.
-Each subject, moreover, was exposed to one strong and one weak policy communication, diaplayed in a random order.
+Each subject, moreover, was exposed to one strong and one weak policy communication, displayed in a random order.
 
@@
 This limitation should be kept in mind when interpreting the results regarding this manipulation.
-The results of the all manipulation and validation checks are avilable from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
+The results of the all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
 
@@
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+sd_trust_air = SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max()
+sd_trust_waste = SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max()
+
 mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
@@
 I regress trust in policy on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).
-The real symbols had positive main effects on both policies compared with the no symbols condition.
+The real symbols had positive main effects on both policies compared with the no symbols condition (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations for the air-pollution and recycling policies, respectively).
 Compared with the fake symbols, the increase is significant at the 90% (one-tailed) regarding the air-pollution policy, and only marginally significant compared with the recycling policy (*p* = `r (summary(mod_waste_1.1_r1)$coefficients["SYMBOL_t.r1",4]/2)%>%round(2)`, one-tailed).
-The information manipulation also has a significant main effect in both policy plans, as expected.
+The information manipulation also has a significant main effect in both policy plans, as expected (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations, respectively).
 Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in the air-pollution policy, and also, to a lower degree, in the recycling policy.
-The latter suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, and to some extent towards EPM or environmental policy in general.
+The latter effects suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, and to some extent towards EPM or environmental policy in general.
 
@@
 In Model 1.6, the interaction between the areas and the information is insignificant, and the interaction with the real symbols is negative.
-**Figure 3** provides a descriptive demonstration of the interaction between the areas and the symbols manipualation for the two policies.
+**Figure 3** provides a descriptive demonstration of the interaction between the areas and the symbols manipulation for the two policies.
 
@@
 First, in addition to the above operationalizations of personal relevance, I also relied on subjects' subjective reporting.
-Second, I further explored the effect of personal relevance on subjects inclincation to scrutinize the policy plans, using additional measures for message elaboration available in the survey: the time participants spent on scanning the policy plans and their score in a memory test.
-I also tested wheather personal relevance decreased the delta (within-subjects) between trust in strong and weak policy plans presented to each subject.
+Second, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey: the time participants spent on scanning the policy plans and their score in a memory test.
+I also tested whether personal relevance decreased the delta (within-subjects) between trust in strong and weak policy plans presented to each subject.
 Third, I added a set of individual-level controls, and factors related to personal relevance of air-pollution, and to personal interest in environmental issues.
-Finally, I replicated my analyses on the unfilterred sample.
+Finally, I replicated my analyses on the unfiltered sample.
 None of these multiple robust analyses supports my theoretical hypotheses.
@@
 
-Public administration studies have demonstrated the positive effect of symbolic elements in governemnt public communications on citizens trust in government organizations and their actions.
+Extant Public-Administration research has demonstrated that government communication can affect citizens' trust not only by conveying substantive information, but also by using familiar symbolic elements.
+This study contributes to this literature by exploring the postulation, derived from social psychology, that people are less susceptible to symbols and more likely to scrutinize the substantive information in the communication the more they perceive it as personally relevant.
+I put this theory to rigorous empirical test in the context of government communications, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
+I further focused on its policy plan regarding air pollution in a specific area, to capture natural variation in citizens' perceptions of the personal relevance.
+In addition to utilizing these natural differences, I also used manipulated the personal relevance of the policy plans.
+
+Whilst the effect of perceived personal relevance on message processing has been substantiated by experiment-based studies in social psychology and marketing, I did not find support for this hypothesis the context of citizens' responses to government communications in this study.
+Subjects residing in the polluted Haifa-Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center.
+However, despite these differences, Haifa-bay subjects did not pay more attention to the logical quality of the policy plan, and they were affected by the symbols in the communication not less than those from the center.
+If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
+Similarly, priming subjects to think about the personal relevance of environmetal policy, and of the consequences of air-pollution in particular, did not moderate the effects of the symbols and information in the communications.
+Even those ,  The comparison between those who were assigned to the treatment
+
+How can we reconcile these unexpected findings with the proposed theory?
+Given that the moderating role of personal relevance on peripheral cues was substantiated by numerous studies in social psychology, I would not argue that we should abandon this postulation based on this one study.
+One plausible explanation is that although Haifa-bay residents perceived the air-pollution policy as more relevant, their motivation to elaborate was not high enough to cause them to avoid peripheral cues.
+Certainly, the air-pollution in their area concerns them a great deal, as they point out themselves.
+However this issue represents a *continuous* concern that they may have got used to over the time, as opposed a new issue that emerged recently.
+If this explanation holds, this entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by very high levels of personal relevance.
+These latter findings are also consistent with the findings of @alonbarkat_2017.
+In that study, the scholars assessed citizens' trust in the government electricity company, and its shaping by its familiar symbol, given citizens' recent personal experience of prolonged blackouts.
+Whilst their study was not purposely designed to test the interaction between symbols and personal relevance, one can assume that those who personally experienced blackouts perceived electricity service as more personally relevant.
+Still, they found that citizens who experienced blackouts were influenced by the symbol, as much as those who did not.
 

### 2018-07-05 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 
-I further explored the robustness of these findings additional analyses, reported in the supplementary appendix.
+<br>
+
+I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
 First, in addition to the above operationalizations of personal relevance, I also relied on subjects' subjective reporting.
@@
 In addition to utilizing these natural differences, I also used manipulated the personal relevance of the policy plans.
+To the best of my knowledge, this is the first study to assess the  moderating role of perceived personal relevance on message elaboration and the effect of symbol in the administrative context.
 
@@
 If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
-Similarly, priming subjects to think about the personal relevance of environmetal policy, and of the consequences of air-pollution in particular, did not moderate the effects of the symbols and information in the communications.
-Even those ,  The comparison between those who were assigned to the treatment
+Priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also did not moderate the effects of the symbols and information in the communications.
 
-How can we reconcile these unexpected findings with the proposed theory?
-Given that the moderating role of personal relevance on peripheral cues was substantiated by numerous studies in social psychology, I would not argue that we should abandon this postulation based on this one study.
-One plausible explanation is that although Haifa-bay residents perceived the air-pollution policy as more relevant, their motivation to elaborate was not high enough to cause them to avoid peripheral cues.
-Certainly, the air-pollution in their area concerns them a great deal, as they point out themselves.
-However this issue represents a *continuous* concern that they may have got used to over the time, as opposed a new issue that emerged recently.
-If this explanation holds, this entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by very high levels of personal relevance.
-These latter findings are also consistent with the findings of @alonbarkat_2017.
-In that study, the scholars assessed citizens' trust in the government electricity company, and its shaping by its familiar symbol, given citizens' recent personal experience of prolonged blackouts.
-Whilst their study was not purposely designed to test the interaction between symbols and personal relevance, one can assume that those who personally experienced blackouts perceived electricity service as more personally relevant.
-Still, they found that citizens who experienced blackouts were influenced by the symbol, as much as those who did not.
+How can we explain the finding that the positive effect of the real symbols was stronger among Haifa-Bay residents?
+The fact that this pattern evident in both policy plans suggests that these differences are not explained by perceived personal relevance.
+Rather, these differences could be explained, by the lower baseline of Haifa-Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
+Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
+as in the case of Haifa-Bay subjects), than shifting them from medium to high levels (i.e.
+as in the case of center subjects).
+Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
+This tentative explanation is supported by the fact that the interaction remains intact when controlling for demographic differences between the areas.[^footnote_ceiling_effect]
+
+[^footnote_ceiling_effect]: This tentative explanation is also supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
+This comparison shows a pattern of decreased marginal reduction.
+In the Haifa-Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased by from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
+In the center, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
+With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa-bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.
+
+How can we reconcile the findings of this study with the proposed theory?
+One plausible explanation is that despite the relatively high involvement of  Haifa-bay residents, they were still not motivated enough to use the central route and to disregard the peripheral cues.
+If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance.
+Indeed, Petty and Cacioppo have admitted that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p.
+206].
+The findings in this study are also consistent with the findings of @alonbarkat_2017, where they found that citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) were nonetheless significantly affected by a symbol of the government-owned electricity company.
+
+The results of this study, if generalizable, have significant normative implications.
+They challenge the optimistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
+Instead, they suggest that more often than not, citizens rely on symbols and other peripheral cues in public communications, including when these communications concern issues that have direct implications on citizens' personal welfare.
+This inclination is in tension with the assumption that citizens should form their opinions about their government and about public affairs, based on rational thinking [@dahl_1973; @soroka_2010].
+It also exacerbates the concern that government organizations will strategically use symbolic communications to manipulate public opinion, and cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
+
+Notwithstanding these conclusions, I acknowledge the limitations of this study, which focuses, empirically, on one specific case.
+Future studies may put these findings to additional test by examining additional cases of public organizations and policy areas, as well as different forms of communications.
+Additionally, the comparison between the two areas is limited insofar as the results suggest that they have diverging prior beliefs about the subject.
+A comparison between two groups that have similar prior beliefs would be more reliable.
+Finally, as noted above, one can question the validity of relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications.
+Still, the main results are robust to different model specifications, and operationalizations of personal relevance and message elaboration, which substantiate their validity.
 

### 2018-07-05 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 ---
-title: "The persuasion of symbolic elements in government public communications, and their moderation by personal relevance"
+title: "The persuasion of symbolic elements in government public communications, and their moderation by the personal relevance of the communication"
 author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
@@
 *Recent experimental studies have demonstrated that government public communications can enhance citizens' trust in government organizations and their policies not only by conveying substantive information, but also by incorporating strategically desigened symbolic element that evoke positive feelings and associations.
-Yet, under which conditions are citizens more/less likely to be emotionally persuaded by these symbols?
-Building on the social psychology Elaboration Likelihood Model (ELM), I theorize that citizens are less susceptible to symbols when they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to invest in elaborate processing.
-I put this theory to test through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing the air pollution in a specific area (the Haifa-Bay) and for reducing domestic waste.
-I operationalize the perceived personal relevance of these policies both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
-The results of both methods do not support the hypothesis that higher personal relevance attenuates the effect of symbols.
-They tentatively suggest that symbols are more likely to persuade citizens who have predominant negative attitudes.*
+Yet, under which conditions are citizens more/less likely to be persuaded by symbols?
+Building on the social psychology Elaboration Likelihood Model (ELM), I theorize that citizens are less susceptible to symbols and more likely to scrutinize the substantive content of the communication, the more they perceive the policy issue in the communication as personally relevant.
+I test this theory through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing the air pollution in a specific area (the Haifa-Bay).
+The perceived personal relevance of the policy is operationalized both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+Counter to the hypotheses, these comparisons suggest that higher perceived personal relevance does not attentuate the effect of symbols.
+The theoretical and norative implications of these findings are discussed.*
 
@@
 Whereas most of the studies have focused on the *informative* aspects of government communications [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @grimmelikhuijsen_2015; @ho_2017], recent experimental studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as  brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
-The latter studies suggested that that familiar and well-designed symbols can enhance citizens' trust irrationally through a mechanism of "evaluative conditioning" - unconscious transfer of affect from the symbols to the public organizations and policies associated with them [@dehouwer_2012].
-Understanding the effect of symbolic elements is important, insofar as they exist in almost any communications between public organizations and citizens, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @grimmelikhuijsen_2015; @ho_2017], recent experimental studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as  brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
+Such symbols and others exist in almost every government communication, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@Eshuis_2012; @Marland_2017].
 
@@
 Similarly, higher perceived personal relevance are expected to enhance citizens' inclination to scrutinize the substantive content of communication.
-Employing a survey experiment, I test this hypothesis in the context of the Israeli Environment Protection Ministry, and two of its policy plans: reducing the air pollution in a specific area (the Haifa-Bay); and reducing domestic waste.
-I operationalize the perceived personal relevance of these policies both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+Employing a survey experiment, I test this hypothesis in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay).
+I operationalize the perceived personal relevance of the policy plan both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
 
@@
 The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a theoretical framework for investigating the effects of "persuasive" communications on people's attitudes [@petty_1986; @petty_2011].
-Whilst this model has been applied in various contexts, thus far, the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.
-
-ELM postulates that people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
+According to ELM, people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
 When people have high motivation and ability to elaborate on the message, they are likely to focus on the arguments in the communication which are central to the merits of the issue, and scrutinize them ("central route").
@@
 These two routes for persuasion are regarded as two ends of an "elaboration continuum".
-When people are located between these two edges, as they are much of the time, persuasion will be determined by a mixture of these processes.
+People can be also located between these two edges, and then persuasion will be determined by a mixture of these processes.
 
@@
 
-This literature has pointed to a variety of factors that shape people's motivation and ability to think about the message, and accordingly - their placement along the elaboration continuum and inclination to be persuaded either by the arguments or by peripheral cues.
+This literature has pointed to a variety of factors that shape people's motivation and ability to think about the message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
 Among others, scholars have theorized that the more people perceive the issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater.
 That postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
-These studies have demonstrated that manipulating the perceived personal relevance of the communication affects subjects' inclination to elaborate, and accordingly, it increases the effect of arguments in the communication and decreases the effect of peripheral cues.
+These studies have demonstrated that increasing the perceived personal relevance of a communication enhances the effect of arguments in the communication and attenuates the effect of peripheral cues.
 Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors]
@@
 
-Connecting the public administration literature on citizens' responses to government public communications with the above insights from social psychology literature, I theorize that the extent to which citizens perceive the communication as personally relevant moderates the effects of symbolic elements on the one hand and of substantive information on the other hand.
-I hypothesize that:
+Connecting the above public administration literature on citizens' responses to government public communications with the social psychology ELM literature, I theorize that:
 
@@
 I tested the above mentioned hypotheses via a randomized survey experiment, building on the methodology of @petty_1983.
-The study focuses on the case of the Israeli Environment Protection Ministry (hereafter: EPM), and examines citizens' responses to communications of EPM regarding two of its current policy plans.
+I focus on the case of the Israeli Environment Protection Ministry (hereafter: EPM), and examines citizens' responses to communications of EPM regarding two of its current policy plans.
 The first policy regards *reducing the air pollution in the Haifa-Bay area*, located in the north of Israel.
@@
 Therefore, adding this policy plan enables to further confirm that their different responses to the air-pollution policy, if found, are explained by differences in perceived personal relevance.
-For the sake of simplicity, I henceforth refer to these two policy plans as "air-pollution" and "recycling" policies.
+I henceforth refer to these two policy plans as "air-pollution" and "recycling".
 
-EPM also makes a good case for this study due to its significant investment in public communications, and its deployment of various symbolic elements.
-Here, I focused on three symbolic elements which have been used in the EPM's public communications, and became widely recognized by the public.
+I focused on three symbolic elements which have been used in the EPM's public communications, and became widely recognized by the public.
 The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
@@
 The survey was conducted online through Qualtrics Survey Software.
-To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
-I will henceforth refer to these two groups of cities as Haifa-bay and center.
-To select and recruit residents of these specific cities, I was assisted by an Israeli internet research panel company *iPanel*.
+To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country (hereafter "center").[^footnote_cities] To select and recruit residents of the selected cities, I was assisted by an Israeli internet research panel company *iPanel*.
 The online survey link was sent by iPanel, between 28.1-1.2.2018.
 A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
-Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
-These filters are not significantly associated with the areas or the experimental conditions.
-Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
+After filtering,[^footnote_filters] I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
+
+[^footnote_cities]: The cities from the Haifa-Bay area are: *Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*.
+The matched cities from the center are: *Natania*, *Petach-Tikva* and *Rishon-Lezion*.
+The socioeconomic characteristics of the cities are summarized in the supplementary appendix.
+
+[^footnote_filters]: I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+These filters are niether associated with the areas nor with the experimental conditions.
 
@@
 Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
-In addition to these three likert-scale questions, they were also asked to describe the most salient environmental issue in their particular area of residence.
 These questions were designed to prime subjects to think about the impact of environmental issues to their own lives.
-They were also designed to prime Haifa-bay residents to think about the personal relevance of the air pollution in their area.
+Subjects were also asked to describe the most salient environmental issue in their particular area of residence.
+The latter open question was specifically designed to prime Haifa-bay residents to think about the personal relevance of the air pollution in their area.
 Subjects in the relevance control group were asked equivalent questions about their field of occupation.
 
-After the relevance manipulation, participants were presented with the two policy plans of EPM, which they were told that were obtained from EPM's annual work plan.
+Participants were then presented with the two policy plans of EPM, which they were told that were obtained from EPM's annual work plan.
 Each policy plan was followed by questions about respondents' trust in them.
@@
 The information in the strong policy plans condition was taken from the real work plan and from other official sources, whereas the information in the weak policy plans was fictional, and was deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.
-The full texts of the weak and strong conditions for the two policy plans is displayed in the supplementary appendix.
+The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
 Each subject, moreover, was exposed to one strong and one weak policy communication, displayed in a random order.
@@
 In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with images of unfamiliar people.
-The symbols conditions are displayed in **Appendix A**.
+The symbols conditions are displayed in **Appendix B**.
 Further details about the real and fake symbols are found in the supplementary appendix.

### 2018-07-06 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @grimmelikhuijsen_2015; @ho_2017], recent experimental studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as  brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
-Such symbols and others exist in almost every government communication, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@Eshuis_2012; @Marland_2017].
+Such symbols and others exist in almost every government communication, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
 
@@
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-Participants were more likely to report low levels of trust in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
+Participants reported lower trust, on average, in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
 
-My key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.
-Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
-Manipulation checks for the information confirm that the weak policy plans were perceived as less effective in achieving the policy goal compared with the strong plans.
-The perceived personal relevance of the communication is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
+My key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.[^footnote_symbols_manipulation_check] The perceived personal relevance of the communication is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
 I coded living in Haifa-bay area according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
-Validity checks confirm that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
+My data confirmes that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
 Moreover, when directly asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects regarded to the air-pollution.
@@
 The results of the all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
+
+[^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
 
@@
 I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
-First, in addition to the above operationalizations of personal relevance, I also relied on subjects' subjective reporting.
-Second, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey: the time participants spent on scanning the policy plans and their score in a memory test.
+*First*, in addition to the above operationalizations of personal relevance, I also relied on subjects' subjective reporting.
+*Second*, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey: the time participants spent on scanning the policy plans and their score in a memory test.
 I also tested whether personal relevance decreased the delta (within-subjects) between trust in strong and weak policy plans presented to each subject.
-Third, I added a set of individual-level controls, and factors related to personal relevance of air-pollution, and to personal interest in environmental issues.
+*Third*, I added a set of individual-level controls, and factors related to personal relevance of air-pollution, and to personal interest in environmental issues.
 Finally, I replicated my analyses on the unfiltered sample.
@@
 
-Extant Public-Administration research has demonstrated that government communication can affect citizens' trust not only by conveying substantive information, but also by using familiar symbolic elements.
-This study contributes to this literature by exploring the postulation, derived from social psychology, that people are less susceptible to symbols and more likely to scrutinize the substantive information in the communication the more they perceive it as personally relevant.
-I put this theory to rigorous empirical test in the context of government communications, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
+This study contributes to the growing public administration research on citizens' responses to government public communications, and specifically to symbolic elements entangled in these communications.
+I explored the postulation, derived from social psychology, that citizens are less susceptible to symbols and more likely to scrutinize the substantive information in the communication the more they perceive it as personally relevant.
+I put this theory to rigorous empirical test, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
 I further focused on its policy plan regarding air pollution in a specific area, to capture natural variation in citizens' perceptions of the personal relevance.
 In addition to utilizing these natural differences, I also used manipulated the personal relevance of the policy plans.
-To the best of my knowledge, this is the first study to assess the  moderating role of perceived personal relevance on message elaboration and the effect of symbol in the administrative context.
+To the best of my knowledge, this is the first study to assess the  moderating role of perceived personal relevance on citizens' responses to government symbolic communications.
 
@@
 If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
-Priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also did not moderate the effects of the symbols and information in the communications.
+Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also did not moderate the effects of the symbols and information in the communications.
 
 How can we explain the finding that the positive effect of the real symbols was stronger among Haifa-Bay residents?
-The fact that this pattern evident in both policy plans suggests that these differences are not explained by perceived personal relevance.
-Rather, these differences could be explained, by the lower baseline of Haifa-Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
+Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance.
+Rather, they can be explained by the lower baseline of Haifa-Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
 Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
 as in the case of Haifa-Bay subjects), than shifting them from medium to high levels (i.e.
-as in the case of center subjects).
-Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
-This tentative explanation is supported by the fact that the interaction remains intact when controlling for demographic differences between the areas.[^footnote_ceiling_effect]
+as in the case of center subjects), which results in a ceiling effect.
+Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.[^footnote_ceiling_effect] Another related explanation is that the symbols distracted the subjects and decreased their inclination to think about this topic.
+As a result, they caused Haifa-bay subjects to disregard their prior beliefs about EPM and its actions regarding the air-pollution.[^footnote_mediation_elaboration]:
 
-[^footnote_ceiling_effect]: This tentative explanation is also supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
+[^footnote_ceiling_effect]: This tentative explanation is supported by the fact that the interaction remains intact when controlling for demographic differences between the areas.
+It is also supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
 This comparison shows a pattern of decreased marginal reduction.
@@
 
+[^footnote_mediation_elaboration]: This explanation is further supported by the survey data.
+The real symbols had a negative effect on the elaboration of these policies,  as measured by reaction time and memory test.
+The decrease in elaboration mediates the effect of symbols on trust.
+These analyses are presented in the supplentary appendix.
+
 How can we reconcile the findings of this study with the proposed theory?
-One plausible explanation is that despite the relatively high involvement of  Haifa-bay residents, they were still not motivated enough to use the central route and to disregard the peripheral cues.
+One plausible explanation is that despite the relatively high involvement of Haifa-bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues.
 If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance.
@@
 They challenge the optimistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
-Instead, they suggest that more often than not, citizens rely on symbols and other peripheral cues in public communications, including when these communications concern issues that have direct implications on citizens' personal welfare.
-This inclination is in tension with the assumption that citizens should form their opinions about their government and about public affairs, based on rational thinking [@dahl_1973; @soroka_2010].
-It also exacerbates the concern that government organizations will strategically use symbolic communications to manipulate public opinion, and cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
+Instead, they suggest that more often than not, citizens rely on symbols and other peripheral cues in public communications, including when these communications concern issues that have direct implications on thrir own lives.
+This inclination is in tension with the assumption that citizens should form their opinions about their government and about public affairs, based on their rational thinking [@dahl_1973; @soroka_2010].
+It also buttresses the concern that government organizations will strategically use symbolic communications to manipulate public opinion, and cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
 
-Notwithstanding these conclusions, I acknowledge the limitations of this study, which focuses, empirically, on one specific case.
-Future studies may put these findings to additional test by examining additional cases of public organizations and policy areas, as well as different forms of communications.
-Additionally, the comparison between the two areas is limited insofar as the results suggest that they have diverging prior beliefs about the subject.
+Notwithstanding these conclusions, the limitations of this study should be acknowledged.
+The study focuses, empirically, on one specific case.
+Future studies may put these findings to further test by examining additional cases of public organizations and policy areas, as well as different forms of communications.
+Additionally, the comparison between the two areas is imperfect, insofar as the differences in personal relevance are confounded with differences in prior beliefs about the subject, which I cannot effectively control.
 A comparison between two groups that have similar prior beliefs would be more reliable.
-Finally, as noted above, one can question the validity of relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications.
+Finally, one can question the validity of relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications.
 Still, the main results are robust to different model specifications, and operationalizations of personal relevance and message elaboration, which substantiate their validity.
 
-##Appendix A: Symbols manipulation
+##Appendix A: Information manipulation
+
+**Air-pollution policy** (Reducing the air-pollution in the Haifa-Bay)
+
+EPM is working to reduce the air-pollution in the Haifa-Bay through:
+
+*Strong*
+
+* **Increasing the supervision of the factories in Haifa-Bay**.
+In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways.
+The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the amount of fines for pollutants.
+
+* **Reduction of smoke emissions from vehicles in Haifa Bay**.
+The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area.
+The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and promotes the operation of a "clean-air area" that restricts the entry of polluting vehicles.
+
+*Weak*
+
+* **Decreasing the supervision of the factories in Haifa-Bay**.
+The Ministry is preparing for a change in the method of supervision of the factories.
+The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the amount of fines.
+The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.
+
+* **Raising citizens' awareness of the efforts to improve air quality**.
+In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful.
+The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents.
+To this end, the ministry has increased its investment in public relations and publicity in this subject.
+
+<br>
+
+**Recycling policy** (Reducing waste and increasing recycling)
+
+EPM is working to reduce the amount of waste and increase its recycling through:
+
+*Strong*
+
+* **Packaging recycling - Increased supervision of manufacturers**.
+In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, which imposes on manufacturers and importers the responsibility for recycling the packaging.
+The Ministry will work to increase enforcement by virtue of this act, and will enforce it with regard to additional manufacturers and importers.
+
+* **Reducing the usage of disposable bags**.
+In order to reduce the use of disposable plastic bags, the Ministry enforces the Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the chains.
+The Ministry works to implement the act, and encourages the transition to reusable grocery bags.
+
+*Weak*
+
+* **Packaging recycling - Decreased supervision of manufacturers**.
+The Ministry is preparing to a change in the method of supervision of the manufacturers, who are responsible for the recycling of product packaging by virtue of the act The ministry will reduce the number of inspections, rely on manufacturers' self-reports regarding their compliance with the requirements of the act, and reduce the amount of fines.
+The change is coordinated with members of the industry, which are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.
+
+* **Reducing the usage of disposable bags**.
+In recent years, the Ministry has taken steps to encourage the reduction of waste, which have been partially successful.
+The Ministry works to raise awareness of the actions taken and to highlight their success in order to improve its image among the public.
+To this end, the ministry has increased its investment in public relations and publicity in this subject.
+
+<br>
+
+##Appendix B: Symbols manipulation
 ![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/symbols_manipulation.png)

### 2018-07-08 paper3_APPENDIX.Rmd
Add files via upload

---
title: "Supplementary appendix"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

<br>

Last edited at `r Sys.Date()`.

<br>

```{r , include=FALSE, echo=FALSE}
source("SVIVA_exp2_dm_03.R")

SVIVA1_01 = read.csv("SVIVA1_01.csv")
CELEBS_00 = read.csv("CELEBS.csv")

SVIVA2_01 = SVIVA2_01 %>%  
mutate(AREA_center = Recode(AREA,"0=1;1=0"))

```

```{r , include=FALSE, echo=FALSE}
library(tidyverse)
library(sjPlot)
library(stargazer)
```

---

#Contents:

1. Supplementary information about the symbolic elements.

2. Manipulation and validity checks.

3. Summary statistics.

4. Supplementary analyses.

5. English translation of the survey experiment.

---

<br>

#1. Supplementary information about the symbolic elements.

In this section, I provide additional details about the creation of the "real" and "fake" symbolic elements that were included in the policy plans in the survey.

##Real symbols

The campaign images which were included in the policy plans in the real symbols condition were downloaded from EPM's official website (http://www.sviva.gov.il), from the section that archives the Ministry's publications and public campaigns. After downloading the images, I cropped them (via GIMP software). The sources of the images are detailed below:

**Air-pollution policy**

Campaign name: "Starting to think green"; Endorser: Tal Friedman.

Source: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/Publications/P0601-P0700/P0641.aspx

**Recycling policy**

Campaign name: "From now on, every bag is taken seriously"; Endorser: Ido Rosenblum.

Source: http://www.sviva.gov.il/InfoServices/NewsAndEvents/MessageDoverAndNews/Pages/2016/December2016/plastic-bags-campaign-2016-IR.aspx

<br>

##Fake symbols

The fake logo and campaign images were specifically designed to represent graphical elements that resemble the look and aesthetic qualities of the real symbolic elements, as much as possible, while removing their symbolic aspects.

The fake logo was created via MS paint software. I replaced the leaves/hands from the original logo with a shape of stars with rounded edges, and replaced the green color with blue. I deliberately selected a natural element - star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturalness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].

To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their face expressions in the campaign images. For this purpose, I used the website www.istockphoto.com that offers multiple collections of professional images for purchase. The original photos which I purchased from the website, and their sources are detailed below. Thereafter, I took these images of models, and edited them (via GIMP software) to create images which are aesthetically similar to the original campaign images, yet without their symbolic aspects. For the recycling policy, I used the same image from EPM's reusable bags campaign, while replacing Rosenblum's face with the face of the unfamiliar model, and changing the color of the bag from green to blue. For the The Air-pollution policy, I took the purchased image of the unfamiliar model, and added a blue rectangle behind him (instead of the green background behind Friedman). I also added a blue geometric shape above the person's head, which I took from a logo of an Israeli mortgage bank, against Friedman's green hair. The latter addition was important, given that the green hair not only has a symbolic connotation, but also functions as an unusual, surprising element, that attracts people's attention.

**Air-pollution policy**

Original image:

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_air_model.jpg")
```

Source: https://www.istockphoto.com/il/photo/smiling-forty-something-man-gm469597956-62477336

**Recycling policy**

Original image:

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_waste_model.jpg")
```

Source: https://www.istockphoto.com/il/photo/young-man-smiling-portrait-gm516728601-48347532

<br>

#2. Manipulation and validity checks
<br>

#3. Summary statistics

**Table A1: summary statistics of research variables**

```{r,results="asis", echo=FALSE,warning=FALSE,message=FALSE}
SVIVA2_01 %>% 
  select(TRUST_air_INDEX,
         TRUST_waste_INDEX,
         WITHIN_DELTA,
         AREA_center,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs,
         ENVIRONMENT_INTEREST,
         CHILDREN,
         CHILDREN_young,
         GENDER,
         AGE,
         GOV_TRUST,
         IDEOLOGY,
         EDUCATION,
         INCOME,
         HOME) %>% 
  stargazer(type="html",
            digits = 3,
            covariate.labels = c("1. Trust in Air-pollution policy",
                                 "2. Trust in recycling policy",
                                 "3. Delta (within subjects)",
                                 "4. Area (0=Haifa-Bay; 1=center)",
                                 "5. Perceived personal relevance - air-pollution",
                                 "6. Perceived personal relevance - recycling",
                                 "7. Interest in environmental issues",
                                 "8. Having children",
                                 "9. Having young children (under 12)",
                                 "10. Gender (Woman=1)",
                                 "11. Age",
                                 "12. Trust in government ministries",
                                 "13. Political Ideology (10 = extreme left)",
                                 "14. Education",
                                 "15. Income (5=high)",
                                 "16. Home ownership"))
```

<br>

**Table A2: Correlation matrix**

<font size="0.5">

```{r, echo=FALSE,warning=FALSE,message=FALSE}
SVIVA2_01 %>% 
  select(TRUST_air_INDEX,
         TRUST_waste_INDEX,
         WITHIN_DELTA,
         AREA_center,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs,
         ENVIRONMENT_INTEREST,
         CHILDREN,
         CHILDREN_young,
         GENDER,
         AGE,
         GOV_TRUST,
         IDEOLOGY,
         EDUCATION,
         INCOME,
         HOME) %>% 
  sjt.corr(triangle="lower",
           remove.spaces=T,
           digits = 2,
           na.deletion="pairwise",
           var.labels = c("1",
                          "2",
                          "3",
                          "4",
                          "5",
                          "6",
                          "7",
                          "8",
                          "9",
                          "10",
                          "11",
                          "12",
                          "13",
                          "14",
                          "15",
                          "16"))
```

</font>

#4. Supplementary analyses

**Table XX: Regression table - subjective reporting of perceived personal relevance**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
mod_air_1.3_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)

mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
mod_waste_1.3_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)

stargazer(mod_air_1.2_apx,mod_air_1.3_apx,
          mod_waste_1.2_apx,mod_waste_1.3_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Reported relevance",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Reported relevance x Real symbols",
                             "Reported relevance x Fake symbols",
                             "Reported relevance x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table XX: Regression table - effect of personal relevance on reaction time**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_RT_air_1.1_apx = lm(ELABORATION_air_time_log~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_RT_air_1.2_apx = update(mod_RT_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

mod_RT_waste_1.1_apx = lm(ELABORATION_waste_time_log~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_RT_waste_1.2_apx = update(mod_RT_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_RT_air_1.1_apx,mod_RT_air_1.2_apx,
          mod_RT_waste_1.1_apx,mod_RT_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table XX: Regression table - effect of personal relevance on memory score**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_memory_air_1.1_apx = lm(MEMORY_air_score~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_memory_air_1.2_apx = update(mod_memory_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

mod_memory_waste_1.1_apx = lm(MEMORY_waste_score~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_memory_waste_1.2_apx = update(mod_memory_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_memory_air_1.1_apx,mod_memory_air_1.2_apx,
          mod_memory_waste_1.1_apx,mod_memory_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table XX: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_delta_1.1_apx = lm(WITHIN_DELTA~AREA_center+RELEVANCE_exp,data=SVIVA2_01)
mod_delta_1.2_apx = update(mod_delta_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_memory_air_1.1_apx,mod_memory_air_1.2_apx,
          mod_memory_waste_1.1_apx,mod_memory_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table XX: Regression table - adding control variables**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION,data=SVIVA2_01_comb)
mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))

mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION,data=SVIVA2_01_comb)
mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))

stargazer(mod_air_1.1_apx,mod_air_1.2_apx,
          mod_waste_1.1_apx,mod_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Gender (1=Woman)",
                             "Ideology",
                             "Trust in government ministries",
                             "Income",
                             "Education",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table XX: Regression table - adding personal relevance and motivational control variables**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+CHILDREN_young,data=SVIVA2_01_comb)
mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
mod_air_1.3_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+ENVIRONMENT_INTEREST+ENVIRONMENT_FOLLOW+CHILDREN_young,data=SVIVA2_01_comb)
mod_air_1.4_apx = update(mod_air_1.3_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak))

mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+ENVIRONMENT_INTEREST+ENVIRONMENT_FOLLOW+CHILDREN_young,data=SVIVA2_01_comb)
mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak))

stargazer(mod_air_1.1_apx,mod_air_1.2_apx,mod_air_1.3_apx,mod_air_1.4_apx,
          mod_waste_1.1_apx,mod_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Interest in environmental issues",
                             "Follows environmental issues in media",
                             "Having young children (under 12)",
                              "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

#5. English translation of the survey experiment

Below is the full text of the survey. Additional comments are presented in square beackets. The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here. The original Qualtrics file is available upon request.

**Greetings,**

**We are researchers from the Department of Political Science at the Hebrew University. The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly. The questionnaire filling time is about 5-10 minutes.**

**It is important for us to clarify that the questionnaire is voluntary. Filling out the questionnaire and submitting it represent your agreement to participate in the research. In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only. Non-consent to participate will be expressed in not filling of the questionnaire. The questionnaire is phrased in masculine form [in Hebrew] but addresses both men and women.**

**Thank you for your cooperation!**

---

**First, we would like to ask you a few general questions about your attitudes towards Israeli government ministries.**

<br>

**How would you evaluate the functioning of National Government Ministries in Israel?**

1. Very poor

2.

3.

4.

5.

6.

7. Very good

**To what extent do you do you have confidence/trust in Israeli Government Ministries?**

1. I have no confidence/trust

2.

3.

4.

5.

6.

7. I have great confidence/trust

**How would you rate your ideological standpoint on a left-right continuum?**

1. Extreme right

2.

3.

4.

5.

6.

7.

8.

9.

10. Extreme Left

---

[The following section includes a manipulation of perceived personal relevance of policy plans. Participants were randomly assigned to treatment and control conditions, as detailed below].

<br>

[Treatment]

**Now, we would like to ask you a few general questions about your interest in environmental issues.**

**To what extent are you interested in environmental issues?**

1. Little interested

2.

3.

4.

5.

6.

7. Very interested

**To what extent do you follow environmental issues in the media and/or in social networks?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**Compared to the current situation, do you think the government should invest more or less in dealing with environmental issues?**

1. Invest much less

2.

3.

4.

5.

6.

7. Invest much more

**In which residential area do you currently live?**

1. North

2. Haifa and the Krayot

3. Center

4. Tel Aviv

5. Lower Galilee

6. Jerusalem

7. Judea and Samaria

8. South

**What is the name of the locality where you live today? _________________**

**In your opinion, what is the most disturbing environmental problem in your area? ________________________________________**

[Control]

<br>

**Now, we would like to ask you a few general questions about your area of occupation.**

**In which sector are you currently employed?**

1. Private sector

2. Public sector

3. Third Sector

4. Other

**What is your field of profession/study? ______________**

**To what extent do you think your profession is interesting?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**To what extent do you follow topics related to your area of occupation in the media and/or social networks?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**Compared to the current situation, do you think the government should assist more or less to promote your field of occupation?**

1. Assist much less

2.

3.

4.

5.

6.

7. Assist much more

**What, in your opinion, might attract people to choose your occupation? _________________________________________**

---

**Next, we will present you two policy plans on specific environmental issues. The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.**

**At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.**

[Participants are then presented with the two policy plans (air-pollution and recycling), in a random order. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]

**Now, we'd like to ask you a few questions about your position on the policy for "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay":**

**State to what extent do you agree with each of the following sentences.**

**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the actions mentioned in the policy plan were designed in a professional manner**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the policy plan is in the interest of citizens**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens.**

**I believe that EPM made an honest attempt to design a good policy plan**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

---

**The following sentences describe the way in which you read the latest policy plan that regarded to "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay".**

**State to what extent do you agree with each of the following sentences.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I paid much attention to reading the policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I skimmed the actions in the policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I tried to thoroughly understand the the policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**While going through the policy plan I was thinking about other things which are not related to it.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I tried to think how the policy plan will personally affect me.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**Try recalling the content of the latest policy plan.**
[Each subjects was asked about the latest policy plan presenter to her]

**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce air pollution in Haifa Bay?**

1. Supervision on the factories

2. Clean air area

3. Investment in public relations

4. The ammonia tank

5. I can not remember

**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce waste and increase recycling?**

1. Supervision on the manufacturers

2. compulsory charge on bags

3. Investment in public relations

4. plastic bottles

5. I can not remember

**To what extent did you feel that the policy on "reducing waste and increasing recycling" is personally relevant to you?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**To what extent did you feel that the policy on "Reducing the air-pollution in the Haifa-Bay" is personally relevant to you?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**In order to make sure you read the question carefully, please type the number 9 under "Other"?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

8. Other: ______

---

**We would like to ask you a few general questions:**

**What is your age?**

10----20----30----40----50----60----70----80

**What is your highest level of education?**

1.	Primary education or less

2.	Partial secondary education

3.	High education without high school diploma

4.	High education with high school diploma

5.	Non-academic tertiary education

6.	Partial academic degree

7.	Full academic degree (first degree)

8.	Full academic degree (second degree or higher).

**According to Israel's Central Bureau of Statistics the monthly average net income per household is approximately 15,500 NIS. Is your income: **

1.	Far below average

2.	Slightly below average

3.	Near average

4.	Slightly above average

5.	Far above average

**Are you a home owner?**

1. Yes

2. No

**In which residential area do you currently live?**

1. North

2. Haifa and the Krayot

3. Center

4. Tel Aviv

5. Lower Galilee

6. Jerusalem

7. Judea and Samaria

8. South

**What is your place of residence? ___________**

**Are you or one of your first-degree relatives working (or worked) in one of the factories in the Haifa Bay industrial area?**

1. No

2. Yes

**State the name of the place where you lived at high-school graduation: ____________**

**Area where you are currently working/studying?**

1. North

2. Haifa and the Krayot

3. Center

4. Tel Aviv

5. Lower Galilee

6. Jerusalem

7. Judea and Samaria

8. South

**Gender**

1.	Man

2. Woman

3.	I prefer not to answer

**What is the age of your oldest son/daughter?**

1. 0-6

2. 7-12

3. 13-18

4. 19 or more

5. I don't have any children

**Is Hebrew your native language?**

1. Yes

2. No

---

[The following section is a manipulation check for the symbols]

<br>

[For subjects assigned to the real symbols]:
**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**

**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**

**When you see the image, what does it make you feel?**

1. Very negative feeling

2.

3.

4.

5.

6.

7. Very positive feeling

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"**

**When you see the image, what does it make you feel?**

1. Very negative feeling

2.

3.

4.

5.

6.

7. Very positive feeling

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much:

<br>

[For subjects assigned to the fake symbols]:
**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**

**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**

**When you see the image, what does it make you feel?**

1. Very negative feeling

2.

3.

4.

5.

6.

7. Very positive feeling

**This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"**

**When you see the image, what does it make you feel?**

1. Very negative feeling

2.

3.

4.

5.

6.

7. Very positive feeling

**We would like to show you additional images, taken from advertisements of the Environmental Protection Ministry.**

[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]

**When you see the image, what does it make you feel?**

1. Very negative feeling

2.

3.

4.

5.

6.

7. Very positive feeling

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much:

<br>

[For subjets assigned to the no symbols]:

**Finally, we would like to show you a few images which were taken from advertisements of the Environmental Protection Ministry.**

[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]

**When you see the image, what does it make you feel?**

1. Very negative feeling

2.

3.

4.

5.

6.

7. Very positive feeling

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much:

---

**Thank you very much for participating in the study. Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently. The tasks related to "raising awareness" and "reducing supervision" are invented tasks that are not part of the Ministry of Environmental Protection's policy. [For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]**

**You may review the original policies of the Environmental Protection Ministry regarding the policy issues which were presented at the website of government work plans: plans.gov.il and at the Ministry's website: sviva.gov.il.**

#References

### 2018-07-08 SVIVA_exp2_dm_03.R

@@ -43,11 +43,11 @@ mutate(ENVIRONMENT_INTEREST = Recode(SVIVA2_raw$Q3.2,"0=NA"),
        ENVIRONMENT_PREFERENCE = Recode(SVIVA2_raw$Q3.4,"0=NA"),
        GOV_EVALUATION = SVIVA2_raw$Q2.3,
        GOV_TRUST = SVIVA2_raw$Q2.4,
-       IDEOLOGY = SVIVA2_raw$Q2.5,
+       IDEOLOGY = Recode(SVIVA2_raw$Q2.5,"0=NA"),
        CHILDREN = if_else(SVIVA2_raw$Q313==5,0,1),
        CHILDREN_young = if_else(SVIVA2_raw$Q313 %in% c(1,2),1,0),
        FACTORIES_relatives = Recode(SVIVA2_raw$Q314,"0=NA;1=0;2=1"))%>%
-  
+mutate(IDEOLOGY=IDEOLOGY-1) %>%   
   
   ##demographics
   mutate(AGE = Recode(SVIVA2_raw$Q24.2_1,"0=NA"),
@@ -532,7 +532,13 @@ SVIVA2_01_comb = SVIVA2_01 %>%
       EDUCATION,
       RECOGNIZE_SVIVA_logo,
       RECOGNIZE_air_real,
-      RECOGNIZE_waste_real) %>% 
+      RECOGNIZE_waste_real,
+      RELEVANCE_air_obs,
+      RELEVANCE_waste_obs,
+      ENVIRONMENT_INTEREST,
+      ENVIRONMENT_FOLLOW,
+      CHILDREN,
+      CHILDREN_young) %>% 
   gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
   mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
                               INFORMATION_waste),
@@ -542,8 +548,10 @@ SVIVA2_01_comb = SVIVA2_01 %>%
                                        ELABORATION_waste_time_log),
          MEMORY_score = ifelse(policy=="TRUST_air_INDEX",MEMORY_air_score,
                                MEMORY_waste_score),
-         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
-                                       ELABORATION_waste_time)) %>% 
+         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",RELEVANCE_air_obs,
[…]

### 2018-07-08 paper3_APPENDIX.Rmd
Add files via upload

@@
 
-**Table XX: Regression table - subjective reporting of perceived personal relevance**
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+library(car)
+
+SVIVA2_comb_robust_1 = SVIVA2_00 %>%
+  filter(!(AGE %in% 1:17)) %>% 
+  dplyr::select(IP,USER_ID,AREA,AREA_names,
+      RELEVANCE_exp,RELEVANCE_exp_n,
+      SYMBOL,SYMBOL_n,
+      INFORMATION_air,INFORMATION_air_n,
+      INFORMATION_waste,INFORMATION_waste_n,
+      TRUST_air_INDEX,
+      TRUST_waste_INDEX,
+      ELABORATION_air_time_log,
+      ELABORATION_waste_time_log,
+      ELABORATION_air_time,
+      ELABORATION_waste_time,
+      MEMORY_air_score,
+      MEMORY_waste_score,
+      GOV_TRUST,
+      GENDER,
+      AIR_order,
+      WASTE_order) %>% 
+  gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
+  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
+                              INFORMATION_waste),
+         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
+                                INFORMATION_waste_n),
+         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
+                                       ELABORATION_waste_time_log),
+         MEMORY_score = ifelse(policy=="TRUST_air_INDEX",MEMORY_air_score,
+                               MEMORY_waste_score),
+         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
+                                       ELABORATION_waste_time)) %>% 
+  mutate(TRUST_air_INDEX = ifelse(policy=="TRUST_air_INDEX",trust,NA),
+         TRUST_waste_INDEX = ifelse(policy=="TRUST_waste_INDEX",trust,NA),
+         INFORMATION_weak = Recode(INFORMATION,"0=1;1=0"),
+         AREA_center = Recode(AREA,"0=1;1=0"),
+         SYMBOL_t = factor(Recode(SYMBOL,"1=2;2=1")),
+         SYMBOL_t.r = factor(Recode(SYMBOL,"0=2;2=1;1=0")),
+         SYMBOL_t.r_2 = factor(Recode(SYMBOL,"0=2;2=0")),
+         ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order))
+
+```
+
+In the tables below, I report the results of additional robust analyses testing the research hypotheses regarding the moderating role of perceived personal.
+In **Table A3** I add subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
+Higher scores of perceived personal relevance did not attentuate the positive effect of the real symbols.
+However, it did slightly increase the effect of the weak information, regarding the air-pollution policy, in line with Hypothesis 2.
+
+In **Tables A4 - A6**, I examine the effect of the operationizations of personal relevance (i.e.
+the differences between the areas and the relevance manipulation) on three measures for subjects elaboration of the two policy plans.
+The first measure is the number of seconds participants spent on scanning the policy plans, log transformed (hereafter: reaction time).
+The second measure is participants' score in a memory test, which was conducted during the survey.
+Participants were asked to indicate whether a list of four items were included in the second policy plan which was presented to them, of which two were/were not included (participants could also select “I don’t know”).
+The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero.
+Accordingly, participants could receive the scores of 0, 1 or 2.
+The third measure is the delta of each subject’s trust in the strong and weak policy plans that were presented to them.
+The latter, within-subject analysis, utilizes the research design in which every participant was presented with one weak and one strong policies.
+Neither residing in the Haifa-bay nor the relevance treatment increase the elaboration of policy plans, based on these three measures.
+
+In **Tables A7** I add additional a set of individual-level control variables, and in **Table A8** I further control for additional factors that can be related to participants' motivation to elaborate, including having young children, general interest in environmental issues and following environmental issues in the media.
+The two final questions were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (n = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).Finally, in **Table A9**, I add those subjects who were filttered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
+The effects of the symbols and information manipulations and their interaction with the areas and the relevance manipulation are consistent with the main models presented in the paper in all these analyses.
+
+<br>
+
+**Table A3: Regression table - subjective reporting of perceived personal relevance**
 
@@
 
-**Table XX: Regression table - effect of personal relevance on reaction time**
+**Table A4: Regression table - effect of personal relevance on reaction time**
 
@@
 
-**Table XX: Regression table - effect of personal relevance on memory score**
+**Table A5: Regression table - effect of personal relevance on memory score**
 
@@
 
-**Table XX: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**
+**Table A6: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**
 
@@
 
-stargazer(mod_memory_air_1.1_apx,mod_memory_air_1.2_apx,
-          mod_memory_waste_1.1_apx,mod_memory_waste_1.2_apx,
+stargazer(mod_delta_1.1_apx,mod_delta_1.2_apx,
           type="html",style = "apsr",
-          dep.var.labels=c("Air-pollution","Recycling"),
+          dep.var.labels=c("Within-subject delta"),
           covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
@@
 
-**Table XX: Regression table - adding control variables**
+**Table A7: Regression table - adding control variables**
 
@@
 
-**Table XX: Regression table - adding personal relevance and motivational control variables**
+**Table A8: Regression table - adding personal relevance and motivational control variables**
 
@@
 
+**Table A9: Regression table - unfiltered sample**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp,data=SVIVA2_comb_robust_1)
+mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
+
+mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp,data=SVIVA2_comb_robust_1)
+mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
+
+stargazer(mod_air_1.1_apx,mod_air_1.2_apx,
+          mod_waste_1.1_apx,mod_waste_1.2_apx,
+          type="html",style = "apsr",
+          dep.var.labels=c("Air-pollution","Recycling"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Relevance treatment",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information",
+                             "Relevance treatment x Real symbols",
+                             "Relevance treatment x Fake symbols",
+                             "Relevance treatment x Weak Information"),
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+<br>
+
 #5. English translation of the survey experiment

### 2018-07-10 paper3_APPENDIX.Rmd
Add files via upload

@@
 
-In this section, I provide additional details about the creation of the "real" and "fake" symbolic elements that were included in the policy plans in the survey.
+In this section, I provide additional details about the of the EPM's symbols which were used in the experiment (the "real" symbols), as well as on the fictional, "fake", symbols.
 
@@
 
-The campaign images which were included in the policy plans in the real symbols condition were downloaded from EPM's official website (http://www.sviva.gov.il), from the section that archives the Ministry's publications and public campaigns.
-After downloading the images, I cropped them (via GIMP software).
-The sources of the images are detailed below:
-
-**Air-pollution policy**
-
-Campaign name: "Starting to think green"; Endorser: Tal Friedman.
-
-Source: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/Publications/P0601-P0700/P0641.aspx
-
-**Recycling policy**
-
-Campaign name: "From now on, every bag is taken seriously"; Endorser: Ido Rosenblum.
-
-Source: http://www.sviva.gov.il/InfoServices/NewsAndEvents/MessageDoverAndNews/Pages/2016/December2016/plastic-bags-campaign-2016-IR.aspx
+The three EPM symbols which were used in the the experiment are displayed in **Figure A1**.
+The first element is the unique brand logo of the EPM (image a.
+in figure A1).
+This logo consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
+The second symbol is the green color, which is strongly associated with taking care of the environment.
+The EPM's logo and the green color can be seen in almost all of the visual communications of the EPM, and they represent key elements of its unique "visual identity".
+The third element is celebrity endorsements.
+I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, that previously endorsed two salient advertising campaigns of the EPM.
+The campaign starring the comedian Tal Friedman (image b.) was launched in 2010, and included a series of advertisements in which Friedman was presented with a green grass head, and accordingly the campaign's slogan was: "starting to think green".
+The campaign starring the comedian Ido Rosenblum (image c.) was launched in 2017, and was focused on reducing the use of disposable bags.
+The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.[^footnote_lapam_reports] The campaign images were downloaded from EPM's website, and thereafter were cropped, to remove any text (via GIMP software).
+
+<br>
+**Figure A1: symbolic elements of EPM**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/EPM_symbols.png) 
+<font size="0.5">
+
+Notes:
+
+a. EPM logo.
+b.
+Tal Friedman, comedian,  EPM campaign “starting to think green” (2010): "Isn't money growing on trees?
+Moving to environmental consumption and saving at least 6,000 NIS per year!", "starting to think green", "The Environmental Protection Ministry".
+c.
+Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "The reusable bag is again left at home?
+A tip from Ido: Hang it on the door handle and you will not leave without it", "Taking every bag seriously", "The Environmental Protection Ministry".
+
+</font>
+
+[^footnote_lapam_reports]: The Multimedia files and evaluation reports for the  "starting to think green" campaign, starring Tal Friedman, are available in the following link: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/Publications/P0601-P0700/P0641.aspx The media files for the "reusable bags" campaign, starring Ido Rosenblum, are available at: http://www.sviva.gov.il/InfoServices/NewsAndEvents/MessageDoverAndNews/Pages/2016/December2016/plastic-bags-campaign-2016-IR.aspx.
+The evaluation report for this campaign is available at: https://cdn.the7eye.org.il/uploads/2017/09/plastic-bags2017.pdf.
+All these materials are available in Hebrew [last entered: July 2017].
 
@@
 
-The fake logo and campaign images were specifically designed to represent graphical elements that resemble the look and aesthetic qualities of the real symbolic elements, as much as possible, while removing their symbolic aspects.
+The fake symbols were specifically designed to represent graphical elements that resemble the look and aesthetic qualities of the familiar EPM symbols, as much as possible, while removing their symbolic aspects (i.e.
+without activating emotions and associations which can be attached to the government ministry and environmental issues).
+Accordingly, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
 
@@
 To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their face expressions in the campaign images.
-For this purpose, I used the website www.istockphoto.com that offers multiple collections of professional images for purchase.
-The original photos which I purchased from the website, and their sources are detailed below.
-Thereafter, I took these images of models, and edited them (via GIMP software) to create images which are aesthetically similar to the original campaign images, yet without their symbolic aspects.
+For this purpose, I used the website www.istockphoto.com that offers multiple collections of professional images for purchase.[^footnote_sources_fake_models] Thereafter, I took these images of models, and edited them (via GIMP software) to create images which are aesthetically similar to the original campaign images, yet without their symbolic aspects.
 For the recycling policy, I used the same image from EPM's reusable bags campaign, while replacing Rosenblum's face with the face of the unfamiliar model, and changing the color of the bag from green to blue.
@@
 The latter addition was important, given that the green hair not only has a symbolic connotation, but also functions as an unusual, surprising element, that attracts people's attention.
-
-**Air-pollution policy**
-
-Original image:
-
-```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
-knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_air_model.jpg")
-```
-
-Source: https://www.istockphoto.com/il/photo/smiling-forty-something-man-gm469597956-62477336
-
-**Recycling policy**
-
-Original image:
-
-```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
-knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_waste_model.jpg")
-```
-
-Source: https://www.istockphoto.com/il/photo/young-man-smiling-portrait-gm516728601-48347532
+The original and edited photos are displayed below:
+
+<br>
+
+**Figure A2: fake symbolic elements.**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_symbols_appendix.png)
+
+<br>
+
+[^footnote_sources_fake_models]: The original photo for the air-pollution policy was purchased from the following link: https://www.istockphoto.com/il/photo/smiling-forty-something-man-gm469597956-62477336, The original photo for the recycling policy was purchased from the following link:
+https://www.istockphoto.com/il/photo/young-man-smiling-portrait-gm516728601-48347532
 
@@
 
-In the tables below, I report the results of additional robust analyses testing the research hypotheses regarding the moderating role of perceived personal.
-In **Table A3** I add subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
-Higher scores of perceived personal relevance did not attentuate the positive effect of the real symbols.
-However, it did slightly increase the effect of the weak information, regarding the air-pollution policy, in line with Hypothesis 2.
-
-In **Tables A4 - A6**, I examine the effect of the operationizations of personal relevance (i.e.
-the differences between the areas and the relevance manipulation) on three measures for subjects elaboration of the two policy plans.
+In the tables below, I report the results of additional robust analyses testing the moderating role of the perceived personal relevance of the communications.
+In **Table A3** I analyze subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
+These analyses show that higher scores of perceived personal relevance did not attentuate the positive effect of the real symbols.
+However, in line with Hypothesis 2, it did slightly increase the effect of the weak information with regard to the air-pollution policy.
+
+In **Tables A4 - A6**, I examine the effects of relevance treatment and the differences between the areas on subjects elaboration of the two policy plans, using three additional measures.
 The first measure is the number of seconds participants spent on scanning the policy plans, log transformed (hereafter: reaction time).
@@
 Accordingly, participants could receive the scores of 0, 1 or 2.
-The third measure is the delta of each subject’s trust in the strong and weak policy plans that were presented to them.
-The latter, within-subject analysis, utilizes the research design in which every participant was presented with one weak and one strong policies.
+The third measure is the delta between trust in the strong and weak policy plans presented to each subject.
+This within-subject analysis utilizes the research design in which every participant was presented with one weak and one strong policies.
 Neither residing in the Haifa-bay nor the relevance treatment increase the elaboration of policy plans, based on these three measures.
 
-In **Tables A7** I add additional a set of individual-level control variables, and in **Table A8** I further control for additional factors that can be related to participants' motivation to elaborate, including having young children, general interest in environmental issues and following environmental issues in the media.
-The two final questions were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (n = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).Finally, in **Table A9**, I add those subjects who were filttered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
-The effects of the symbols and information manipulations and their interaction with the areas and the relevance manipulation are consistent with the main models presented in the paper in all these analyses.
+In **Tables A7 and A8**, I replicate the main analyses while adding additional control variables.
+In Tables A7, I control for demographics and additional individual-level covariates, including ideology and trust in government ministries in general.
+In Table A8 I further control for factors that can be related to participants' motivation to elaborate, including having young children, general interest in environmental issues and following environmental issues in the media.
+The two final variables are based on survey items which were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (n = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).Finally, in **Table A9**, I add those subjects who were filttered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
+In all these analyses, the effects of the symbols and information manipulations and their interaction with the areas and the relevance manipulation are consistent with the main models.
 

### 2018-07-10 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 
-*Recent experimental studies have demonstrated that government public communications can enhance citizens' trust in government organizations and their policies not only by conveying substantive information, but also by incorporating strategically desigened symbolic element that evoke positive feelings and associations.
-Yet, under which conditions are citizens more/less likely to be persuaded by symbols?
+*Recent experimental studies have demonstrated that government public communications can enhance citizens' trust in government organizations and their policies not only by conveying substantive information, but also by incorporating strategically designed symbolic element that evoke positive feelings and associations.
+Yet, under what conditions are citizens more/less likely to be persuaded by symbols?
 Building on the social psychology Elaboration Likelihood Model (ELM), I theorize that citizens are less susceptible to symbols and more likely to scrutinize the substantive content of the communication, the more they perceive the policy issue in the communication as personally relevant.
-I test this theory through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing the air pollution in a specific area (the Haifa-Bay).
-The perceived personal relevance of the policy is operationalized both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
-Counter to the hypotheses, these comparisons suggest that higher perceived personal relevance does not attentuate the effect of symbols.
+I test this theory through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted geographical area.
+The perceived personal relevance of the policy is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere.
+Counter to the well-grounded theoretical expectations hypotheses, these comparisons suggest that higher perceived personal relevance does not attentuate the effect of symbols.
 The theoretical and norative implications of these findings are discussed.*
@@
 
-While previous studies have substantiated the distinct effect of symbols on citizens' trust, they did not theorize, nor they empirically examined the conditions under which are these symbols are likely to be more/less effective.
+While previous studies have substantiated the distinct effect of symbols on citizens' trust, they did not theorize, nor empirically examine, the conditions under which these symbols are likely to be more, or less, effective.
 This research gap has great significance.
-First, from the practical point of view of government organizations, this may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
-Second, employing a broader perspective of democratic theory, one can argue that the emotive effect of symbols challenges the fundamental normative expectation that citizens' judgments should be based on their critical thinking.
+First, from the practical point of view of government organizations, understanding the boundries of the effects of symbols may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
+Second, employing a broader perspective of democratic theory, one can argue that in the public-sector domain the emotive effect of symbols undermines the fundamental normative expectation that citizens' judgments of government should be based on their critical judgment.
 Furthermore, the positive symbolic message can compensate for poor performance and create a misalignment between citizens' perceptions and the "real world" [@alonbarkat_2017].
-Hence, by identifying the circumstances under which citizens are more/less likely to be affected by symbols, we would better assess the potential risk for governments' manipulative use of public communications.
+Hence, by identifying the circumstances under which citizens are more/less likely to be affected by symbols, we could better assess the potential risk for governments' manipulative use of public communications.
 
-To address this literature gap, I draw upon the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
-I hypothesize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to invest in elaborate processing.
-Similarly, higher perceived personal relevance are expected to enhance citizens' inclination to scrutinize the substantive content of communication.
+To address this gap, I draw upon the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
+I hypothesize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
+Similarly, higher perceived personal relevance is expected to enhance citizens' inclination to scrutinize the substantive content of communication.
 Employing a survey experiment, I test this hypothesis in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay).
@@
 
-# The Elaboration Likelihood Model (ELM) and the effect of symbols and information in communicaions.
+# The Elaboration Likelihood Model (ELM) and the effect of symbols and information in communications.
 
@@
 According to ELM, people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
-When people have high motivation and ability to elaborate on the message, they are likely to focus on the arguments in the communication which are central to the merits of the issue, and scrutinize them ("central route").
+When people have high motivation and ability to elaborate on a message, they are likely to focus on the arguments in the communication that are central to the merits of the issue, and scrutinize them ("central route").
 Conversely, when they are unmotivated or unable to elaborate, they may rely on available heuristic cues that require relatively little amount of cognitive effort ("peripheral route").
 These two routes for persuasion are regarded as two ends of an "elaboration continuum".
-People can be also located between these two edges, and then persuasion will be determined by a mixture of these processes.
+People may also be located between these two edges, and then a mixture of these processes will determine their persuasion.
 
-In light of the latter conceptualization of ELM, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
+Viewed against the above theoretical framework of ELM, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
 Conversely, symbolic elements can be regarded as potential peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
-Accordingly, the more citizens are motivated to think about the content of the communication, and the more they are capable of doing so, the more they are likely to form their attitudes based on its substantive information.
+Accordingly, the more citizens are motivated to think about the content of the communication, and the more capable they are of doing so, the more they are likely to form their attitudes based on substantive information.
 Conversely, the less motivated and capable they are to elaborate, the more susceptible they are to symbolic elements in the communication.
 
-This literature has pointed to a variety of factors that shape people's motivation and ability to think about the message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
-Among others, scholars have theorized that the more people perceive the issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater.
-That postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
+This literature has pointed to a variety of factors that shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
+Among others, scholars have theorized that the more people perceive an issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater.
+This postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
 These studies have demonstrated that increasing the perceived personal relevance of a communication enhances the effect of arguments in the communication and attenuates the effect of peripheral cues.
@@
 
-*H<sub>1</sub> - Symbolic elements in communications are less (more) likely to increase citizens' trust in governemnt organizations and policicies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
+*H<sub>1</sub> - Symbolic elements in communications are less (more) likely to increase citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
 
@@
 
-I tested the above mentioned hypotheses via a randomized survey experiment, building on the methodology of @petty_1983.
-I focus on the case of the Israeli Environment Protection Ministry (hereafter: EPM), and examines citizens' responses to communications of EPM regarding two of its current policy plans.
-The first policy regards *reducing the air pollution in the Haifa-Bay area*, located in the north of Israel.
+In this paper, the above-mentioned hypotheses are tested via a randomized survey experiment, building on the methodology of @petty_1983.
+Focusing on the case of the Israeli Environment Protection Ministry (hereafter: EPM), I examine citizens' responses to communications of EPM regarding two of its current policy plans.
+The first policy regards *reducing the the air pollution in the highly polluted Haifa-Bay area*, located in the north of Israel.
 This policy issue offers a fortunate case for examining the moderating role of perceived personal relevance.
-The differences between those who reside in the polluted area and those who do not represent natural variation in this factor.
-Moreover, because this policy issue is intangible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as it is the case in many other policy issues [@petty_1983].
-Congruently, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize a communication about the air-pollution in their area of residence, yet are not more capable to do so than those who reside elsewhere.
-As explained below, the sample population of the study consists of residents of Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
+The distinction between those who reside in the polluted area and those who do not represents natural variation in personal relevance.
+Moreover, because this policy issue is intangible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as is the case in many other policy issues [@petty_1983].
+Congruently, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize a communication about the air-pollution in their area of residence, yet no more capable to do so than those who reside elsewhere.
+As explained below, the sample population of the study consists of residents of the Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
 The second policy plan regards *reducing domestic waste and increasing recycling*.
 This topic is assumed to be equally relevant for Haifa-bay residents and others.
-Therefore, adding this policy plan enables to further confirm that their different responses to the air-pollution policy, if found, are explained by differences in perceived personal relevance.
+Therefore, adding this policy plan is intended to confirm that respondents’ different responses to the air-pollution policy, if found, may be attributed to perceived personal relevance.
 I henceforth refer to these two policy plans as "air-pollution" and "recycling".
 
-I focused on three symbolic elements which have been used in the EPM's public communications, and became widely recognized by the public.
+I exploited three three symbolic elements which have been used in the EPM's public communications, and became widely recognized by the public.
 The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
 The second element is the green color, which is strongly associated with taking care of the environment.
-The third element is the images of two high-profile celebrity comedians which were taken from advertising campaigns of the EPM.
+The third element are the images of two high-profile celebrity comedians which were taken from advertising campaigns of the EPM.
 Further details about these symbolic elements are found in the supplementary appendix.
@@
 The survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general.
-After a set of pre-manipulation questions, they subjects were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance).
+After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance).
 Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
@@
 The latter open question was specifically designed to prime Haifa-bay residents to think about the personal relevance of the air pollution in their area.
-Subjects in the relevance control group were asked equivalent questions about their field of occupation.
+Subjects in the relevance control group were asked equivalent questions about their field of occupation .
 
-Participants were then presented with the two policy plans of EPM, which they were told that were obtained from EPM's annual work plan.
+Participants were then presented with the two policy plans of EPM, and informed that these were obtained from EPM's annual work plan.
 Each policy plan was followed by questions about respondents' trust in them.
@@
 logically unpersuasive).
-The information in the strong policy plans condition was taken from the real work plan and from other official sources, whereas the information in the weak policy plans was fictional, and was deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.
+Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order.
+The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.
 The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
-Each subject, moreover, was exposed to one strong and one weak policy communication, displayed in a random order.
 
 The participants were also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
-In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the EPM logo, green color and celebrity images from campaigns.
-In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
+In the symbol treatment condition, the two policies (as explained, one weak and one strong) are displayed with the EPM logo, green color and celebrity images from campaigns.
+In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images.
 In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with images of unfamiliar people.
@@
 
-My outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively).
+The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively).
 This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-Participants reported lower trust, on average, in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
+Participants reported, on average, lower trust, on average, in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
 
-My key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.[^footnote_symbols_manipulation_check] The perceived personal relevance of the communication is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
-I coded living in Haifa-bay area according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
+The key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.[^footnote_symbols_manipulation_check] The perceived personal relevance of the communication is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
+I coded living in Haifa-bay area according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities.
 My data confirmes that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
-Moreover, when directly asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects regarded to the air-pollution.
+Moreover, when directly asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects made reference to air-pollution.
 As for the relevance priming questions, however, manipulation checks suggest that those in the relevance treatment group did not perceive either of the two policies as more personally relevant.
 This limitation should be kept in mind when interpreting the results regarding this manipulation.
-The results of the all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
+The results of all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
 
@@
 Compared with the fake symbols, the increase is significant at the 90% (one-tailed) regarding the air-pollution policy, and only marginally significant compared with the recycling policy (*p* = `r (summary(mod_waste_1.1_r1)$coefficients["SYMBOL_t.r1",4]/2)%>%round(2)`, one-tailed).
-The information manipulation also has a significant main effect in both policy plans, as expected (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations, respectively).
-Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in the air-pollution policy, and also, to a lower degree, in the recycling policy.
-The latter effects suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, and to some extent towards EPM or environmental policy in general.
+The weak (versus strong) information manipulation also has a significant main effect in both policy plans, as expected (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations, respectively).
+Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in both the air-pollution policy, and, to a lower degree, the recycling policy.
+The latter effect suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, which to some extent extends towards EPM or environmental policy in general.
 
 Keeping in mind these main effects, I now turn to analyze the interactions between the manipulations and the areas.
-With regard to the air-pollution policy, my first hypotheses entails a positive interaction between residence in the center (i.e.
+With regard to the air-pollution policy, my first hypothesis entails a positive coefficient to the interaction between residence in the center (i.e.
 low personal relevance) and the real symbols.
@@
 Counter to these expectations, in Model 1.3, the interaction between residence in the center and the real symbols is negative (*p*<.1), and the interaction with the weak information is insignificant.
-These findings suggest that the real symbols were more effective in increasing the trust of those reside in the polluted area and that the latter were not more likely to scrutinize the content of the communication.
+These findings suggest that the real symbols were more effective in increasing the trust of those reside in the polluted area and that the latter were no more likely to scrutinize the content of the communication.
 I also found similar patterns regarding the recycling policy.
@@
 I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
-*First*, in addition to the above operationalizations of personal relevance, I also relied on subjects' subjective reporting.
-*Second*, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey: the time participants spent on scanning the policy plans and their score in a memory test.
-I also tested whether personal relevance decreased the delta (within-subjects) between trust in strong and weak policy plans presented to each subject.
+*First*, I also relied on subjects' subjective reporting of the personal relevnace of the policy plans, in addition to the above operationalizations.
+*Second*, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey, which were again insignificant: the time participants spent on scanning the policy plans and their score in a memory test.
+I also tested whether personal relevance decreased the delta (within-subjects) between trust in the strong and weak policy plans presented to each subject.
 *Third*, I added a set of individual-level controls, and factors related to personal relevance of air-pollution, and to personal interest in environmental issues.
 Finally, I replicated my analyses on the unfiltered sample.
-None of these multiple robust analyses supports my theoretical hypotheses.
+None of these multiple robust analyses supports the theoretical hypotheses regarding the moderating effect of personal relevance.
 
@@
 I explored the postulation, derived from social psychology, that citizens are less susceptible to symbols and more likely to scrutinize the substantive information in the communication the more they perceive it as personally relevant.
-I put this theory to rigorous empirical test, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
-I further focused on its policy plan regarding air pollution in a specific area, to capture natural variation in citizens' perceptions of the personal relevance.
-In addition to utilizing these natural differences, I also used manipulated the personal relevance of the policy plans.
+I put this theory to rigorous empirical testing, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
+I exploited the natural variation in citizens' perceptions of the personal relevance of the ministry’s policy plan regarding air pollution in a specific area.
+In addition to utilizing these natural differences, I also manipulated the personal relevance of the policy plans.
 To the best of my knowledge, this is the first study to assess the moderating role of perceived personal relevance on citizens' responses to government symbolic communications.
 
-Whilst the effect of perceived personal relevance on message processing has been substantiated by experiment-based studies in social psychology and marketing, I did not find support for this hypothesis the context of citizens' responses to government communications in this study.
+Whilst the effect of perceived personal relevance on message processing has been substantiated by experiment-based studies in social psychology and marketing, I did not find support for this hypothesis in the context of citizens' responses to government communications in this study.
 Subjects residing in the polluted Haifa-Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center.
-However, despite these differences, Haifa-bay subjects did not pay more attention to the logical quality of the policy plan, and they were affected by the symbols in the communication not less than those from the center.
+However, despite these differences, Haifa-bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication.
 If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
-Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also did not moderate the effects of the symbols and information in the communications.
+Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also failed to moderate the effects of the symbols and information in the communications.
+These findings are also consistent with the findings of @alonbarkat_2017, where they found that citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) were nonetheless significantly affected by a symbol of the government-owned electricity company.
 
@@
 as in the case of Haifa-Bay subjects), than shifting them from medium to high levels (i.e.
-as in the case of center subjects), which results in a ceiling effect.
-Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.[^footnote_ceiling_effect] Another related explanation is that the symbols distracted the subjects and decreased their inclination to think about this topic.
-As a result, they caused Haifa-bay subjects to disregard their prior beliefs about EPM and its actions regarding the air-pollution.[^footnote_mediation_elaboration]:
+as in the case of center subjects), indicating a ceiling effect.
+Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.[^footnote_ceiling_effect] A related explanation is that the symbols distracted the subjects and decreased their inclination to think about the topic.
+As a result, they caused Haifa-bay subjects to disregard their prior beliefs about EPM and its failure regarding air-pollution.[^footnote_mediation_elaboration]:
 
@@
 The decrease in elaboration mediates the effect of symbols on trust.
-These analyses are presented in the supplentary appendix.
 
@@
 206].
-The findings in this study are also consistent with the findings of @alonbarkat_2017, where they found that citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) were nonetheless significantly affected by a symbol of the government-owned electricity company.
 
@@
 They challenge the optimistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
-Instead, they suggest that more often than not, citizens rely on symbols and other peripheral cues in public communications, including when these communications concern issues that have direct implications on thrir own lives.
+Instead, they suggest that more often than not, citizens rely on symbols and other peripheral cues in public communications, even when these communications concern issues that have direct implications on their own lives.
 This inclination is in tension with the assumption that citizens should form their opinions about their government and about public affairs, based on their rational thinking [@dahl_1973; @soroka_2010].
@@
 A comparison between two groups that have similar prior beliefs would be more reliable.
-Finally, one can question the validity of relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications.
+Finally, one can question the validity of the relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications.
 Still, the main results are robust to different model specifications, and operationalizations of personal relevance and message elaboration, which substantiate their validity.

### 2018-07-11 paper3_APPENDIX.Rmd
Add files via upload

@@
 #2. Manipulation and validity checks
+
+In this section, I report the results of manipulation checks for the symbols and relevance manipulations.
+In addition, I report the results of additional analyses regarding the empirical assumptions underlying the comparison between the two areas.
+These analyses are based on the survey data, and on two prior surveys, as described below.
+
+## Symbols manipulation
+
+In two prior surveys, I confirmed that the real EPM symbols are recognizable and have a positive affect, whereas the fake logo is unrecognizable, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
+
+The first prior survey was conducted on May 2017 among `r SVIVA1_01 %>% nrow()` participants, which were recruited by iPanel.
+This survey was designed as a survey experiment, which was a first attempt to test the moderating role of personal relevance on the effects of symbols and information.
+However, after analyzing the results, I came to the conclusion that the experimental procedure had several methodological problems.
+Mainly, the assignment to experimental conditions yielded imbalanced groups, and the manipulations of symbolic elements and information ware too subtle.
+In addition, perceived personal relevance was measured only through the comparison between the areas (i.e.
+without the relevance manipulation), and the information was manipulated only with regard to the air-pollution policy.
+Despite these weaknesses, the survey included specific questions about the affect and symbolic associations of the logos and the colors, which provide valuable descriptive data.[^footnote_prior_survey_1] In this survey, the participants were assigned to one of three conditions of symbols: real symbols, fake symbols and no symbols.
+The real and fake symbols conditions included the same logos and colors which were eventually used in the final experiment (but not the campaign images).
+At the end of the survey, participants were asked about their familiarity with the logos and colors that appeared in their policy plans, and their affect.
+These items and their descriptive results are presented below.
+
+[^footnote_prior_survey_1]: Overall, the findings of this limited prior study are consistent Consistent with the findings of the main experiment, reported in the paper.
+The effect of the real symbols were greater among those who reside in the Haifa-Bay.
+Congruently, the statistical analyses yielded a negative and significant interaction between the real symbols and residence in the center.
+Also consistent with the main experiment, the interaction between the areas and the information manipulation was not significant.
+
+"How familiar are you with the symbol [that appeared in the policy plans]?" (1=not at all; 7=very much)
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+set_theme("scatterw")
+
+sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
+        geom.size = 0.9,
+        ylim=c(0,155),
+        axis.title="",
+        title = "Real logo")
+
+sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
+        geom.size = 0.9,
+        ylim=c(0,155),
+        axis.title="",
+        title = "Fake logo")
+
+```
+
+"When you see the symbol [that appeared in the policy plans], what does it make you feel?" (1=very negative feeling; 7=very positive feeling)
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+set_theme("scatterw")
+
+sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,160),
+        axis.title="",
+        title = "Real logo")
+
+sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,160),
+        axis.title="",
+       title = "Fake logo")
+
+```
+
+Overall, these results show that the real logo is relatively recognizable and has a fairly positive affect, whereas the fake logo is unrecognized and neutral.
+Participants were also asked "What is the first thought / association that comes to mind when you see the symbol?"  With regard to the real logo, many of the participants filled associations related to carting for the environment.
+Representative examples for such answers are: "environmental protection", "a desire to protect nature and the environment", "green policy", "together for the sake of nature", "connection between nature and man".
+The participants were similarly asked about the first thought / association that comes to their mind when they see the color.
+Representative answers for the green color were: "nature", "a green and healthy environment", "environment protection".
+The responses for the fake logo and the blue color were more diverse, and mostly unrelated to environmental issues.
+
+The second prior survey was conducted on January 2018 among `r CELEBS_00%>%nrow()` participants, which were similarly recruited via iPanel.
+This survey was designed as a pre-test that was aimed at assessing the recognizability, affect and associations of the real vs.
+fake campaign images.
+Participants were presented with the four campaign images (two real and two fake), in a random order.
+After every image, they were asked a series of questions regarding the familiarity and affect of the image and of the person presented.
+The items and their descriptive results are presented below.
+
+"The person presented in the image is familiar to me" (1=weakly agree; 7=strongly agree)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real celeb (Tal Friedman)")
+
+sjp.frq(CELEBS_00$air_fake_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Unfamiliar model")
+
+```
+
+Recycling policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real celeb (Ido Rosenblum)")
+
+sjp.frq(CELEBS_00$waste_fake_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        xlim=c(0,110),
+        axis.title="",
+        title = "Unfamiliar model")
+
+```
+
+"The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?" (1=not at all; 7=very much)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real campaign (starting to think green)")
+
+sjp.frq(CELEBS_00$air_fake_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+Recycling policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real campaign (reusable bags)")
+
+sjp.frq(CELEBS_00$waste_fake_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+"The image evokes a positive feeling" (1=weakly agree; 7=strongly agree)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_positive_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Real campaign (starting to think green)")
+
+sjp.frq(CELEBS_00$air_fake_positive_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+Recycling policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_positive_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Real campaign (reusable bags)")
+
+sjp.frq(CELEBS_00$waste_fake_positive_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+"The image evokes a negative feeling" (1=weakly agree; 7=strongly agree)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_negative_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,80),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Real campaign (starting to think green)")
+
+sjp.frq(CELEBS_00$air_fake_negative_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,80),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+Recycling policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_negative_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,80),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Real campaign (reusable bags)")
+
+sjp.frq(CELEBS_00$waste_fake_negative_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,80),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative of positive feelings.
+Finally, I similarly asked subjects to describe their first thoughts/associations regarding the images of Friedman and Rosenblum from their campaigns (without any text).
+Most of the participants associated Rosenblum's image to the reducing the use of disposable grocery bags, in line with the campaign's message (e.g.
+"reusable bag", "reusable instead of disposable bag for protecting the environment").
+With regard to Friedman's grass-head image from his "starting to think green" campaign, participants mostly mentioned associations related to environmental awareness (e.g.
+"green head, thinking about the environment", "green environment", "think green"), and to the humoristic aspect (e.g.
+"funny", "comedian", "Funny advertisement", "hahaha").
+
+<br>
+
+## Areas: Haifa-Bay vs. Center
+
+To confirm the assumption that the Air-pollution policy is perceived as more personally relevant by Haifa-Bay subjects, whereas the recycling policy is perceived as equally relevant by both groups, I relied on the following question, which was included in the survey, regarding both policy plans:
+
+"To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
+
+The distribution of this variable for the two policies, across the two areas, is displayed in the following plots. These comparisons confirm the assumption.
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_air_obs,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,600),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Center")
+
+sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_air_obs,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,600),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Haifa-bay")
+
+```
+
+Recycling policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_waste_obs,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,600),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Center")
+
+sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_waste_obs,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,600),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Haifa-bay")
+
+```
+
+I also examined the assumption that Haifa-bay subjects do not have greater knowledge on the air-pollution in their area issue, compared with the participants who reside in the Center.
+To test that assumption I relied on three incdicators.
+First, I assessed participants prior knowledge about the causes of the phenomenon.
+Participants were given a list of causes and were asked to rank them based on their contribution to air-pollution.
+There were no significant differences between the two samples for this task.
+Additionally, I assessed participants knowledge of the effectiveness of the Ministry’s previous policy by asking participants whether air-pollution has increased, decreased, or remained the same during the past years.
+Haifa-bay residents were only slightly more likley to indicate correctly that it had decreased according to EPM reports (`r filter(SVIVA1_01,AREA==1)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`% compared with `r filter(SVIVA1_01,AREA==0)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`%).
+Still, even among Haifa-bay subjects, the vast majority of subjects were incorrect.
+
+<br>
+
+## Relevance manipulation
+
+I tested whether the priming questions in the relevance treatment condition increased the perceived personal relevance of the two policy plans.
+For this purpose, I relied on the following question, which was included in the survey, regarding both policy plans:
+
+"To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
+
+I analyze the effect of the relevance manipulation, across the two areas, on this variable, via OLS regression.
+Table AX shows the results of these regression analyses.
+For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafer I add their interaction.
+Counter to my expectations, the relevance manipulation did not have a positive main effect on either of these two policy plans.
+In Model 2, the interaction between the relevance treatment and the center area is positive and significant and the coefficient of the relevance treatment is negative and significant.
+The interpretation of this interaction model suggests that the priming questions had a negative effect on Haifa-Bay subjects, and a positive effect on those who reside in the Center.
+Regarding the recycling policy, the interaction is insignificant in Model 4.
+
+**Table AX: Regression table - effect of relevance manipulation, across areas, on perceived personal relevance**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_relevance_air_1.1_apx = lm(RELEVANCE_air_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
+mod_relevance_air_1.2_apx = update(mod_relevance_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
+
+mod_relevance_waste_1.1_apx = lm(RELEVANCE_waste_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
+mod_relevance_waste_1.2_apx = update(mod_relevance_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
+
+stargazer(mod_relevance_air_1.1_apx,mod_relevance_air_1.2_apx,
+          mod_relevance_waste_1.1_apx,mod_relevance_waste_1.2_apx,
+          type="html",style = "apsr",
+          dep.var.labels=c("Air-pollution","Recycling"),
+          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
+                             "Relevance treatment",
+                             "Area x Relevance treatment"),
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+```
+
+<br>
+
 <br>

### 2018-07-13 paper3_APPENDIX.Rmd
Add files via upload

@@
 mutate(AREA_center = Recode(AREA,"0=1;1=0"))
+
+SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
+SVIVA2_01_center = filter(SVIVA2_01,AREA==0)
 
@@
 
-In this section, I report the results of manipulation checks for the symbols and relevance manipulations.
-In addition, I report the results of additional analyses regarding the empirical assumptions underlying the comparison between the two areas.
+In this section, I report the results of the manipulation checks for the symbols and relevance manipulations, and analyses regarding the validity of the comparison between the two areas.
 These analyses are based on the survey data, and on two prior surveys, as described below.
@@
 
-## Areas: Haifa-Bay vs. Center
-
-To confirm the assumption that the Air-pollution policy is perceived as more personally relevant by Haifa-Bay subjects, whereas the recycling policy is perceived as equally relevant by both groups, I relied on the following question, which was included in the survey, regarding both policy plans:
+## Comparison between Haifa-Bay and Center
+
+The comparison between the two areas is based on the assumption that the Air-pollution policy is perceived as more personally relevant by Haifa-Bay subjects, whereas the recycling policy is perceived as equally relevant by both groups.
+To test that assumption, I relied on the following question, which was included in the survey, regarding both policy plans:
 
@@
 
-The distribution of this variable for the two policies, across the two areas, is displayed in the following plots. These comparisons confirm the assumption.
+The air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents.
+As for the recycling policy, it is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them.
+The distribution of the perceived personal relevance variable of the two policies, across the two areas, is displayed in the following figures.
 
@@
 
-I also examined the assumption that Haifa-bay subjects do not have greater knowledge on the air-pollution in their area issue, compared with the participants who reside in the Center.
-To test that assumption I relied on three incdicators.
-First, I assessed participants prior knowledge about the causes of the phenomenon.
-Participants were given a list of causes and were asked to rank them based on their contribution to air-pollution.
-There were no significant differences between the two samples for this task.
-Additionally, I assessed participants knowledge of the effectiveness of the Ministry’s previous policy by asking participants whether air-pollution has increased, decreased, or remained the same during the past years.
-Haifa-bay residents were only slightly more likley to indicate correctly that it had decreased according to EPM reports (`r filter(SVIVA1_01,AREA==1)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`% compared with `r filter(SVIVA1_01,AREA==0)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`%).
-Still, even among Haifa-bay subjects, the vast majority of subjects were incorrect.
-
+Moreover, Participants in the relevance treatment group were asked to describe the most salient environmental issue in their particular area of residence.
+Indeed, most of the Haifa-Bay subjects regarded in their responses to the air-pollution generated from the industrial area, and many of them linked it to higher morbidity rates in the area.
+Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, whereas relatively few of them mentioned air-pollution as a prominent environmental concern in their area.
+
+In the first prior survey, I also tested the empirical assumption that Haifa-bay subjects do not have greater knowledge on the air-pollution in their area issue, compared with the participants who reside in the Center.
+*First*, I assessed participants prior knowledge about the causes of the air-pollution in that area.
+Participants were given a list of three causes, and were asked to rank them based on their contribution to air-pollution.[^footnote_air-pollution_causes] There were no significant differences between the two areas regarding the performance in this task.
+*Second*, I examined participants knowledge of the effectiveness of the previous EPM policy by asking participants whether air-pollution during the past years has decreased (the correct answer), increased, or remained the same, according to EPM reports.
+In both groups, the vast majority of subjects were incorrect.
+Haifa-bay residents were only slightly more likely to state that it had decreased (`r filter(SVIVA1_01,AREA==1)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`% compared with `r filter(SVIVA1_01,AREA==0)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`%).
+*Third*, subjects were asked about the frequency in which they monitor the air quality (in their area of residence).
+Haifa-bay subjects reported that they tend to monitor air pollution more frequently.
+Congruently, 48.9% of them reported that they tend to monitor it occasionally ("from time to time", but less than once a week), compared with only 28.2% of Center subjects.
+34.6% of Center subjects reported that they do not monitor air pollution at all, compared with only 18.7% of Center subjects.
+Still, in both areas, only 2-3% of subjects reported that they monitor air pollution once a week or more frequently.
+Taken together, these comparisons indicate that in both areas, most people tend to have relatively little prior knowledge of the air-pollution.
+At the same time, some Haifa-bay subjects do have greater knowledge about it.
+This might suggest that on average, Haifa-bay subjects not only have greater motivation to scrutinize the communication on the policy, but also slightly greater ability to do so.
+
+[^footnote_air-pollution_causes]: The three causes are: emissions of pollutants from the factories and refineries in the area; emissions of diesel smoke from vehicles in the area; emissions of pollutants from unauthorized coal production sites.
 <br>
@@
 
-I tested whether the priming questions in the relevance treatment condition increased the perceived personal relevance of the two policy plans.
-For this purpose, I relied on the following question, which was included in the survey, regarding both policy plans:
-
-"To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
-
-I analyze the effect of the relevance manipulation, across the two areas, on this variable, via OLS regression.
-Table AX shows the results of these regression analyses.
-For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafer I add their interaction.
+I tested whether the priming questions in the relevance treatment condition increased the perceived personal relevance of the two policy plans (in each of the two areas).
+For this purpose, I relied on the above perceived personal relevance items.
+Table A1 shows the results of regression analyses.
+For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafter I add their interaction.
 Counter to my expectations, the relevance manipulation did not have a positive main effect on either of these two policy plans.
-In Model 2, the interaction between the relevance treatment and the center area is positive and significant and the coefficient of the relevance treatment is negative and significant.
-The interpretation of this interaction model suggests that the priming questions had a negative effect on Haifa-Bay subjects, and a positive effect on those who reside in the Center.
-Regarding the recycling policy, the interaction is insignificant in Model 4.
-
-**Table AX: Regression table - effect of relevance manipulation, across areas, on perceived personal relevance**
+Regarding the air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative (model 2).
+The interpretation of this interaction suggests that the priming questions decreased the perceived personal relevance of the air-pollution policy among Haifa-Bay subjects, but increased it among those who reside in the Center.
+Regarding the recycling policy, the interaction is insignificant.
+
+**Table A1: Regression table - effect of relevance manipulation, across areas, on perceived personal relevance**
 
@@
 
-<br>
-
 #3. Summary statistics
 
-**Table A1: summary statistics of research variables**
+**Table A2: summary statistics of research variables**
 
@@
 
-**Table A2: Correlation matrix**
+**Table A3: Correlation matrix**
 
@@
 In the tables below, I report the results of additional robust analyses testing the moderating role of the perceived personal relevance of the communications.
-In **Table A3** I analyze subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
-These analyses show that higher scores of perceived personal relevance did not attentuate the positive effect of the real symbols.
-However, in line with Hypothesis 2, it did slightly increase the effect of the weak information with regard to the air-pollution policy.
-
-In **Tables A4 - A6**, I examine the effects of relevance treatment and the differences between the areas on subjects elaboration of the two policy plans, using three additional measures.
+In **Table A4** I analyze subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
+These analyses show that higher scores of perceived personal relevance did not attenuate the positive effect of the real symbols.
+However, it did slightly increase the effect of the weak information with regard to the air-pollution policy, consistent with Hypothesis 2.
+
+In **Tables A5 - A7**, I examine the effects of relevance treatment and the differences between the areas on subjects elaboration of the two policy plans, using three additional measures.
 The first measure is the number of seconds participants spent on scanning the policy plans, log transformed (hereafter: reaction time).
@@
 
-In **Tables A7 and A8**, I replicate the main analyses while adding additional control variables.
+In **Tables A8 and A9**, I replicate the main analyses while adding additional control variables.
 In Tables A7, I control for demographics and additional individual-level covariates, including ideology and trust in government ministries in general.
 In Table A8 I further control for factors that can be related to participants' motivation to elaborate, including having young children, general interest in environmental issues and following environmental issues in the media.
-The two final variables are based on survey items which were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (n = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).Finally, in **Table A9**, I add those subjects who were filttered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
+The two final variables are based on survey items which were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (n = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).Finally, in **Table A10**, I add those subjects who were filtered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
 In all these analyses, the effects of the symbols and information manipulations and their interaction with the areas and the relevance manipulation are consistent with the main models.
@@
 
-**Table A3: Regression table - subjective reporting of perceived personal relevance**
+**Table A4: Regression table - subjective reporting of perceived personal relevance**
 
@@
 
-**Table A4: Regression table - effect of personal relevance on reaction time**
+**Table A5: Regression table - effect of personal relevance on reaction time**
 
@@
 
-**Table A5: Regression table - effect of personal relevance on memory score**
+**Table A6: Regression table - effect of personal relevance on memory score**
 
@@
 
-**Table A6: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**
+**Table A7: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**
 
@@
 
-**Table A7: Regression table - adding control variables**
+**Table A8: Regression table - adding control variables**
 
@@
 
-**Table A8: Regression table - adding personal relevance and motivational control variables**
+**Table A9: Regression table - adding personal relevance and motivational control variables**
 
@@
 
-**Table A9: Regression table - unfiltered sample**
+**Table A10: Regression table - unfiltered sample**
 
@@
 Below is the full text of the survey.
-Additional comments are presented in square beackets.
+Additional comments are presented in square brackets.
 The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here.
@@
 
-[For subjets assigned to the no symbols]:
+[For subjects assigned to the no symbols]:
 

### 2018-07-13 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 
-*Recent experimental studies have demonstrated that government public communications can enhance citizens' trust in government organizations and their policies not only by conveying substantive information, but also by incorporating strategically designed symbolic element that evoke positive feelings and associations.
-Yet, under what conditions are citizens more/less likely to be persuaded by symbols?
-Building on the social psychology Elaboration Likelihood Model (ELM), I theorize that citizens are less susceptible to symbols and more likely to scrutinize the substantive content of the communication, the more they perceive the policy issue in the communication as personally relevant.
-I test this theory through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted geographical area.
+*Recent studies have demonstrated that symbolic elements in government public communications can enhance citizens' trust in government organizations and their policies.
+Moreover, the emotive effect of these symbols can compensate for organizations' poor performane and inefficient policies, and distort public opinion.
+This study explores the boundaries of governments' persuasion of citizens through symbolic communication.
+Building on social psychology literature, I hypothesize that citizens are less susceptible to symbols and more likely to scrutinize the substantive content of the communication, the more they perceive the policy issue in the communication as personally relevant.
+I test this expectation through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted geographical area.
 The perceived personal relevance of the policy is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere.
-Counter to the well-grounded theoretical expectations hypotheses, these comparisons suggest that higher perceived personal relevance does not attentuate the effect of symbols.
-The theoretical and norative implications of these findings are discussed.*
+The results indicate that even high levels of perceived personal relevance do not attentuate the positive effect of symbols.
+This may suggest that the boundaries of the effect of symbolic communication are wider than expected, which carries serious implications.*
 
@@
 This research gap has great significance.
-First, from the practical point of view of government organizations, understanding the boundries of the effects of symbols may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
+First, from the practical point of view of government organizations, understanding the boundaries of the effects of symbols may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
 Second, employing a broader perspective of democratic theory, one can argue that in the public-sector domain the emotive effect of symbols undermines the fundamental normative expectation that citizens' judgments of government should be based on their critical judgment.
@@
 [^footnote_filters]: I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
-These filters are niether associated with the areas nor with the experimental conditions.
+These filters are neither associated with the areas nor with the experimental conditions.
 
@@
 I coded living in Haifa-bay area according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities.
-My data confirmes that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
+My data confirms that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
 Moreover, when directly asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects made reference to air-pollution.
@@
 I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
-*First*, I also relied on subjects' subjective reporting of the personal relevnace of the policy plans, in addition to the above operationalizations.
+*First*, I also relied on subjects' subjective reporting of the personal relevance of the policy plans, in addition to the above operationalizations.
 *Second*, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey, which were again insignificant: the time participants spent on scanning the policy plans and their score in a memory test.

### 2018-07-15 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 ---
-title: "The persuasion of symbolic elements in government public communications, and their moderation by the personal relevance of the communication"
+title: "The persuasion of symbolic elements in government public communications, and their moderation by personal relevance"
 author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
@@
       toc_depth: 3
+  pdf_document:
+    toc: yes
+  word_document: default
 link-citations: yes
 bibliography: phd_paper_2.bib
+#csl: apsa.csl
 urlcolor: blue
@@
 *Recent studies have demonstrated that symbolic elements in government public communications can enhance citizens' trust in government organizations and their policies.
-Moreover, the emotive effect of these symbols can compensate for organizations' poor performane and inefficient policies, and distort public opinion.
+They also suggested that the emotive effect of these symbols can compensate for organizations' poor performance and inefficient policies, thereby eliciting undue trust.
 This study explores the boundaries of governments' persuasion of citizens through symbolic communication.
 Building on social psychology literature, I hypothesize that citizens are less susceptible to symbols and more likely to scrutinize the substantive content of the communication, the more they perceive the policy issue in the communication as personally relevant.
-I test this expectation through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted geographical area.
+I test this expectation through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted area.
 The perceived personal relevance of the policy is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere.
-The results indicate that even high levels of perceived personal relevance do not attentuate the positive effect of symbols.
-This may suggest that the boundaries of the effect of symbolic communication are wider than expected, which carries serious implications.*
+The results indicate that even high levels of perceived personal relevance do not attenuate the positive effect of symbols.
+These findings may suggest that the boundaries of the effect of symbolic communication are wider than expected, which carries significant implications.*
 
@@
 A growing public administration literature explores whether government public communications can enhance citizens' trust in public organizations and policies.
-Whereas most of the studies have focused on the *informative* aspects of government communications [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @grimmelikhuijsen_2015; @ho_2017], recent experimental studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as  brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
+Whereas most of the priovious studies have focused on the *informative* aspects of government communications [e.g.
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011], recent studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
 Such symbols and others exist in almost every government communication, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
 
-While previous studies have substantiated the distinct effect of symbols on citizens' trust, they did not theorize, nor empirically examine, the conditions under which these symbols are likely to be more, or less, effective.
-This research gap has great significance.
-First, from the practical point of view of government organizations, understanding the boundaries of the effects of symbols may enable them to design more effective communications which may enhance citizens' collaboration with their policies.
-Second, employing a broader perspective of democratic theory, one can argue that in the public-sector domain the emotive effect of symbols undermines the fundamental normative expectation that citizens' judgments of government should be based on their critical judgment.
-Furthermore, the positive symbolic message can compensate for poor performance and create a misalignment between citizens' perceptions and the "real world" [@alonbarkat_2017].
-Hence, by identifying the circumstances under which citizens are more/less likely to be affected by symbols, we could better assess the potential risk for governments' manipulative use of public communications.
+Persuasion through symbolic communications and branding can be perceived favorably, insofar as it enables governments to engage more effectively with relevant publics, thereby to increase their trust and enhance their collaboration.
+The effectiveness of symbols, as opposed to communication of "objective" information, stems from their potency to overcome citizens' negative biases.
+On the other hand, employing a broader perspective of democratic theory, one can argue that in the public-sector domain, the emotive effect of symbols undermines the fundamental normative expectation that citizens' judgments of government should be based on their critical judgment.
+Furthermore, as previous studies demonstrated, positive symbolic messages can compensate for poor performance and create a misalignment between citizens' positive perceptions and the "real world" [@alonbarkat_2017; @alonbarkat_2018].
+Accordingly, symbols can mitigate justified public criticism of government failures.
 
-To address this gap, I draw upon the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
-I hypothesize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
-Similarly, higher perceived personal relevance is expected to enhance citizens' inclination to scrutinize the substantive content of communication.
-Employing a survey experiment, I test this hypothesis in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay).
+In this study I explore the boundaries of governments' persuasion of citizens through symbolic communication.
+Namely, I seek to explore the conditions under which symbolic elements are likely to be more, or less, effective in shaping (and possibly manipulating) citizens' trust.
+Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I hypothesize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
+Similarly, high perceived personal relevance is expected to enhance citizens' inclination to scrutinize the substantive content of communication.
+
+Employing a survey experiment, I test these hypotheses in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay).
 I operationalize the perceived personal relevance of the policy plan both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+contrary to my expectations, the results indicate that even high levels of perceived personal relevance do not attenuate the effect of symbols on citizens' trust.
+These findings may suggest that the boundaries of the effect of symbolic communication are wider than expected.
+I discuss the theoretical and normative implications of these findings.
 
@@
 
-# The Elaboration Likelihood Model (ELM) and the effect of symbols and information in communications.
+# The persuasion of symbols and information in government public communications.
 

### 2018-07-15 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 The effectiveness of symbols, as opposed to communication of "objective" information, stems from their potency to overcome citizens' negative biases.
-On the other hand, employing a broader perspective of democratic theory, one can argue that in the public-sector domain, the emotive effect of symbols undermines the fundamental normative expectation that citizens' judgments of government should be based on their critical judgment.
-Furthermore, as previous studies demonstrated, positive symbolic messages can compensate for poor performance and create a misalignment between citizens' positive perceptions and the "real world" [@alonbarkat_2017; @alonbarkat_2018].
-Accordingly, symbols can mitigate justified public criticism of government failures.
+On the other hand, employing a broader perspective of democratic theory, one can argue that in the public-sector domain, the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment.
+Furthermore, previous studies have demonstrated that the positive effect of symbols can compensate for organizations' poor performance (@alonbarkat_2017) and for logically unpersuasive informative content (@alonbarkat_2018).
+Accordingly, symbolic communication can create a misalignment between citizens' positive perceptions and the "real world", and mitigate justified public criticism of government failures.
 
-In this study I explore the boundaries of governments' persuasion of citizens through symbolic communication.
+In this study, I explore the boundaries of governments' persuasion of citizens through symbolic communication, to assess the above concern.
 Namely, I seek to explore the conditions under which symbolic elements are likely to be more, or less, effective in shaping (and possibly manipulating) citizens' trust.
-Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I hypothesize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
+Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I theorize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
 Similarly, high perceived personal relevance is expected to enhance citizens' inclination to scrutinize the substantive content of communication.
-
 Employing a survey experiment, I test these hypotheses in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay).
 I operationalize the perceived personal relevance of the policy plan both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
-contrary to my expectations, the results indicate that even high levels of perceived personal relevance do not attenuate the effect of symbols on citizens' trust.
+The results indicate that even high levels of perceived personal relevance do not attenuate the effect of symbols on citizens' trust, contrary to my expectations.
 These findings may suggest that the boundaries of the effect of symbolic communication are wider than expected.
@@
 
-The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a theoretical framework for investigating the effects of "persuasive" communications on people's attitudes [@petty_1986; @petty_2011].
+The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a theoretical framework for investigating the effects of communications on people's attitudes [@petty_1986; @petty_2011].
 According to ELM, people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
@@
 
-Viewed against the above theoretical framework of ELM, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
+Viewed against the above theoretical framework, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
 Conversely, symbolic elements can be regarded as potential peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
@@
 
-In this paper, the above-mentioned hypotheses are tested via a randomized survey experiment, building on the methodology of @petty_1983.
+In this paper, the above-mentioned theoretical expectations are tested via a randomized survey experiment, building on the methodology of @petty_1983.
 Focusing on the case of the Israeli Environment Protection Ministry (hereafter: EPM), I examine citizens' responses to communications of EPM regarding two of its current policy plans.
@@
 
+Public communications has been proposed as a remedy for citizens’ low trust in government, and their underestimation of public-service performance.
+Congruently, governments' investments in public communications, and specifically in branding and advertising, has increased over the past generation in many economically-developed democratic countries.
 This study contributes to the growing public administration research on citizens' responses to government public communications, and specifically to symbolic elements entangled in these communications.
-I explored the postulation, derived from social psychology, that citizens are less susceptible to symbols and more likely to scrutinize the substantive information in the communication the more they perceive it as personally relevant.
-I put this theory to rigorous empirical testing, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
+I explored the expectation, derived from social psychology, that citizens are less affected by symbols and more likely to scrutinize the content of the communication the more they perceive it as relevant to their own lives.
+I put these hypotheses to rigorous empirical testing, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
 I exploited the natural variation in citizens' perceptions of the personal relevance of the ministry’s policy plan regarding air pollution in a specific area.
 In addition to utilizing these natural differences, I also manipulated the personal relevance of the policy plans.
-To the best of my knowledge, this is the first study to assess the moderating role of perceived personal relevance on citizens' responses to government symbolic communications.
+To the best of my knowledge, this is the first study to assess the moderating role of perceived personal relevance on citizens' responses to government symbolic communications or branding.
 
-Whilst the effect of perceived personal relevance on message processing has been substantiated by experiment-based studies in social psychology and marketing, I did not find support for this hypothesis in the context of citizens' responses to government communications in this study.
+Contrary to my expectations, and those of extant research in social psychology and marketing, I did not find that high levels of perceived personal relevance attenuate the effect of symbols on citizens' trust.
 Subjects residing in the polluted Haifa-Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center.
-However, despite these differences, Haifa-bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication.
+However, despite these significant differences, Haifa-bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication.
 If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
@@
 
+The results of this study, if generalizable, have significant implications.
+They challenge the optimistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
+Instead, they highlight the significant role played by superficial symbols in public communications in shaping citizens view of governments, as suggested by recent scholars of government branding.
+I demonstrate that citizens can be persuaded by government branding and symbolic communication even with regard to policy issues that have direct implications on their own lives.
+These conclusions buttress the concern that government organizations will strategically use symbolic communications to manipulate public opinion, and cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
 How can we explain the finding that the positive effect of the real symbols was stronger among Haifa-Bay residents?
@@
 206].
-
-The results of this study, if generalizable, have significant normative implications.
-They challenge the optimistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
-Instead, they suggest that more often than not, citizens rely on symbols and other peripheral cues in public communications, even when these communications concern issues that have direct implications on their own lives.
-This inclination is in tension with the assumption that citizens should form their opinions about their government and about public affairs, based on their rational thinking [@dahl_1973; @soroka_2010].
-It also buttresses the concern that government organizations will strategically use symbolic communications to manipulate public opinion, and cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
 

### 2018-07-15 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011], recent studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
-Such symbols and others exist in almost every government communication, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
+Such symbols and others exist in almost every government communication, and most prominently in public campaigns and branding activities, which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
 
@@
 On the other hand, employing a broader perspective of democratic theory, one can argue that in the public-sector domain, the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment.
-Furthermore, previous studies have demonstrated that the positive effect of symbols can compensate for organizations' poor performance (@alonbarkat_2017) and for logically unpersuasive informative content (@alonbarkat_2018).
-Accordingly, symbolic communication can create a misalignment between citizens' positive perceptions and the "real world", and mitigate justified public criticism of government failures.
+Furthermore, previous studies have demonstrated that the positive effect of symbols can compensate for organizations' poor performance [@alonbarkat_2017] and for logically unpersuasive informative content [@alonbarkat_2018].
+Accordingly, they can create a misalignment between citizens' positive perceptions and the "real world", and mitigate justified public criticism of government failures.
 
@@
 
-The results of this study, if generalizable, have significant implications.
-They challenge the optimistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
-Instead, they highlight the significant role played by superficial symbols in public communications in shaping citizens view of governments, as suggested by recent scholars of government branding.
-I demonstrate that citizens can be persuaded by government branding and symbolic communication even with regard to policy issues that have direct implications on their own lives.
-These conclusions buttress the concern that government organizations will strategically use symbolic communications to manipulate public opinion, and cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
 How can we explain the finding that the positive effect of the real symbols was stronger among Haifa-Bay residents?
@@
 206].
+
+The results of this study, if generalizable, have significant implications.
+They challenge the view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
+Instead, they suggest that more often than not, citizens rely on symbols and other peripheral cues in public communications, even when these communications concern issues that have direct implications on their own lives.
+Indeed, these findings highlight the role played by symbols in shaping citizens view of governments, in line with the recent literature on government branding.
+Moreover, they suggest that the boundaries of persuasion via symbols and branding are wider than expected, based on previous social psychology and marketing studies.
+These conclusions buttress the concern that government organizations will strategically use symbolic communications to manipulate public opinion, and cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
 

### 2018-07-16 paper3_relevance and symbols_01.Rmd
Add files via upload

--- 2018-07-15 paper3_relevance and symbols_01.Rmd
@@
 
-Last edited at `r Sys.Date()`.[^footnote_scripts]
-
-[^footnote_scripts]: Original R scripts available at:  https://github.com/saaralonbarkat/symbols_and_relevance
+Draft, last edited at `r Sys.Date()`.
 
@@
 
-*Recent studies have demonstrated that symbolic elements in government public communications can enhance citizens' trust in government organizations and their policies.
-They also suggested that the emotive effect of these symbols can compensate for organizations' poor performance and inefficient policies, thereby eliciting undue trust.
+*Recent studies demonstrated that symbolic elements in government communications can enhance citizens' trust in government organizations and policies.
+The emotive effect of symbols can further compensate for organizations' poor functioning, thereby eliciting undue trust.
 This study explores the boundaries of governments' persuasion of citizens through symbolic communication.
-Building on social psychology literature, I hypothesize that citizens are less susceptible to symbols and more likely to scrutinize the substantive content of the communication, the more they perceive the policy issue in the communication as personally relevant.
+Building on social psychology, I hypothesize that citizens are less susceptible to symbols, the more they perceive the policy issue in the communication as personally relevant.
 I test this expectation through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted area.
-The perceived personal relevance of the policy is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere.
-The results indicate that even high levels of perceived personal relevance do not attenuate the positive effect of symbols.
-These findings may suggest that the boundaries of the effect of symbolic communication are wider than expected, which carries significant implications.*
+The policy's perceived personal relevance is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere.
+The results indicate that even high levels of perceived personal relevance do not attenuate the symbols' effect, which entails that the boundaries of persuasion through symbols are wider than expected.*
+
+<br>
+
+*Keywords: Government communications; Government branding; Trust; Experiment*
 
@@
 A growing public administration literature explores whether government public communications can enhance citizens' trust in public organizations and policies.
-Whereas most of the priovious studies have focused on the *informative* aspects of government communications [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011], recent studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
-Such symbols and others exist in almost every government communication, and most prominently in public campaigns, which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
+Whereas most of the studies have focused on the *informative* aspects of government communications [e.g.
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011], recent studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
+Such symbols and others exist in almost every government communication, and most prominently in public campaigns and branding activities,[^footnote_branding] which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
 
-Persuasion through symbolic communications and branding can be perceived favorably, insofar as it enables governments to engage more effectively with relevant publics, thereby to increase their trust and enhance their collaboration.
-The effectiveness of symbols, as opposed to communication of "objective" information, stems from their potency to overcome citizens' negative biases.
-On the other hand, employing a broader perspective of democratic theory, one can argue that in the public-sector domain, the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment.
-Furthermore, previous studies have demonstrated that the positive effect of symbols can compensate for organizations' poor performance (@alonbarkat_2017) and for logically unpersuasive informative content (@alonbarkat_2018).
-Accordingly, symbolic communication can create a misalignment between citizens' positive perceptions and the "real world", and mitigate justified public criticism of government failures.
+Governments' employment of symbolic communications and branding can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016].
+Accordingly, it can mitigate citizens' distrust in government organizations and enhance their collaboration with their policies.
+On the other hand, one can argue that the persuasion of citizens through symbols is problematic, since the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment.
+Furthermore, symbols can compensate for organizations' poor performance and for logically unpersuasive informative content, as empirically demonstrated in previous studies [@alonbarkat_2017; @alonbarkat_2018].
+They can yield a misalignment between citizens' positive perceptions and the "real world".
+This raises the concern that government organizations will strategically use symbols to manipulate public opinion and mitigate justified public criticism of their failures.
+
+[^footnote_branding]: A symbol can be as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp.
+28-29].
+Eshuis and Klijn [-@eshuis_2012, p.
+19] define brand as *a symbolic construct that consists of a name, term, sign, symbol, or design, or combination of these, created deliberately to identify and phenomenon and differentiate it from similar phenomena by adding particular meaning to it*.
+Brand elements, therefore, can be regarded as symbolic elements.
 
@@
 
-The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a theoretical framework for investigating the effects of communications on people's attitudes [@petty_1986; @petty_2011].
+The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a comprehensive theoretical framework for investigating the effects of communications on people's attitudes [@petty_1986; @petty_2011].
 According to ELM, people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
@@
 <br>
-**Figure 1: Theoretical model**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/theoretical_model_relevance.png)
+
+[Figure 1 about here]
 
@@
 <br>
-**Figure 2: Experimental design for policy plan communications**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow_relevance.png)
+
+[Figure 2 about here]
 
@@
 
-**Table 1: Regression analyses – observational measure for perceived personal relevance.**
+<br>
 
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-stargazer(mod_air_1.1,mod_air_1.2,mod_air_1.3,
-          mod_waste_1.1,mod_waste_1.2,mod_waste_1.3,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
+[Table 1 about here]
 
-```
+<br>
 
-&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
+[Figure 3 about here]
 
-**Figure 3: The effect of symbolic elements on trust across areas**
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
-SVIVA2_01_comb = SVIVA2_01_comb %>% 
-  mutate(POLICY_n = Recode(policy,"'TRUST_air_INDEX'='Air-pollution'; 'TRUST_waste_INDEX'='Recycling'"))
-
-ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
-  theme_classic()+
-  #geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.65),
-               width=0.2,size=0.5,position=position_dodge(0.2),color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.2))+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.2),alpha=0.8)+
-  scale_shape_manual(guide=F,values=c(19,1))+
-  scale_linetype_manual(name="Area",values=c(1,4))+
-  facet_grid(~POLICY_n)+
-  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
-
-```
-
-<font size="0.5">
-
-*Note*: Error bars represent 90% confidence intervals.
-
-</font>
+<br>
 
@@
 
-**Table 2: Regression analyses – experimental manipulation of perceived personal relevance.**
+<br>
 
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_air_2.1 = lm(TRUST_air_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_air_2.2 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
-mod_air_2.3 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
-mod_air_2.4 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
-
-mod_waste_2.1 = lm(TRUST_waste_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_waste_2.2 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
-mod_waste_2.3 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
-mod_waste_2.4 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
-
-stargazer(mod_air_2.1,mod_air_2.2,mod_air_2.4,
-          mod_waste_2.1,mod_waste_2.2,mod_waste_2.4,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Relevance treatment",
-                             "Relevance treatment x Real symbols",
-                             "Relevance treatment x Fake symbols",
-                             "Relevance treatment x Weak Information",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information",
-                             "Relevance treatment x Area",
-                             "Relevance treatment x Area x Real symbols",
-                             "Relevance treatment x Area x Fake symbols",
-                             "Relevance treatment x Area x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          order = c(1,2,4,3,6:8,5,9,10,12,11,13:15),
-          initial.zero = FALSE,
-          notes = "",
-          notes.append = FALSE)
-
-```
+[Table 2 about here]
 
@@
 Congruently, governments' investments in public communications, and specifically in branding and advertising, has increased over the past generation in many economically-developed democratic countries.
-This study contributes to the growing public administration research on citizens' responses to government public communications, and specifically to symbolic elements entangled in these communications.
+This study contributes to the growing Public-Administration research on citizens' responses to government public communications, and specifically to symbolic elements entangled in these communications.
 I explored the expectation, derived from social psychology, that citizens are less affected by symbols and more likely to scrutinize the content of the communication the more they perceive it as relevant to their own lives.
@@
 206].
+
+The results of this study, if generalizable, have significant implications.
+They challenge the rationalistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
+Instead, they suggest that more often than not, citizens rely on brands and other symbolic elements in public communications, even with regard to policy issues that have direct implications on their own lives.
+Altogether, this study highlights the role played by government branding and other forms of symbolic communication in shaping citizens view of governments.
+It suggests that the boundaries of persuasion via symbols and branding are much wider than expected, based on previous social psychology and marketing studies.
+From the practical point of view of government organizations, this entails that organizations can overcome citizens distrust by investing in symbolic communications.
+Nonetheless, employing a broader perspective of democratic theory, these conclusions are disturbing insofar as they buttress the concern that government organizations will deliberately use symbolic communications to cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements, namely as "propaganda".
+For good or for ill, citizens are affected by the emotional connections and associations of symbols.
 
@@
 
+#References
+
 <br>
 
-#References
+#Figures and tables
+
+<br>
+**Figure 1: Theoretical model**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/theoretical_model_relevance.png)
+
+<br>
+
+**Figure 2: Experimental design for policy plan communications**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow_relevance.png)
+
+<br>
+
+**Table 1: Regression analyses – observational measure for perceived personal relevance.**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+stargazer(mod_air_1.1,mod_air_1.2,mod_air_1.3,
+          mod_waste_1.1,mod_waste_1.2,mod_waste_1.3,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information"),
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
+
+<br>
+
+**Figure 3: The effect of symbolic elements on trust across areas**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
+SVIVA2_01_comb = SVIVA2_01_comb %>% 
+  mutate(POLICY_n = Recode(policy,"'TRUST_air_INDEX'='Air-pollution'; 'TRUST_waste_INDEX'='Recycling'"))
+
+ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
+  theme_classic()+
+  #geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.65),
+               width=0.2,size=0.5,position=position_dodge(0.2),color="gray70") + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.2))+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.2),alpha=0.8)+
+  scale_shape_manual(guide=F,values=c(19,1))+
+  scale_linetype_manual(name="Area",values=c(1,4))+
+  facet_grid(~POLICY_n)+
+  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
+  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
+
+```
+
+<font size="0.5">
+
+*Note*: Error bars represent 90% confidence intervals.
+
+</font>
+
+<br>
+
+**Table 2: Regression analyses – experimental manipulation of perceived personal relevance.**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_air_2.1 = lm(TRUST_air_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_air_2.2 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
+mod_air_2.3 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
+mod_air_2.4 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
+
+mod_waste_2.1 = lm(TRUST_waste_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_waste_2.2 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
+mod_waste_2.3 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
+mod_waste_2.4 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
+
+stargazer(mod_air_2.1,mod_air_2.2,mod_air_2.4,
+          mod_waste_2.1,mod_waste_2.2,mod_waste_2.4,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Relevance treatment",
+                             "Relevance treatment x Real symbols",
+                             "Relevance treatment x Fake symbols",
+                             "Relevance treatment x Weak Information",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information",
+                             "Relevance treatment x Area",
+                             "Relevance treatment x Area x Real symbols",
+                             "Relevance treatment x Area x Fake symbols",
+                             "Relevance treatment x Area x Weak Information"),
+          omit.stat = c("rsq","ser", "f"),
+          order = c(1,2,4,3,6:8,5,9,10,12,11,13:15),
+          initial.zero = FALSE,
+          notes = "",
+          notes.append = FALSE)
+
+```
+
+<br>

### 2018-07-16 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
       toc_depth: 3
+  pdf_document:
+    toc: yes
+  word_document: default
 link-citations: yes
 bibliography: phd_paper_2.bib
-#csl: apsa.csl
+csl: apa.csl
 urlcolor: blue
@@
 Finally, I replicated my analyses on the unfiltered sample.
-None of these multiple robust analyses supports the theoretical hypotheses regarding the moderating effect of personal relevance.
+None of these multiple robust analyses supports the theoretical hypotheses regarding the moderation of personal relevance on the effect of symbols.
+The interaction between personal relevance and information is confirmed only by the analysis of analysis of participants' subjective reporting of the personal relevance, and only with regard to the air-pollution policy.
 
@@
 
-Public communications has been proposed as a remedy for citizens’ low trust in government, and their underestimation of public-service performance.
+Public communications have been proposed as a remedy for citizens’ low trust in government, and their underestimation of public-service performance.
 Congruently, governments' investments in public communications, and specifically in branding and advertising, has increased over the past generation in many economically-developed democratic countries.

### 2018-07-20 paper3_APPENDIX.Rmd
Add files via upload

@@
 In the tables below, I report the results of additional robust analyses testing the moderating role of the perceived personal relevance of the communications.
-In **Table A4** I analyze subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
-These analyses show that higher scores of perceived personal relevance did not attenuate the positive effect of the real symbols.
-However, it did slightly increase the effect of the weak information with regard to the air-pollution policy, consistent with Hypothesis 2.
-
-In **Tables A5 - A7**, I examine the effects of relevance treatment and the differences between the areas on subjects elaboration of the two policy plans, using three additional measures.
+
+In **Tables A4 - A6**, I examine the effects of relevance treatment and the differences between the areas on subjects elaboration of the two policy plans, using three additional measures.
 The first measure is the number of seconds participants spent on scanning the policy plans, log transformed (hereafter: reaction time).
@@
 
-In **Tables A8 and A9**, I replicate the main analyses while adding additional control variables.
+In **Tables A7 and A8**, I replicate the main analyses while adding additional control variables.
 In Tables A7, I control for demographics and additional individual-level covariates, including ideology and trust in government ministries in general.
 In Table A8 I further control for factors that can be related to participants' motivation to elaborate, including having young children, general interest in environmental issues and following environmental issues in the media.
-The two final variables are based on survey items which were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (n = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).Finally, in **Table A10**, I add those subjects who were filtered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
+The two final variables are based on survey items which were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (*n* = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).
+Finally, in **Table A9**, I add those subjects who were filtered, except for those who are under the age of 18 (*n* = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
 In all these analyses, the effects of the symbols and information manipulations and their interaction with the areas and the relevance manipulation are consistent with the main models.
 
-<br>
-
-**Table A4: Regression table - subjective reporting of perceived personal relevance**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
-mod_air_1.3_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)
-
-mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
-mod_waste_1.3_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)
-
-stargazer(mod_air_1.2_apx,mod_air_1.3_apx,
-          mod_waste_1.2_apx,mod_waste_1.3_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Reported relevance",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Reported relevance x Real symbols",
-                             "Reported relevance x Fake symbols",
-                             "Reported relevance x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-**Table A5: Regression table - effect of personal relevance on reaction time**
+In **Table A10** I analyze subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
+These analyses show that higher scores of perceived personal relevance did not attenuate the positive effect of the real symbols.
+However, it did slightly increase the effect of the weak information with regard to the air-pollution policy, consistent with Hypothesis 2.
+
+<br>
+
+<br>
+
+**Table A4: Regression table - effect of personal relevance on reaction time**
 
@@
 
-**Table A6: Regression table - effect of personal relevance on memory score**
+**Table A5: Regression table - effect of personal relevance on memory score**
 
@@
 
-**Table A7: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**
+**Table A6: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**
 
@@
 
-**Table A8: Regression table - adding control variables**
+**Table A7: Regression table - adding control variables**
 
@@
 
-**Table A9: Regression table - adding personal relevance and motivational control variables**
+**Table A8: Regression table - adding personal relevance and motivational control variables**
 
@@
 
-**Table A10: Regression table - unfiltered sample**
+**Table A9: Regression table - unfiltered sample**
 
@@
 
+**Table A10: Regression table - subjective reporting of perceived personal relevance**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
+mod_air_1.3_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)
+
+mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
+mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
+mod_waste_1.3_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)
+
+stargazer(mod_air_1.2_apx,mod_air_1.3_apx,
+          mod_waste_1.2_apx,mod_waste_1.3_apx,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Reported relevance",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Reported relevance x Real symbols",
+                             "Reported relevance x Fake symbols",
+                             "Reported relevance x Weak Information"),
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+<br>
+
 #5. English translation of the survey experiment

### 2018-07-20 paper3_relevance and symbols_01.Rmd
Add files via upload

@@
 A growing public administration literature explores whether government public communications can enhance citizens' trust in public organizations and policies.
-Whereas most of the studies have focused on the *informative* aspects of government communications [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011], recent studies further pointed to the emotive effect of *symbolic* elements entangled in them, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
+Most studies have focused on the *informative* aspects of government communications [e.g.
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011].
+Recent studies, however, further pointed to the emotive effect of symbolic elements entangled in communications, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
 Such symbols and others exist in almost every government communication, and most prominently in public campaigns and branding activities,[^footnote_branding] which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
@@
 On the other hand, one can argue that the persuasion of citizens through symbols is problematic, since the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment.
-Furthermore, symbols can compensate for organizations' poor performance and for logically unpersuasive informative content, as empirically demonstrated in previous studies [@alonbarkat_2017; @alonbarkat_2018].
+Furthermore, symbols can compensate for organizations' poor performance and for logically unpersuasive informative content, as empirically demonstrated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
 They can yield a misalignment between citizens' positive perceptions and the "real world".
-This raises the concern that government organizations will strategically use symbols to manipulate public opinion and mitigate justified public criticism of their failures.
+This raises the concern that government organizations will strategically exploit symbols to manipulate public opinion and mitigate justified public criticism of their failures.
 
@@
 
-In this study, I explore the boundaries of governments' persuasion of citizens through symbolic communication, to assess the above concern.
-Namely, I seek to explore the conditions under which symbolic elements are likely to be more, or less, effective in shaping (and possibly manipulating) citizens' trust.
-Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I theorize that citizens are less susceptible to symbols the more they perceive the policy issue in the communication as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
-Similarly, high perceived personal relevance is expected to enhance citizens' inclination to scrutinize the substantive content of communication.
+To assess the above concern, this study explores the boundaries of governments' persuasion of citizens through symbolic communication.
+Namely, I seek to examine the conditions under which symbolic elements are likely to be more, or less, effective in shaping (and possibly manipulating) citizens' trust.
+Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I theorize that citizens are less susceptible to symbols, and more inclined to scrutinize the substantive content of communication, the more they perceive the policy issue at hand as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
 Employing a survey experiment, I test these hypotheses in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay).
@@
 These two routes for persuasion are regarded as two ends of an "elaboration continuum".
-People may also be located between these two edges, and then a mixture of these processes will determine their persuasion.
+People may also be located between these two ends of the continuum, and then a mixture of these processes will determine their persuasion.
 
 Viewed against the above theoretical framework, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
-Conversely, symbolic elements can be regarded as potential peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
+Conversely, symbolic elements can be regarded as peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
 Accordingly, the more citizens are motivated to think about the content of the communication, and the more capable they are of doing so, the more they are likely to form their attitudes based on substantive information.
@@
 This postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
-These studies have demonstrated that increasing the perceived personal relevance of a communication enhances the effect of arguments in the communication and attenuates the effect of peripheral cues.
+These studies have demonstrated that increasing the perceived personal relevance of a communication enhances the effect of its argumentation and attenuates the effect of peripheral cues.
 Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors]
@@
 
-*H<sub>2</sub> - The logical quality of the communication is more (less) likely to affect citizens' trust in governemnt organizations and policicies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
+*H<sub>2</sub> - The logical quality of the communication is more (less) likely to affect citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
 
@@
 Focusing on the case of the Israeli Environment Protection Ministry (hereafter: EPM), I examine citizens' responses to communications of EPM regarding two of its current policy plans.
-The first policy regards *reducing the the air pollution in the highly polluted Haifa-Bay area*, located in the north of Israel.
+The first policy regards *reducing the air pollution in the highly polluted Haifa-Bay area*, located in the north of Israel.
 This policy issue offers a fortunate case for examining the moderating role of perceived personal relevance.
@@
 Moreover, because this policy issue is intangible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as is the case in many other policy issues [@petty_1983].
-Congruently, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize a communication about the air-pollution in their area of residence, yet no more capable to do so than those who reside elsewhere.
+Congruently, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize the communication about the air-pollution in their area of residence, yet are no more capable of doing so than those who reside elsewhere.
 As explained below, the sample population of the study consists of residents of the Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
@@
 This topic is assumed to be equally relevant for Haifa-bay residents and others.
-Therefore, adding this policy plan is intended to confirm that respondents’ different responses to the air-pollution policy, if found, may be attributed to perceived personal relevance.
+Therefore, adding this policy plan is intended to confirm that respondents’ divergent responses to the symbolic elements in the communication regarding the air-pollution policy, if found, may be attributed to differences in perceived personal relevance.
 I henceforth refer to these two policy plans as "air-pollution" and "recycling".
 
-I exploited three three symbolic elements which have been used in the EPM's public communications, and became widely recognized by the public.
+I exploited three symbolic elements, which have been used in the EPM's public communications, and became widely recognized by the public.
 The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
@@
 The latter open question was specifically designed to prime Haifa-bay residents to think about the personal relevance of the air pollution in their area.
-Subjects in the relevance control group were asked equivalent questions about their field of occupation .
+Subjects in the relevance control group were asked equivalent questions about their field of occupation.
 
@@
 
-The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively).
+The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies, respectively).
 This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-Participants reported, on average, lower trust, on average, in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
+Participants reported, on average, lower trust in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
 
-The key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.[^footnote_symbols_manipulation_check] The perceived personal relevance of the communication is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
+The key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.[^footnote_symbols_manipulation_check] The latter is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
 I coded living in Haifa-bay area according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities.
@@
 I regress trust in policy on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).
+
 The real symbols had positive main effects on both policies compared with the no symbols condition (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations for the air-pollution and recycling policies, respectively).
@@
 Counter to these expectations, in Model 1.3, the interaction between residence in the center and the real symbols is negative (*p*<.1), and the interaction with the weak information is insignificant.
-These findings suggest that the real symbols were more effective in increasing the trust of those reside in the polluted area and that the latter were no more likely to scrutinize the content of the communication.
-I also found similar patterns regarding the recycling policy.
-In Model 1.6, the interaction between the areas and the information is insignificant, and the interaction with the real symbols is negative.
-**Figure 3** provides a descriptive demonstration of the interaction between the areas and the symbols manipulation for the two policies.
+I also found similar patterns regarding the recycling policy: in Model 1.6, the interaction between residing in the center and the weak information is insignificant, and the interaction with the real symbols is negative and significant.
+Figure 3 provides a descriptive demonstration of the interaction between the areas and the symbols manipulation for the two policies.
+The findings, as illustrated in **Figure 3**, suggest that the real symbols were more effective in increasing the trust of those residing in the polluted area and that the latter were no more likely to scrutinize the content of the communication.
 
@@
 In all these models, the relevance treatment did not yield significant effects, and there are no significant interactions with the symbols and information manipulations.
-The triple interactions with the areas are also insignificant (in Models 2.3, 2.6), which indicates that in neither of these areas did the relevance treatment moderate the effects of the symbols and information manipulations.
+The triple interactions with the areas are also insignificant (in Models 2.3, 2.6), which indicates that the relevance treatment did not moderate the effects of the symbols and information manipulations across the two areas.
 
@@
 None of these multiple robust analyses supports the theoretical hypotheses regarding the moderation of personal relevance on the effect of symbols.
-The interaction between personal relevance and information is confirmed only by the analysis of analysis of participants' subjective reporting of the personal relevance, and only with regard to the air-pollution policy.
+The interaction between personal relevance and information is confirmed only by the analysis of participants' subjective reporting of the personal relevance, and only with regard to the air-pollution policy.
 
@@
 
-Public communications have been proposed as a remedy for citizens’ low trust in government, and their underestimation of public-service performance.
+Public communications have been proposed as a remedy for citizens’ low trust in government, and for their underestimation of public-service performance.
 Congruently, governments' investments in public communications, and specifically in branding and advertising, has increased over the past generation in many economically-developed democratic countries.
@@
 Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also failed to moderate the effects of the symbols and information in the communications.
-These findings are also consistent with the findings of @alonbarkat_2017, where they found that citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) were nonetheless significantly affected by a symbol of the government-owned electricity company.
+These findings are also consistent with the findings of @alonbarkat_2017, where they found that the trust of citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) was nonetheless significantly affected by a symbol of the government-owned electricity company.
 
@@
 Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance.
-Rather, they can be explained by the lower baseline of Haifa-Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
+Rather, it might be explained by the lower baseline of Haifa-Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
 Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
